### 2022-10-26 characterisation/Code/Comparing_symptoms.Rmd
update

---
title: "Exploring_symptoms_across_cohorts"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE, 
                      message=FALSE, 
                      comment = FALSE,
                      cache.lazy=FALSE)
options(scipen=999)
```

```{r include=FALSE}
# packages
library(SqlRender)
library(DBI)
library(DatabaseConnector)
library(here)
library(dplyr)
library(tidyr)
library(CDMConnector)
library(stringr)
library(lubridate)
library(gtsummary)

# Connection details ----
server    <- Sys.getenv("SERVER_JUN22")
server_dbi<- Sys.getenv("SERVER_DBI_JUN22")
user      <- Sys.getenv("DB_USER_JUN22")
password  <- Sys.getenv("DB_PASSWORD_JUN22")
port      <- Sys.getenv("DB_PORT_JUN22") 
host      <- Sys.getenv("DB_HOST_JUN22")

db <- dbConnect(RPostgres::Postgres(), 
                dbname = server_dbi,
                port = port,
                host = host, 
                user = user, 
                password = password)

targetDialect              <- "postgresql"
cdm_database_schema        <- "omop21t4_cmbd" 
vocabulary_database_schema <-"omop21t4_cmbd" 
write_schema               <-"results21t4_cmbd"

# Generate cdm object to access the tables
cdm <- cdm_from_con(db, 
             cdm_schema = cdm_database_schema,
             write_schema = write_schema,
             cohort_tables = c("er_long_covid_final_cohorts",
                               "er_long_covid_all_symptoms_cohorts"))

```

```{r include=FALSE}
generate_table <- function(cohort_id, window, name){
data <- cdm$er_long_covid_all_symptoms_cohorts %>%
  filter(main_cohort_id == cohort_id & window_days == window) %>%
  collect()
summary <-  data%>% 
  mutate(all_symp = as.factor(all_symp)) %>%
  select(-subject_id, -window_days, - main_cohort_id, - cohort_start_date ) %>%
  mutate(gen = paste0(name)) %>%
   tbl_summary(
       by = "gen",
  digits = all_categorical()~ c(0,1),
  missing = "ifany",
  missing_text= "Missing",
  percent = "col"
           ) %>% 
  bold_labels()
  summary
}
```

```{r include=FALSE}
t.covid.infection <- generate_table(cohort_id= "22",
                                    window="90",
                                    name = "New COVID-19 infection")

t.covid.reinfections <- generate_table(cohort_id= "71",
                                    window="90",
                                    name = "Reinfections")

t.covid.confirmed <- generate_table(cohort_id= "30",
                                    window="90",
                                    name = "Confirmed infections")

t.tested.negative.earliest <- generate_table(cohort_id = "29",
                                    window="90",
                                    name = "Tested negative, earliest")

t.pcr.negative.earliest <- generate_table(cohort_id = "24",
                                    window="90",
                                    name = "PCR negative, earliest")

```

```{r}

table  <- tbl_merge(tbls = list(t.covid.infection,      
                                t.covid.reinfections,
                                t.tested.negative.earliest,
                                t.pcr.negative.earliest
                                 ), 
                     tab_spanner = c("", "", "", ""))

table

```
```{r}
## explorar numero de sintomas en tested negative y covid infection
# plot_grid(
#   covid_infection_numb_symp %>% filter(window==90) %>% 
#     ggplot(aes(all_symp)) +geom_bar() + theme_minimal() + ggtitle("Covid-19")  ,
# tested_negative_all_numb_symp %>% filter(window==90) %>%
#   ggplot(aes(all_symp)) +geom_bar() + theme_minimal() + ggtitle("Tested negative")
# )

```

### 2022-10-26 characterisation/Code/Create_Table1.R

@@ -1,0 +1,455 @@
+##  CHaracteristing Long COVID ### 
+# Getting  TABLE 1-  Comparing characteristics of Covid cases vs Long Covid 
+
+# packages
+library(SqlRender)
+library(DBI)
+library(DatabaseConnector)
+library(here)
+library(dplyr)
+library(tidyr)
+library(CDMConnector)
+library(stringr)
+library(lubridate)
+library(tableone)
+
+
+# Connection details ----
+server    <- Sys.getenv("SERVER_JUN22")
+server_dbi<- Sys.getenv("SERVER_DBI_JUN22")
+user      <- Sys.getenv("DB_USER_JUN22")
+password  <- Sys.getenv("DB_PASSWORD_JUN22")
+port      <- Sys.getenv("DB_PORT_JUN22") 
+host      <- Sys.getenv("DB_HOST_JUN22") 
+
+
+db <- dbConnect(RPostgres::Postgres(), 
+                dbname = server_dbi,
+                port = port,
+                host = host, 
+                user = user, 
+                password = password)
+
+targetDialect              <- "postgresql"
+cdm_database_schema        <- "omop21t4_cmbd" 
+vocabulary_database_schema <-"omop21t4_cmbd" 
+write_schema               <-"results21t4_cmbd"
+
+# Generate cdm object to access the tables
+cdm <- cdm_from_con(db, 
+             cdm_schema = cdm_database_schema,
+             write_schema = write_schema,
+             cohort_tables = c("er_long_covid_final_cohorts"))
+
+## cohrot of interest - first New Covid infections
+# main_cohort_interest <- cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == 22)
+# 90 days long Covid cohort
+# first two digits are for the "mother cohort"
+# digits 3,4 are for the symptoms cohort (99 is for any symptom") 
+# last two digits for window period
+# long_covid_cohort <- cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == 229990)
+
+
+# Function to get the data for the table 
+generate_data_table1 <- function(main_cohort_interest, long_covid_cohort){
+working_cohort <- main_cohort_interest %>% 
+ rename(person_id=subject_id) %>%
+  left_join(cdm$person  %>%
+              select(person_id, gender_concept_id, year_of_birth, month_of_birth, day_of_birth) %>%
[…]

### 2022-10-26 characterisation/Code/Data_prep.R

@@ -308,18 +308,18 @@ covid_infection <- covid_infection %>%
   mutate(cohort_definition_id= as.integer(cohort_definition_id))
 
 ## inserting these cohorts into the database
-#### guardar cohorts mare 
-# esborrar taula
-# sql_query <- glue::glue("DROP TABLE {write_schema}.er_long_covid_final_cohorts\n" )
-# DBI::dbExecute(db, as.character(sql_query))
+#### remove prior tables fi needed
+ sql_query <- glue::glue("DROP TABLE {write_schema}.er_long_covid_final_cohorts\n" )
+ DBI::dbExecute(db, as.character(sql_query))
 
+ # create the new table 
 sql_query <- glue::glue("SELECT * INTO {write_schema}.er_long_covid_final_cohorts\n",
                           "FROM (\n",
                           dbplyr::sql_render(reinfections),
                           "\n) AS from_table")
 DBI::dbExecute(db, as.character(sql_query))
 
-# quan la taula ja existeix
+# append rows to existing table
 sql_query <- glue::glue("INSERT INTO {write_schema}.er_long_covid_final_cohorts\n",
                           "SELECT * FROM (\n",
                           dbplyr::sql_render(covid_infection),
@@ -642,8 +642,6 @@ PCR_negative_all_id <- cohorts_ids %>%
                           filter(str_detect(name, "PCR_Negative_all")) %>%
                           select(cohort_definition_id) %>% pull()
 
-
-
 tested_negative_earliest <- generate_tested_negative_cohort(id_interest = tested_negative_earliest_id)
 tested_negative_all      <- generate_tested_negative_cohort(id_interest = tested_negative_all_id)
 PCR_negative_earliest    <- generate_tested_negative_cohort(id_interest = PCR_negative_earliest_id)
@@ -658,40 +656,32 @@ exclusion_table <- bind_rows(exclusion_table,
   left_join(cohorts_ids %>% select(cohort_definition_id, name, type) %>%
               mutate(cohort_definition_id=as.integer(cohort_definition_id)))
 
-
-
 #### save tested negative cohorts 
-# canviar el codi per fer-ho dincs la funcio 
-sql_query <- glue::glue("INSERT INTO {write_schema}.er_long_covid_final_cohorts\n",
-                          "SELECT * FROM (\n",
-                          dbplyr::sql_render(tested_negative_earliest[[1]]),
[…]

### 2022-10-26 characterisation/Code/Data_prep.R
update

@@ -27,7 +27,7 @@ db <- dbConnect(RPostgres::Postgres(),
                 user = user, 
                 password = password)
 
-## connectionDetails per inserir table amb OHDSI tools
+## we also cuse connection details to insert later tables using OHDSI  tools
 connectionDetails <-DatabaseConnector::downloadJdbcDrivers("postgresql", here::here())
 connectionDetails <- DatabaseConnector::createConnectionDetails(dbms = "postgresql",
                                                                 server =server,
@@ -39,8 +39,20 @@ connectionDetails <- DatabaseConnector::createConnectionDetails(dbms = "postgres
  
 targetDialect              <- "postgresql"
 cdm_database_schema        <- "omop21t4_cmbd" 
-vocabulary_database_schema <-"omop21t4_cmbd" 
-write_schema               <-"results21t4_cmbd"
+vocabulary_database_schema <- "omop21t4_cmbd" 
+write_schema               <- "results21t4_cmbd"
+
+# cdm object to access the tables easily
+cdm <- cdm_from_con(db, 
+             cdm_schema = cdm_database_schema,
+             write_schema = write_schema,
+             cohort_tables = c("er_cohorts_for_longcov"))
+
+# create results folder if needed
+cohorts.folder <- here::here("results")
+if (!file.exists(cohorts.folder)){
+  dir.create(cohorts.folder)
+}
 
 # parameters ----
 # to get rid of covid diagnoses captured before the start of the pandemic --
@@ -52,22 +64,14 @@ influenza_start_date<- as.Date("2019-12-01", "%Y-%m-%d")
 symptoms_start_date <- as.Date("2019-08-29","%Y-%m-%d")
 end_index_date      <- as.Date("2021-09-02", "%Y-%m-%d")
 
-
-
 # Cohort ids -----
-# Cohort ids are in csv with all cohorts ids
+# Cohort ids are in a csv with all cohorts ids
 cohorts_ids  <- read.csv2(here("ATLAS Cohort Definitions_LongCovid.csv")) %>%
-  mutate(name= paste(sub(".*LongCov-ER_", "", name)))
+                          mutate(name= paste(sub(".*LongCov-ER_", "", name)))
 covid_ids    <- cohorts_ids %>% filter(type=="covid-19") %>% select(cohort_definition_id) %>% pull()
 influenza_id <- cohorts_ids %>% filter(type=="influenza") %>% select(cohort_definition_id) %>% pull()
[…]

### 2022-10-26 characterisation/Cohort_Dx_initial/00_Get_json_cohorts_Atlas.R

@@ -1,6 +1,7 @@
 #### warning #### 
 #### this is not working for the cohorts that include Measurements (such as COVID one) with results in LOINC
 # concept ids for LOINC are >10000000  (10^8) and numbers are rounded - so the concepts IDs end up being wrong!!
+# the error applies also for allergy
 # use this just for the Symptoms cohorts
 library(here)
 library(DatabaseConnector)
@@ -12,20 +13,21 @@ baseUrl <- "https://atlas-demo.ohdsi.org/WebAPI"
 cohortIds <- c(
 1780619,1780589,1780628,1780624,1780622,1780617,1780615,1780618,1780621,1780620,
   1780626,1780612,1780625,1780614,1780613,1780631,1780623,1780627,1780629,1780630,
-1780632,1780603,1780604,1780608,
-  1780846
+1780632,1780603,1780604,  1780846
 )
 
 # cohorts with measurements
-cohorts_measurements <- c(1780611,1780580,1780634,1780587,1780635,1780582,1780581)
+cohorts_measurements <- c(1780611,1780580,1780634,1780587,1780635,1780582,1780581, 1780608)
 
 
 # create folder to save cohorts if needed
-cohorts.folder <- here::here("1_InstantiateCohorts/Cohorts_v2")
+cohorts.folder <- here::here("Cohort_Dx_initial/1_InstantiateCohorts/Cohorts_v2")
 if (!file.exists(cohorts.folder)){
   dir.create(cohorts.folder)
 }
 
+
+cohortId <- 1780608
 for (i in 1:length(cohortIds)){
 cohortId <- cohortIds[i]
  message(paste0("working on ",cohortId))

### 2022-10-26 characterisation/Cohort_Dx_initial/01_CodeToRun.R

@@ -15,8 +15,6 @@ library(CohortGenerator)
 library(here)
 library(stringr)
 
-
-
 # database metadata and connection details -----
 
 # database connection details
@@ -68,7 +66,7 @@ db <- dbConnect(RPostgres::Postgres(),
 cohortTableStem<-"er_cohorts_for_longcov"
 
 # Run analysis ----
-source(here("RunAnalysis.R"))
+source(here("Cohort_Dx_initial", "RunAnalysis.R"))
 
 # Review results -----
 # CohortDiagnostics::preMergeDiagnosticsFiles(dataFolder = here("Results"))

### 2022-10-26 characterisation/Cohort_Dx_initial/RunAnalysis.R

@@ -1,12 +1,12 @@
 # Get cohort details -----
- cohortJsonFiles <- list.files(here("1_InstantiateCohorts", "Cohorts"))
+ cohortJsonFiles <- list.files(here("Cohort_Dx_initial","1_InstantiateCohorts", "Cohorts"))
 #cohortJsonFiles <- list.files(here("1_InstantiateCohorts", "Covid_cohorts"))
 
 cohortJsonFiles <- cohortJsonFiles[str_detect(cohortJsonFiles,".json")]
 
 cohortDefinitionSet <- list()
 for(i in 1:length(cohortJsonFiles)){
-working.json<-here("1_InstantiateCohorts", "Cohorts",
+working.json<-here("Cohort_Dx_initial","1_InstantiateCohorts", "Cohorts",
                       cohortJsonFiles[i])
 cohortJson <- readChar(working.json, file.info(working.json)$size)
 cohortExpression <- cohortExpressionFromJson(cohortJson) # generates the sql
@@ -44,28 +44,28 @@ CohortGenerator::exportCohortStatsTables(
     connection = NULL,
     cohortDatabaseSchema = results_database_schema,
     cohortTableNames = cohortTableNames,
-    cohortStatisticsFolder = here("Results"),
+    cohortStatisticsFolder = here("Cohort_Dx_initial", "Results"),
     incremental = FALSE)
 
 # cohort diagnostics
-executeDiagnostics(cohortDefinitionSet,
-                   connectionDetails = connectionDetails,
-                   cohortTable = cohortTableStem,
-                   cohortDatabaseSchema = results_database_schema,
-                   cdmDatabaseSchema = cdm_database_schema,
-                   exportFolder = here("Results"),
-                   databaseId = db.name,
-                   minCellCount = 5,
-                   runInclusionStatistics = FALSE,
-                   runOrphanConcepts = FALSE,
-                   runTimeDistributions = FALSE,
-                   runVisitContext = FALSE,
-                   runBreakdownIndexEvents = FALSE,
-                   runIncidenceRate = FALSE,
-                   runTimeSeries = FALSE,
-                   runCohortOverlap = FALSE,
-                   runCohortCharacterization = TRUE,
-                   runTemporalCohortCharacterization = FALSE)
+# executeDiagnostics(cohortDefinitionSet,
+#                    connectionDetails = connectionDetails,
+#                    cohortTable = cohortTableStem,
+#                    cohortDatabaseSchema = results_database_schema,
[…]

### 2022-10-27 characterisation/Code/Comparing_symptoms.Rmd
updates

@@
 library(gtsummary)
+library(tableone)
 
@@
 
+#  get ids for cohorts
+
+cohorts_ids  <- read.csv2(here("ATLAS Cohort Definitions_LongCovid.csv")) %>%
+                          mutate(name= paste(sub(".*LongCov-ER_", "", name)))
+
+new_infection_id <- as.character(cohorts_ids %>%
+                    filter(str_detect(name, "New_Infection")) %>% 
+                    select(cohort_definition_id) %>% pull())
+
+tested_positive_id <- as.character(cohorts_ids %>%
+                    filter(str_detect(name, "Tested_Positive")) %>% 
+                    select(cohort_definition_id) %>% pull())
+
+tested_negative_earliest_id <- as.character(cohorts_ids %>%
+                    filter(str_detect(name, "Tested_Negative_earliest")) %>% 
+                    select(cohort_definition_id) %>% pull())
+
+pcr_negative_earliest_id <-as.character( cohorts_ids %>%
+                    filter(str_detect(name, "PCR_Negative_earliest")) %>% 
+                    select(cohort_definition_id) %>% pull())
+
+# get data for table 1
+ table1_data_new_infections  <- load(here("data", "table1_data_new_infections.Rda")))
+
+```
+
+```{r}
+
+table1.data<-rbind(  
+# those without missing values
+       table1_data_new_infections   %>%
+        mutate(group = "With COVID-19_infection"),
+        table1_data_new_infections  %>%
+        filter(long_covid == 1)%>%
+          mutate(group = "90 days Long Covid symtpoms"))
+
+# variables
+vars<-c(
+        "age",
+        "age_gr2",
+        "gender",
+        "nationality_cat",
+        "vaccination_status",
+        "medea",
+        "asthma",
+        "autoimmune_disease",
+        "copd",
+        "dementia",
+        "diabetes",
+        "heart_disease",
+        "cancer",
+        "hypertension",
+        "renal_impairment"
+)
+
+factor.vars<- c(
+        "age_gr2",
+        "gender",
+        "nationality_cat",
+        "vaccination_status",
+        "medea",
+        "asthma",
+        "autoimmune_disease",
+        "copd",
+        "dementia",
+        "diabetes",
+        "heart_disease",
+        "cancer",
+        "hypertension",
+        "renal_impairment"
+)
+
+summary.characteristics<-print(CreateTableOne(
+  vars =  vars,
+  factorVars = factor.vars,
+  includeNA=T,
+  data = table1.data,
+  strata=c("group"),
+  test = F), 
+  showAllLevels=F,
+  smd=T,
+  nonnormal = vars, #all 
+  noSpaces = TRUE,
+  contDigits = 1,
+  printToggle=FALSE)
+
+# format numbers (eg commas etc)  
+# functionality does not seem to be in tableone package
+# so do this manually
+for(i in 1:2) {
+# tidy up 
+  cur_column <- summary.characteristics[, i]
+  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
+                as.numeric() 
+  cur_column <-nice.num(cur_column)
+  # add back in
+  summary.characteristics[, i] <- str_replace(string=summary.characteristics.loss[, i], 
+                              pattern='[0-9.]+\\b', 
+                              replacement=cur_column)    
+}
+
 ```
@@
 ```{r include=FALSE}
+# function to obtain data for table
 generate_table <- function(cohort_id, window, name){
@@
   filter(main_cohort_id == cohort_id & window_days == window) %>%
+  distinct() %>%
   collect()
@@
 ```{r include=FALSE}
-t.covid.infection <- generate_table(cohort_id= "22",
+t.covid.infection <- generate_table(cohort_id= new_infection_id,
                                     window="90",
@@
 
-t.covid.confirmed <- generate_table(cohort_id= "30",
+t.covid.confirmed <- generate_table(cohort_id= tested_positive_id,
                                     window="90",
@@
 
-t.tested.negative.earliest <- generate_table(cohort_id = "29",
+t.tested.negative.earliest <- generate_table(cohort_id = tested_negative_earliest_id,
                                     window="90",
@@
 
-t.pcr.negative.earliest <- generate_table(cohort_id = "24",
+t.pcr.negative.earliest <- generate_table(cohort_id = pcr_negative_earliest_id,
                                     window="90",

### 2022-10-27 characterisation/Code/Data_prep.R

@@ -270,6 +270,7 @@ cohorts_ids <- rbind(cohorts_ids,
                      tibble(atlas_id = NA,
                             name = "First COVID-19 infection",
                             cohort_definition_id =70, 
+                            name_var = "first_infection",
                             type = "covid-19"))
 
 exclusion_table<-rbind(exclusion_table,
@@ -304,6 +305,7 @@ cohorts_ids <- rbind(cohorts_ids,
                      tibble(atlas_id = NA,
                             name = "Reinfections",
                             cohort_definition_id =71, 
+                            name_var = "reinfections",
                             type = "covid-19"))
 
 covid_infection <- covid_infection %>%

### 2022-10-27 characterisation/Code/Comparing_symptoms.Rmd
update

@@
 ```{r setup, include=FALSE}
+
 knitr::opts_chunk$set(echo = TRUE,
@@
 options(scipen=999)
+
 ```
@@
 library(tableone)
+library(kableExtra)
 
@@
 # get data for table 1
- table1_data_new_infections  <- load(here("data", "table1_data_new_infections.Rda")))
+load(here("data", "table1_data_new_infections.Rda"))
 
@@
 
-```{r}
-
+```{r include=FALSE}
 table1.data<-rbind(  
@@
        table1_data_new_infections   %>%
-        mutate(group = "With COVID-19_infection"),
+        mutate(group = "COVID-19_infection"),
         table1_data_new_infections  %>%
         filter(long_covid == 1)%>%
-          mutate(group = "90 days Long Covid symtpoms"))
+          mutate(group = "Long Covid symptoms (90 days)"))
 
@@
 
-# format numbers (eg commas etc)  
-# functionality does not seem to be in tableone package
-# so do this manually
-for(i in 1:2) {
-# tidy up 
-  cur_column <- summary.characteristics[, i]
-  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
-                as.numeric() 
-  cur_column <-nice.num(cur_column)
-  # add back in
-  summary.characteristics[, i] <- str_replace(string=summary.characteristics.loss[, i], 
-                              pattern='[0-9.]+\\b', 
-                              replacement=cur_column)    
-}
+```
+
+## Table: Baseline characteristics of individuals with COVID-19 and with long COVID-19 
+```{r}
+
+kable(summary.characteristics, 
+      col.names = c("New COVID-19 infection",  
+                    "Long COVID-19, 90 days",
+                    "SMD"
+                    ))%>%
+  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
+ # pack_rows("Baseline comorbidities", 40, 44)
 
@@
 
+t.covid.confirmed <- generate_table(cohort_id= tested_positive_id,
+                                    window="90",
+                                    name = "Confirmed infections")
+
 t.covid.reinfections <- generate_table(cohort_id= "71",
@@
                                     name = "Reinfections")
-
-t.covid.confirmed <- generate_table(cohort_id= tested_positive_id,
-                                    window="90",
-                                    name = "Confirmed infections")
 
@@
 
+## Table: Symptoms distribution across cohorts
+
 ```{r}
-
 table  <- tbl_merge(tbls = list(t.covid.infection,   
+                                t.covid.confirmed,
                                 t.covid.reinfections,
@@
                                  ), 
-                     tab_spanner = c("", "", "", ""))
+                     tab_spanner = c("","", "", "", ""))
 
@@
 ```
-```{r}
-## explorar numero de sintomas en tested negative y covid infection
-# plot_grid(
-#   covid_infection_numb_symp %>% filter(window==90) %>% 
-#     ggplot(aes(all_symp)) +geom_bar() + theme_minimal() + ggtitle("Covid-19")  ,
-# tested_negative_all_numb_symp %>% filter(window==90) %>%
-#   ggplot(aes(all_symp)) +geom_bar() + theme_minimal() + ggtitle("Tested negative")
-# )
-
-```

### 2022-10-27 characterisation/Code/Create_data_Table1.R

@@ -41,6 +41,10 @@ cdm <- cdm_from_con(db,
              write_schema = write_schema,
              cohort_tables = c("er_long_covid_final_cohorts"))
 
+cohorts_ids  <- read.csv2(here("ATLAS Cohort Definitions_LongCovid.csv")) %>%
+                          mutate(name= paste(sub(".*LongCov-ER_", "", name)))
+
+
 ## cohrot of interest - first New Covid infections
 # main_cohort_interest <- cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == 22)
 # 90 days long Covid cohort
@@ -362,94 +366,23 @@ working_cohort
 }
 
 
-# main_cohort_interest <- cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == 22)
-# 90 days long Covid cohort
-# first two digits are for the "mother cohort"
-# digits 3,4 are for the symptoms cohort (99 is for any symptom") 
-# last two digits for window period
-# long_covid_cohort <- cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == 229990)
+# Get ids for cohorts of interest 
+# New infection
+main_cohort_id <- cohorts_ids %>%
+                    filter(str_detect(name, "New_Infection")) %>% 
+                    select(cohort_definition_id) %>% pull()
+# Symptoms - long Covid is 99
+symptom_id <- 99
+# time window of interest
+window_id <- 90
+
+long_covid_id <- main_cohort_id*10^4+symptom_id*10^2+window_id
+
 
 table1_data_new_infections <- generate_data_table1(
-  main_cohort_interest = cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == 22) ,
-  long_covid_cohort = cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == 229990))
+  main_cohort_interest = cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == main_cohort_id) ,
+  long_covid_cohort = cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == long_covid_id))
 
-table1.data<-rbind(  
-# those without missing values
-       table1_data_new_infections   %>%
-        mutate(group = "With COVID-19_infection"),
-        table1_data_new_infections  %>%
-        filter(long_covid == 1)%>%
-          mutate(group = "90 days Long Covid symtpoms"))
+save(table1_data_new_infections,
[…]

### 2022-10-27 characterisation/Code/Incidence_Rates.R

@@ -1,0 +1,6 @@
+### Incidence Rates of LOng COVID-19
+
+
+library(DBI)
+library(CDMConnector)
+library(IncidencePrevalence)

### 2022-10-27 characterisation/Code/Data_prep.R
Update Data_prep.R

@@ -951,8 +951,8 @@ symps_cohort <- bind_rows(list_cohorts[1]) %>%
   group_by(subject_id, cohort_start_date, window_days) %>%
   spread(name_var, symptom) %>%
     ungroup()  %>%
- mutate_at(c(5:27), ~replace_na(.,0))
-symps_cohort$all_symp<-rowSums(symps_cohort[,5:27],na.rm=T)
+ mutate_at(c(5:28), ~replace_na(.,0))
+symps_cohort$all_symp<-rowSums(symps_cohort[,5:28],na.rm=T)
 symps_cohort 
 }
 

### 2022-10-28 characterisation/Code/Comparing_symptoms.Rmd
update

@@
 ---
-title: "Exploring_symptoms_across_cohorts"
+title: "Descriptive characteristics of Long COVID Cohorts"
 output: html_document
@@
 # get data for table 1
-load(here("data", "table1_data_new_infections.Rda"))
+load(here("data", "table1_data.Rdata"))
 
@@
         "gender",
+        "trimester",
         "nationality_cat",
@@
         "gender",
+                "trimester",
         "nationality_cat",
@@
                     "Long COVID-19, 90 days",
+                    "SMD"
+                    ))%>%
+  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
+ # pack_rows("Baseline comorbidities", 40, 44)
+
+```
+
+```{r include=FALSE}
+table2.data<-rbind(  
+# those without missing values
+       table1_data_tested_negative   %>%
+        mutate(group = "1- Tested negative"),
+       table1_data_tested_negative   %>%
+        filter(long_covid == 1)%>%
+          mutate(group = "2- Long Covid symptoms (90 days)"))
+
+# variables
+vars<-c(
+        "age",
+        "age_gr2",
+        "gender",
+        "trimester",
+        "nationality_cat",
+        "vaccination_status",
+        "medea",
+        "asthma",
+        "autoimmune_disease",
+        "copd",
+        "dementia",
+        "diabetes",
+        "heart_disease",
+        "cancer",
+        "hypertension",
+        "renal_impairment"
+)
+
+factor.vars<- c(
+        "age_gr2",
+        "gender",
+                "trimester",
+        "nationality_cat",
+        "vaccination_status",
+        "medea",
+        "asthma",
+        "autoimmune_disease",
+        "copd",
+        "dementia",
+        "diabetes",
+        "heart_disease",
+        "cancer",
+        "hypertension",
+        "renal_impairment"
+)
+
+summary.characteristics.negative <-print(CreateTableOne(
+  vars =  vars,
+  factorVars = factor.vars,
+  includeNA=T,
+  data = table2.data,
+  strata=c("group"),
+  test = F), 
+  showAllLevels=F,
+  smd=T,
+  nonnormal = vars, #all 
+  noSpaces = TRUE,
+  contDigits = 1,
+  printToggle=FALSE)
+
+```
+
+## Table: Baseline characteristics of individuals tested negative and with long COVID-18 symptoms
+```{r}
+
+kable(summary.characteristics.negative, 
+      col.names = c("Tested negative, earliest",  
+                    "Long COVID-19 symptoms, 90 days",
+                    "SMD"
+                    ))%>%
+  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
+ # pack_rows("Baseline comorbidities", 40, 44)
+
+```
+
+```{r include=FALSE}
+table3.data<-rbind(  
+# those without missing values
+        table1_data_new_infections  %>%
+        mutate(group = "New infections"),
+        table1_data_tested_negative   %>%
+        mutate(group = "Tested negative"))
+
+# variables
+vars<-c(
+        "age",
+        "age_gr2",
+        "gender",
+        "trimester",
+        "nationality_cat",
+        "vaccination_status",
+        "medea",
+        "asthma",
+        "autoimmune_disease",
+        "copd",
+        "dementia",
+        "diabetes",
+        "heart_disease",
+        "cancer",
+        "hypertension",
+        "renal_impairment",
+                "long_covid"
+
+)
+
+factor.vars<- c(
+        "age_gr2",
+        "gender",
+                "trimester",
+        "nationality_cat",
+        "vaccination_status",
+        "medea",
+        "asthma",
+        "autoimmune_disease",
+        "copd",
+        "dementia",
+        "diabetes",
+        "heart_disease",
+        "cancer",
+        "hypertension",
+        "renal_impairment",
+        "long_covid"
+)
+
+summary.characteristics.infection.negative <-print(CreateTableOne(
+  vars =  vars,
+  factorVars = factor.vars,
+  includeNA=T,
+  data = table3.data,
+  strata=c("group"),
+  test = F), 
+  showAllLevels=F,
+  smd=T,
+  nonnormal = vars, #all 
+  noSpaces = TRUE,
+  contDigits = 1,
+  printToggle=FALSE)
+
+```
+
+## Table: Baseline characteristics of individuals tested negative and with long COVID-18 symptoms
+```{r}
+
+kable(summary.characteristics.infection.negative, 
+      col.names = c("New COVID-19 infection",  
+                    "Tested negative",
                     "SMD"

### 2022-10-28 characterisation/Code/Create_data_Table1.R

@@ -354,35 +354,59 @@ working_cohort <- working_cohort%>%
  ## we add long covid 90 days 
  working_cohort <- working_cohort %>%
    left_join( long_covid_cohort   %>% 
+                 distinct() %>%
                 select(-cohort_definition_id) %>%
                 mutate(long_covid = 1) %>%
                 rename(long_covid_date = cohort_end_date,
                       person_id = subject_id))  %>%
     mutate(long_covid=ifelse(is.na(long_covid),0,long_covid)) %>%
    distinct() %>%
+     mutate(year = lubridate::year(cohort_start_date),
+         month = lubridate::month(cohort_start_date)) %>%
+  mutate(trimester=ifelse(year==2020 & month<4, "1- Jan_Mar_2020", 
+                   ifelse(year==2020 & (month==4 | month==5| month==6), "2- Apr_Jun_2020", 
+                   ifelse(year==2020 & (month==7 | month==8| month==9), "3- Jul_Sep_2020",
+                   ifelse(year==2020 & month>9, "4- Oct_Dec_2020",
+                   ifelse(year==2021 & month<4, "5- Jan_Mar_2021",
+                   ifelse(year==2021 & (month==4 | month==5| month==6), "6- Apr_Jun_2021",
+                   ifelse(year==2021 & (month==7 | month==8| month==9), "7- Jul_Sep_2021",
+                   ifelse(year==2021 & month>9, "8- Oct_Dec_21", 
+                   NA))))))))) %>%
+  select(-year, -month) %>%
  collect()
  
 working_cohort
 }
 
-
-# Get ids for cohorts of interest 
-# New infection
-main_cohort_id <- cohorts_ids %>%
-                    filter(str_detect(name, "New_Infection")) %>% 
-                    select(cohort_definition_id) %>% pull()
+## Parameters ----
 # Symptoms - long Covid is 99
 symptom_id <- 99
 # time window of interest
 window_id <- 90
 
+# New COVID-19 infection ----- 
+main_cohort_id <- cohorts_ids %>%
+                    filter(str_detect(name, "New_Infection")) %>% 
+                    select(cohort_definition_id) %>% pull()
 long_covid_id <- main_cohort_id*10^4+symptom_id*10^2+window_id
-
 
 table1_data_new_infections <- generate_data_table1(
   main_cohort_interest = cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == main_cohort_id) ,
[…]

### 2022-10-28 characterisation/Code/Incidence_Rates.R

@@ -1,6 +1,328 @@
 ### Incidence Rates of LOng COVID-19
-
+remotes::install_github("darwin-eu/IncidencePrevalence")
 
 library(DBI)
 library(CDMConnector)
 library(IncidencePrevalence)
+library(dbplyr)
+library(dplyr)
+library(here)
+library(ggplot2)
+
+# Connection details ----
+server    <- Sys.getenv("SERVER_JUN22")
+server_dbi<- Sys.getenv("SERVER_DBI_JUN22")
+user      <- Sys.getenv("DB_USER_JUN22")
+password  <- Sys.getenv("DB_PASSWORD_JUN22")
+port      <- Sys.getenv("DB_PORT_JUN22") 
+host      <- Sys.getenv("DB_HOST_JUN22") 
+
+
+db <- dbConnect(RPostgres::Postgres(), 
+                dbname = server_dbi,
+                port = port,
+                host = host, 
+                user = user, 
+                password = password)
+
+targetDialect              <- "postgresql"
+cdm_database_schema        <- "omop21t4_cmbd" 
+vocabulary_database_schema <-"omop21t4_cmbd" 
+write_schema               <-"results21t4_cmbd"
+
+# Generate cdm object to access the tables
+cdm <- cdm_from_con(db, 
+             cdm_schema = cdm_database_schema,
+             write_schema = write_schema,
+             cohort_tables = c("er_long_covid_final_cohorts"
+                               ))
+
+
+# parameters ---- 
+study_start_date <- as.Date("01/03/2020", "%d/%m/%Y") # only needed for the gen pop denominator 
+study_end_date   <- as.Date("01/09/2021", "%d/%m/%Y")  # only needed for the gen pop denominator 
+study_days_prior_history <- 180  # only needed for the gen pop denominator 
+study_age_stratas <- list(c(18,110))
+study_age_stratas <- list(
+                         c(18,39), # only adults for this study
+                         c(40,64),
+                         c(65,79),
+                         c(80,110))
+study_sex_stratas <- c("Male", "Female")
+
+# Table in our CDM with study cohorts 
+study_cohorts <- "er_long_covid_final_cohorts"
+# ID cohorts 
+# Cohort 9 - C9: [Long COVID] 90d prior with 14d run-in 28d after
+
+# Id_TestNeg_cohort <- 
+get_ir <- function(  table_name_strata,
+                     strata_cohort_id,
+                     study_age_stratas,
[…]

### 2022-11-15 characterisation/Code/Comparing_symptoms.Rmd
update

@@
 
-knitr::opts_chunk$set(echo = TRUE,
+knitr::opts_chunk$set(echo = FALSE,
                       warning=FALSE, 
@@
                       comment = FALSE,
+                      cache = FALSE,
                       cache.lazy=FALSE)
@@
 library(kableExtra)
+library(ggplot2)
+library(forcats)
 
@@
                     filter(str_detect(name, "PCR_Negative_earliest")) %>% 
+                    select(cohort_definition_id) %>% pull())
+
+tested_negative_all_id <- as.character(cohorts_ids %>%
+                    filter(str_detect(name, "Tested_Negative_all")) %>% 
+                    select(cohort_definition_id) %>% pull())
+
+pcr_negative_all_id <-as.character( cohorts_ids %>%
+                    filter(str_detect(name, "PCR_Negative_all")) %>% 
                     select(cohort_definition_id) %>% pull())
@@
 
-summary.characteristics<-print(CreateTableOne(
+summary.characteristics <-print(CreateTableOne(
   vars =  vars,
@@
 ## Table: Baseline characteristics of individuals with COVID-19 and with long COVID-19 
-```{r}
+```{r echo=FALSE}
 
 kable(summary.characteristics, 
-      col.names = c("New COVID-19 infection",  
+      col.names = c("COVID-19 infection",  
                     "Long COVID-19, 90 days",
@@
 
-# variables
-vars<-c(
-        "age",
-        "age_gr2",
-        "gender",
-        "trimester",
-        "nationality_cat",
-        "vaccination_status",
-        "medea",
-        "asthma",
-        "autoimmune_disease",
-        "copd",
-        "dementia",
-        "diabetes",
-        "heart_disease",
-        "cancer",
-        "hypertension",
-        "renal_impairment"
-)
-
-factor.vars<- c(
-        "age_gr2",
-        "gender",
-                "trimester",
-        "nationality_cat",
-        "vaccination_status",
-        "medea",
-        "asthma",
-        "autoimmune_disease",
-        "copd",
-        "dementia",
-        "diabetes",
-        "heart_disease",
-        "cancer",
-        "hypertension",
-        "renal_impairment"
-)
-
 summary.characteristics.negative <-print(CreateTableOne(
@@
 
-## Table: Baseline characteristics of individuals tested negative and with long COVID-18 symptoms
+## Table: Baseline characteristics of individuals tested negative and with long COVID-19 symptoms
 ```{r}
@@
         table1_data_tested_negative   %>%
-        mutate(group = "Tested negative"))
-
-# variables
-vars<-c(
-        "age",
-        "age_gr2",
-        "gender",
-        "trimester",
-        "nationality_cat",
-        "vaccination_status",
-        "medea",
-        "asthma",
-        "autoimmune_disease",
-        "copd",
-        "dementia",
-        "diabetes",
-        "heart_disease",
-        "cancer",
-        "hypertension",
-        "renal_impairment",
-                "long_covid"
-
-)
-
-factor.vars<- c(
-        "age_gr2",
-        "gender",
-                "trimester",
-        "nationality_cat",
-        "vaccination_status",
-        "medea",
-        "asthma",
-        "autoimmune_disease",
-        "copd",
-        "dementia",
-        "diabetes",
-        "heart_disease",
-        "cancer",
-        "hypertension",
-        "renal_impairment",
-        "long_covid"
+        mutate(group = "Tested negative"),
+        table1_data_tested_negative_all   %>%
+        mutate(group = "Tested negative, all")
         )
@@
 
-## Table: Baseline characteristics of individuals tested negative and with long COVID-18 symptoms
-```{r}
+## Table: Baseline characteristics of individuals with new COVID-19 infection and Tested negative (earliest)
+```{r echo=FALSE}
 
 kable(summary.characteristics.infection.negative, 
-      col.names = c("New COVID-19 infection",  
-                    "Tested negative",
+      col.names = c("COVID-19 infection",  
+                    "Tested negative, earliest",
+                    "Tested negative, all events",
                     "SMD"
@@
   bold_labels()
+
   summary
@@
                                     window="90",
-                                    name = "New COVID-19 infection")
+                                    name = "COVID-19 infection")
 
@@
                                     window="90",
-                                    name = "Confirmed infections")
+                                    name = "Laboratory-confirmed infections")
 
@@
 
+t.tested.negative.all <- generate_table(cohort_id = tested_negative_all_id,
+                                    window="90",
+                                    name = "Tested negative, all")
+
 t.pcr.negative.earliest <- generate_table(cohort_id = pcr_negative_earliest_id,
@@
                                     name = "PCR negative, earliest")
+t.pcr.negative.all <- generate_table(cohort_id = pcr_negative_all_id,
+                                    window="90",
+                                    name = "PCR negative, all")
 
@@
 
-## Table: Symptoms distribution across cohorts
-
-```{r}
+## Table: Symptom distribution across cohorts
+```{r echo=FALSE}
 table  <- tbl_merge(tbls = list(t.covid.infection,   
@@
                                 t.tested.negative.earliest,
-                                t.pcr.negative.earliest
+                                 t.tested.negative.all,
+                                t.pcr.negative.earliest,
+                                 t.pcr.negative.all
                                  ), 
-                     tab_spanner = c("","", "", "", ""))
+                     tab_spanner = c("","", "", "", "", "", ""))
 
@@
 ```
+
+## Figure: Heatmap of symptoms distribution across cohorts
+```{r include=FALSE}
+get_prop <- function(data){
+  filt <- c("1","2","3","4","5","6","7","8","9","10","11", "__all_symp__")
+  output <- as_tibble(data,  col_labels = FALSE) %>%
+  filter(!(label %in% filt)) %>%
+ mutate(prop = str_extract(stat_1, "(?<=\\()(.*?)%")) %>%
+  mutate(prop= substring(prop,1, nchar(prop)-1)) %>%
+  mutate(prop = as.numeric(prop)) %>%
+  select(-stat_1) %>%
+  mutate(label= substring(label,1, nchar(label)-2)) %>%
+  mutate(label= substring(label,3)) %>%
+  as.data.frame()
+}
+
+results <- rbind(
+  get_prop(t.covid.infection) %>%  mutate(group = "COVID-19\n infection"),
+  get_prop(t.covid.confirmed) %>%  mutate(group = "Laboratory-confirmed\nCOVID-19 infections"),
+  get_prop(t.covid.reinfections) %>% mutate(group = "Reinfections"),
+  get_prop(t.tested.negative.earliest) %>% mutate(group = "Tested negative,\n earliest"),
+  get_prop( t.tested.negative.all) %>% mutate(group = "Tested negative ,\n all"),
+  get_prop( t.pcr.negative.earliest) %>% mutate(group = "Tested negative (PCR only),\n earliest"),
+  get_prop( t.pcr.negative.all) %>% mutate(group = "Tested negative (PCR only),\n all")
+ ) %>%
+  mutate(label = str_replace_all(label, "_", " ")) %>%
+  mutate(label = str_to_title(label))
+
+```
+
+```{r echo=FALSE}
+results %>% 
+    mutate(label = fct_rev(factor(label))) %>%
+  ggplot() +
+  aes(x = 1, y = label, fill = prop) +
+  facet_grid(~group)+
+  geom_tile(colour = "black") +
+  scale_fill_gradient(high = "#C81D25", low = "#E4F1EB")+
+  geom_text(aes(label = round(prop, 1))) +
+  theme_minimal() +
+  theme(axis.text.x=element_blank(),
+        legend.position = "bottom")+
+  xlab("")+
+  ylab("Symptom")+
+  labs(fill= "Proportion, in %")
+
+```

### 2022-11-15 characterisation/Code/Comparing_symptoms_matched.Rmd
update

---
title: "Descriptive characteristics, matched"
output: html_document
---
---
title: "Descriptive characteristics of Long COVID Cohorts"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      warning=FALSE, 
                      message=FALSE, 
                      comment = FALSE,
                      cache = FALSE,
                      cache.lazy=FALSE)
options(scipen=999)

```

```{r include=FALSE}
# packages
library(SqlRender)
library(DBI)
library(DatabaseConnector)
library(here)
library(dplyr)
library(tidyr)
library(CDMConnector)
library(stringr)
library(lubridate)
library(gtsummary)
library(tableone)
library(kableExtra)
library(ggplot2)
library(forcats)
library(tsibble)
library(MatchIt)
library(survey)

# get data for table 1
filtering_date <- as.Date("2020-09-01", "%Y-%m-%d")
load(here("data", "table1_data.Rdata"))
load(here("data", "table1_data_matched.Rdata"))

```

```{r include=FALSE}
# variables for Table 1 
vars<-c(
        "age",
        "age_gr2",
        "gender",
        "trimester",
        "vaccination_status",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment",
        "long_covid"
)

factor.vars<- c(
        "age_gr2",
        "gender",
        "trimester",
        "vaccination_status",
        "asthma",
        "autoimmune_disease",
        "copd",
        "dementia",
        "diabetes",
        "heart_disease",
        "cancer",
        "hypertension",
        "renal_impairment",
        "long_covid"
)

```

# Baseline characteristics 
```{r}
table1.data<-rbind(  
# those without missing values
       table1_data_new_infections   %>%
        mutate(group = "1 COVID-19 infection"),
      table1_data_confirmed_infection  %>%
        mutate(group = "2 Confirmed infection"),
      table1_data_first_infection %>%
        mutate(group = "3 First infection"),
       table1_data_reinfections  %>%
        mutate(group = "4 Reinfections"),
        table1_data_tested_negative_earliest  %>%
        mutate(group = "5 Tested negative, earliest"),
      table1_data_tested_negative_all %>%
        mutate(group = "6 Tested negative, all "),
        table1_data_pcr_negative_earliest  %>%
        mutate(group = "7 PCR negative, earliest "),
         table1_data_pcr_negative_all  %>%
        mutate(group = "8 PCR negative, all ")) %>%
  filter(cohort_start_date >=filtering_date)

summary.characteristics <-print(CreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = table1.data,
  strata=c("group"),
  test = F), 
  showAllLevels=F,
  smd=F,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)

```

```{r}
kable(summary.characteristics,
        col.names = c( "COVID-19 infection",
        "Confirmed infection",
        "First infection",
        "Reinfections",
        "Tested negative, earliest",
        "Tested negative, all ",
        "PCR negative, earliest ",
        "PCR negative, all "
                    ))%>%
  kable_styling(bootstrap_options = c("striped", "bordered"))

```

## New COVID-19 infection vs Tested negative (earliest event), after matching by week/year of testing and 5y age group
```{r include=FALSE}
data <- m.new_covid_tested_negative_earliest[[3]]

summary.characteristics_covid_negative <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)

```

```{r}

kable(summary.characteristics_covid_negative)%>%
  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
 # pack_rows("Baseline comorbidities", 40, 44)

```

## Confirmed infections vs tested negative (earliest), after matching by week/year of testing and 5y age group
```{r}
data <- m.confirmed_infection_negative_earliest[[3]]

summary.characteristics.confirmed<-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)

```

```{r}
kable(summary.characteristics.confirmed
     )%>%
  kable_styling(bootstrap_options = c("striped", "bordered"))

```

## First infections vs reinfections, after matching by week/year of testing and 5y age group

```{r include=FALSE}
data <- m.first_infection_reinfections[[3]]

summary.characteristics.reinfections<-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)

```

```{r echo=FALSE}

kable(summary.characteristics.reinfections 
     )%>%
  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
 # pack_rows("Baseline comorbidities", 40, 44)

```

```{r Old_function_matching, eval=FALSE, include=FALSE}
# matched_table_symptom_cohorts <- function(cohort_id1, cohort_id2, window, name1, name2){
#  results_list <- list()
#  
#   cohort1 <- cdm$er_long_covid_all_symptoms_cohorts %>%
#   filter(main_cohort_id == cohort_id1 & window_days == window) %>%
#   mutate(name = name1) %>%
#   mutate(cohort = "0") %>% 
#   distinct() %>%
#   collect()
# 
#   cohort2 <- cdm$er_long_covid_all_symptoms_cohorts %>%
#   filter(main_cohort_id == cohort_id2 & window_days == window) %>%
#    mutate(name = name2) %>%
#       mutate(cohort = "1") %>%
#   distinct() %>%
#   collect()
# 
#   data <- rbind(cohort1 , cohort2) %>% mutate(week_year = yearweek(as.Date(cohort_start_date)))
# # we match by week and year using exact method 
# m.week_year <- matchit(cohort ~ week_year, data = data, method = "exact")
# sum_matching <- summary(m.week_year)
# # we extract matched data
# m.data <- match.data(m.week_year) %>%
#   rename(ps_weights= weights) %>%
#     mutate(all_symp = as.factor(all_symp)) %>%
#   select(-subject_id, -window_days, - cohort_start_date , -week_year, -main_cohort_id, -cohort) 
# 
# s.data <- svydesign(ids = ~subclass, # clusters 
#           data = m.data, 
#           weights= ~ps_weights) # weights
# 
# summary <-  s.data%>% 
#    tbl_svysummary(
#        by = "cohort",
#   digits = all_categorical()~ c(0,1),
#   missing = "ifany",
#   missing_text= "Missing",
#   percent = "col"
#            ) %>% 
#   bold_labels()
# 
# results_list <- list(sum_matching, m.data, s.data,   summary)
# results_list
# }
# t.first.infections.reinfections <- matched_table_symptom_cohorts(cohort_id1= "70", name1= "First COVID-19 infection",
#                                                            cohort_id2 = "71", name2 = "Reinfections", 
#                                                            window="90")
# 
# 
# t.infections.tested.negative <- matched_table_symptom_cohorts(cohort_id1= "22", name1= "New COVID-19 infection",
#                                                            cohort_id2 = "30", name2 = "Tested negative, earliest", 
#                                                            window="90")

```

# 90 days Long Covid symptoms distribution
```{r}
vars <- c("abdominal_pain", "allergy", "altered_smell_taste",  "anxiety" , 
         "blurred_vision","chest_pain" ,"cognitive_dysfunction_brain_fog", "cough" ,"depression" ,
         "dizziness" ,"dyspnea" , "fatigue_malaise" , "gastrointestinal_issues","headache" ,"intermittent_fever" ,
         "joint_pain" ,  "memory_issues_v2" ,"menstrual_problems" , "muscle_spams_pain", "neuralgia" , "pins_sensation",  
         "sleep_disorder", "tachycardia" ,"tinnitus_hearing_problems")

factor.vars <- c("abdominal_pain", "allergy", "altered_smell_taste",  "anxiety" , 
         "blurred_vision","chest_pain" ,"cognitive_dysfunction_brain_fog", "cough" ,"depression" ,
         "dizziness" ,"dyspnea" , "fatigue_malaise" , "gastrointestinal_issues","headache" ,"intermittent_fever" ,
         "joint_pain" ,  "memory_issues_v2" ,"menstrual_problems" , "muscle_spams_pain", "neuralgia" , "pins_sensation",  
         "sleep_disorder", "tachycardia" ,"tinnitus_hearing_problems")

```

```{r include=FALSE}
# function to get data for the plot
get_prop <- function(data){
  filt <- c("1","2","3","4","5","6","7","8","9","10","11", "__all_symp__")
  names <- names(as_tibble(data,  col_labels = T)) 
  names <- str_extract(names, "\\*(.*)\\*")
  names <- str_sub(names, 3)
  names <- str_sub(names, end=-3)

  output <- as_tibble(data,  col_labels = F) %>%
   filter(!(label %in% filt)) %>%
    mutate(prop1 = str_extract(stat_1, "(?<=\\()(.*?)%")) %>%
    mutate(prop1= substring(prop1,1, nchar(prop1)-1)) %>%
  mutate(prop1 = as.numeric(prop1)) %>%
  select(-stat_1) %>%
     mutate(prop2 = str_extract(stat_2, "(?<=\\()(.*?)%")) %>%
  mutate(prop2= substring(prop2,1, nchar(prop2)-1)) %>%
  mutate(prop2 = as.numeric(prop2)) %>%
      select(-stat_2) %>%
  mutate(label= substring(label,1, nchar(label)-2)) %>%
  mutate(label= substring(label,3)) %>%
  mutate(label = str_replace_all(label, "_", " ")) %>%
  mutate(label = str_to_title(label)) %>%
  as.data.frame()

  names(output) <- names
  output
}

# plot function
function_matched_heatmap <- function(data){
 plot <-  data %>% 
  pivot_longer(!Characteristic, names_to = "Cohort", values_to = "Proportion") %>%
  mutate(Characteristic = fct_rev(factor(Characteristic))) %>%
  ggplot() +
  aes(x = 1, y = Characteristic, fill = Proportion) +
  facet_grid(~Cohort)+
  geom_tile(colour = "black") +
  scale_fill_gradient(high = "#C81D25", low = "#E4F1EB")+
  geom_text(aes(label= round(Proportion, 1))) +
  theme_minimal() +
  theme(axis.text.x=element_blank(),
        legend.position = "bottom")+
  xlab("")+
  ylab("Symptom")+
  labs(fill= "Proportion, in %")
 plot
}

```

## Matched New COVID-19 infection vs Tested negative (earliest record) cohorts
```{r echo=FALSE}

data <- m.new_covid_tested_negative_earliest[[2]] %>% filter(long_covid == 1) 
data <- data %>% 
  select(name, abdominal_pain, allergy, altered_smell_taste,  anxiety , 
         blurred_vision ,chest_pain ,cognitive_dysfunction_brain_fog, cough ,depression ,
         dizziness ,dyspnea , fatigue_malaise , gastrointestinal_issues,headache ,intermittent_fever ,
         joint_pain  ,  memory_issues_v2 ,menstrual_problems , muscle_spams_pain, neuralgia , pins_sensation,  
         sleep_disorder , tachycardia ,tinnitus_hearing_problems,  all_symp, ps_weights, matched_pair  )

s.data <- svydesign(ids = ~matched_pair,  
          data = data, 
          weights= ~ps_weights) # weights all 1

summary.characteristics_symptoms <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = s.data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)

```

```{r}
kable(summary.characteristics_symptoms
     )%>%
  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
 # pack_rows("Baseline comorbidities", 40, 44)
```

## Heatmap

```{r eval=FALSE, include=FALSE}
results <-  get_prop(summary_new_covid_tested_negative) 
function_matched_heatmap(results)

```

## Matched Confirmed infection vs tested negative (earliest)
```{r}
data <- m.confirmed_infection_negative_earliest[[2]] %>% filter(long_covid == 1)
data <- data %>% 
  select(name, abdominal_pain, allergy, altered_smell_taste,  anxiety , 
         blurred_vision ,chest_pain ,cognitive_dysfunction_brain_fog, cough ,depression ,
         dizziness ,dyspnea , fatigue_malaise , gastrointestinal_issues,headache ,intermittent_fever ,
         joint_pain  ,  memory_issues_v2 ,menstrual_problems , muscle_spams_pain, neuralgia , pins_sensation,  
         sleep_disorder , tachycardia ,tinnitus_hearing_problems,  all_symp, ps_weights, matched_pair  )

s.data <- svydesign(ids = ~matched_pair,  
          data = data, 
          weights= ~ps_weights) # weights all 1

summary.characteristics_symptoms <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = s.data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)
```

```{r}
kable(summary.characteristics_symptoms
     )%>%
  kable_styling(bootstrap_options = c("striped", "bordered"))
```

```{r eval=FALSE, include=FALSE}
data <- m.confirmed_infection_negative_earliest[[2]] %>% filter(long_covid == 1)
# keep only variables of interest
data <- data %>% 
  select(name, abdominal_pain, allergy, altered_smell_taste,  anxiety , 
         blurred_vision ,chest_pain ,cognitive_dysfunction_brain_fog, cough ,depression ,
         dizziness ,dyspnea , fatigue_malaise , gastrointestinal_issues,headache ,intermittent_fever ,
         joint_pain  ,  memory_issues_v2 ,menstrual_problems , muscle_spams_pain, neuralgia , pins_sensation,  
         sleep_disorder , tachycardia ,tinnitus_hearing_problems,  all_symp, ps_weights, matched_pair  )

s.data <- svydesign(ids = ~matched_pair, # clusters 
          data = data, 
          weights= ~ps_weights) # weights

summary_confirmed_infection_tested_negative_earliest <-  s.data%>%
   tbl_svysummary(
       by = "name",
  digits = all_categorical()~ c(0,1),
  missing = "ifany",
  missing_text= "Missing",
  percent = "col"
           ) %>%
  bold_labels()

summary_confirmed_infection_tested_negative_earliest 
```

## Heatmap
```{r eval=FALSE, include=FALSE}
results <-  get_prop(summary_confirmed_infection_tested_negative_earliest ) 
function_matched_heatmap(results)
```

## Matched First COVID-19 infection vs Reinfection cohorts
```{r}
data <- m.first_infection_reinfections[[2]] %>% filter(long_covid == 1)
data <- data %>% 
  select(name, abdominal_pain, allergy, altered_smell_taste,  anxiety , 
         blurred_vision ,chest_pain ,cognitive_dysfunction_brain_fog, cough ,depression ,
         dizziness ,dyspnea , fatigue_malaise , gastrointestinal_issues,headache ,intermittent_fever ,
         joint_pain  ,  memory_issues_v2 ,menstrual_problems , muscle_spams_pain, neuralgia , pins_sensation,  
         sleep_disorder , tachycardia ,tinnitus_hearing_problems,  all_symp, ps_weights, matched_pair  )

s.data <- svydesign(ids = ~matched_pair,  
          data = data, 
          weights= ~ps_weights) # weights all 1

summary.characteristics_symptoms <-print(svyCreateTableOne(
  vars =  vars,
  factorVars = factor.vars,
  includeNA=T,
  data = s.data,
  strata=c("name"),
  test = F), 
  showAllLevels=F,
  smd=T,
  nonnormal = vars, #all 
  noSpaces = TRUE,
  contDigits = 0,
  printToggle=FALSE)

```

```{r}
kable(summary.characteristics_symptoms
     )%>%
  kable_styling(bootstrap_options = c("striped", "bordered"))
```

## Heatmap
```{r eval=FALSE, include=FALSE}
results <-  get_prop(summary_first_infection_reinfections ) 
function_matched_heatmap(results)
```

### 2022-11-15 characterisation/Code/Code_to_Run.R

@@ -1,0 +1,105 @@
+
+# packages
+if (!require("pacman")) install.packages("pacman")
+library(pacman)
+
+
+
+
+
+p_load(SqlRender,
+       DBI,
+       DatabaseConnector,
+       CohortGenerator,
+       CohortDiagnostics,
+       here,
+       tidyr,
+       dplyr,
+       dbplyr,
+       CDMConnector,
+       stringr,
+       lubridate,
+       MatchIt,
+       tsibble,
+       survey,
+       CirceR,
+       lubridate,
+       MatchIt,
+       tsibble,
+       survey)
+
+# library(here)
+# library(SqlRender)
+# library(DBI)
+# library(DatabaseConnector)
+# library(CohortGenerator)
+# library(CohortDiagnostics)
+# library(dplyr)
+# library(dbplyr)
+# library(tidyr)
+# library(CDMConnector)
+# library(stringr)
+# library(CirceR)
+# library(lubridate)
+# library(MatchIt)
+# library(tsibble)
+# library(survey)
+
+
+# Connection details ----
+server    <- Sys.getenv("SERVER_JUN22")
+server_dbi<- Sys.getenv("SERVER_DBI_JUN22")
+user      <- Sys.getenv("DB_USER_JUN22")
+password  <- Sys.getenv("DB_PASSWORD_JUN22")
+port      <- Sys.getenv("DB_PORT_JUN22") 
+host      <- Sys.getenv("DB_HOST_JUN22") 
+
+targetDialect              <- "postgresql"
+cdm_database_schema        <- "omop21t4_cmbd" 
+vocabulary_database_schema <- "omop21t4_cmbd" 
+# this is the schema to save results in the database
+write_schema               <- "results21t4_cmbd"
+
+
+db <- dbConnect(RPostgres::Postgres(), 
+                dbname = server_dbi,
+                port = port,
+                host = host, 
+                user = user, 
+                password = password)
+
+## we also cuse connection details to insert later tables using OHDSI  tools
+connectionDetails <-DatabaseConnector::downloadJdbcDrivers("postgresql", here::here())
+connectionDetails <- DatabaseConnector::createConnectionDetails(dbms = "postgresql",
+                                                                server =server,
+                                                                user = user,
+                                                                password = password,
+                                                                port = port ,
+                                                                pathToDriver = here::here())
+
[…]

### 2022-11-15 characterisation/Code/Run_Analysis.R

@@ -1,0 +1,1686 @@
+# Tables in the write_schema to save Inital Json cohorts
+cohortTableJsons <-"er_cohorts_for_longcov"
+
+
+# create results folder if needed
+cohorts.folder <- here::here("results")
+if (!file.exists(cohorts.folder)){
+  dir.create(cohorts.folder)
+}
+
+# create data folder if needed
+cohorts.folder <- here::here("data")
+if (!file.exists(cohorts.folder)){
+  dir.create(cohorts.folder)
+}
+
+
+# Initial Json cohorts ----
+if(create_initial_json_cohorts=="FALSE"){
+print(paste0("- Skipping creating initial json cohorts"))
+} else { 
+print(paste0("- Creating initial json cohorts"))
+
+
+### Get cohort details -----
+ cohortJsonFiles <- list.files(here("Cohort_Dx_initial","1_InstantiateCohorts", "Cohorts"))
+cohortJsonFiles <- cohortJsonFiles[str_detect(cohortJsonFiles,".json")]
+
+cohortDefinitionSet <- list()
+for(i in 1:length(cohortJsonFiles)){
+working.json<-here("Cohort_Dx_initial","1_InstantiateCohorts", "Cohorts",
+                      cohortJsonFiles[i])
+cohortJson <- readChar(working.json, file.info(working.json)$size)
+cohortExpression <- cohortExpressionFromJson(cohortJson) # generates the sql
+sql <- buildCohortQuery(cohortExpression, 
+                   options = CirceR::createGenerateOptions(generateStats = TRUE))
+
+cohortDefinitionSet[[i]]<-tibble(atlasId = i,
+      cohortId = i,
+      cohortName = str_replace(cohortJsonFiles[i],".json",""),
+      json=cohortJson,
+      sql=sql,
+      logicDescription = NA,
+      generateStats=TRUE)
+}
+cohortDefinitionSet<-bind_rows(cohortDefinitionSet)
+
+# Names of tables to be created during study run ----- 
+cohortTableNames <- CohortGenerator::getCohortTableNames(cohortTable = cohortTableJsons)
+
+# Create the tables in the database -----
+CohortGenerator::createCohortTables(connectionDetails = connectionDetails,
+                                    cohortTableNames = cohortTableNames,
+                                    cohortDatabaseSchema = write_schema)
+
+# Generate the cohort set -----
+CohortGenerator::generateCohortSet(connectionDetails= connectionDetails,
[…]

### 2022-11-15 characterisation/Code/Comparing_symptoms.Rmd
update

@@
 # packages
-library(SqlRender)
-library(DBI)
-library(DatabaseConnector)
-library(here)
-library(dplyr)
-library(tidyr)
-library(CDMConnector)
-library(stringr)
-library(lubridate)
-library(gtsummary)
-library(tableone)
-library(kableExtra)
-library(ggplot2)
-library(forcats)
+if (!require("pacman")) install.packages("pacman")
+library(pacman)
+
+p_load(SqlRender,
+       DBI,
+       here,
+       tidyr,
+       dplyr,
+       dbplyr,
+       CDMConnector,
+       stringr,
+       lubridate,
+       tableone,
+       kableExtra,
+       ggplot2,
+       forcats,
+       gtsummary)
 
 # Connection details ----
-server    <- Sys.getenv("SERVER_JUN22")
-server_dbi<- Sys.getenv("SERVER_DBI_JUN22")
-user      <- Sys.getenv("DB_USER_JUN22")
-password  <- Sys.getenv("DB_PASSWORD_JUN22")
-port      <- Sys.getenv("DB_PORT_JUN22") 
-host      <- Sys.getenv("DB_HOST_JUN22")
-
-db <- dbConnect(RPostgres::Postgres(), 
-                dbname = server_dbi,
-                port = port,
-                host = host, 
-                user = user, 
-                password = password)
-
-targetDialect              <- "postgresql"
-cdm_database_schema        <- "omop21t4_cmbd" 
-vocabulary_database_schema <-"omop21t4_cmbd" 
-write_schema               <-"results21t4_cmbd"
-
+source("Code_to_Run.R", local = knitr::knit_global())
 # Generate cdm object to access the tables
@@
 #  get ids for cohorts
-
 cohorts_ids  <- read.csv2(here("ATLAS Cohort Definitions_LongCovid.csv")) %>%
@@
   noSpaces = TRUE,
-  contDigits = 1,
+  contDigits = 0,
+  catDigits = 0,
   printToggle=FALSE)
@@
                     ))%>%
-  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
- # pack_rows("Baseline comorbidities", 40, 44)
+  kable_styling(bootstrap_options = c("striped", "bordered"))
 

### 2022-11-15 characterisation/Code/Comparing_symptoms_matched.Rmd
update

@@
 ---
-title: "Descriptive characteristics, matched"
-output: html_document
----
----
-title: "Descriptive characteristics of Long COVID Cohorts"
+title: "Descriptive characteristics of Long COVID cohrots, matched"
 output: html_document
@@
 # packages
-library(SqlRender)
-library(DBI)
-library(DatabaseConnector)
 library(here)
@@
 library(tidyr)
-library(CDMConnector)
 library(stringr)
@@
 library(tsibble)
-library(MatchIt)
 library(survey)
@@
 # get data for table 1
-filtering_date <- as.Date("2020-09-01", "%Y-%m-%d")
+# get full testing_start from Code to Run
+# source("Code_to_Run.R", local = knitr::knit_global())
+full_testing_start_date <- as.Date("2020-09-01", "%Y-%m-%d")
+
 load(here("data", "table1_data.Rdata"))
@@
         mutate(group = "8 PCR negative, all ")) %>%
-  filter(cohort_start_date >=filtering_date)
+  filter(cohort_start_date >=full_testing_start_date)
 
@@
   contDigits = 0,
+  catDigits = 0,
   printToggle=FALSE)
@@
 kable(summary.characteristics,
-        col.names = c( "COVID-19 infection",
+        col.names = c(
+        "COVID-19 infection",
         "Confirmed infection",
@@
   noSpaces = TRUE,
+  catDigits = 0,
   contDigits = 0,
@@
 kable(summary.characteristics_covid_negative)%>%
-  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
- # pack_rows("Baseline comorbidities", 40, 44)
+  kable_styling(bootstrap_options = c("striped", "bordered"))
 
@@
   contDigits = 0,
+   catDigits = 0,
   printToggle=FALSE)

### 2022-11-15 characterisation/Code/Code_to_Run.R

@@ -21,11 +21,7 @@ p_load(SqlRender,
        lubridate,
        MatchIt,
        tsibble,
-       survey,
        CirceR,
-       lubridate,
-       MatchIt,
-       tsibble,
        survey)
 
 # library(here)
@@ -85,15 +81,17 @@ influenza_start_date<- as.Date("2019-12-01", "%Y-%m-%d")
 # for symptoms, we only need symptoms occurring during covid + 180 days washout
 symptoms_start_date <- as.Date("2019-08-29","%Y-%m-%d")
 end_index_date      <- as.Date("2021-09-02", "%Y-%m-%d")
-# 
+# for filtering some results 
 full_testing_start_date <- as.Date("2020-09-01", "%Y-%m-%d")
 
 # Create initial Json cohorts ---- 
-create_initial_json_cohorts <- FALSE
+create_initial_json_cohorts     <- TRUE
 # Crate Long Covid  cohorts and save in the db
-create_long_covid_cohorts <- TRUE
+create_long_covid_cohorts       <- TRUE
 # Generate data for descritpive tables and save locally
-generate_data_descriptive_table <- FALSE
+generate_data_descriptive_table <- TRUE
+# Generate Html with results files
+generate_results                <- TRUE
 
 
 # Window for long COvid - 90 or 28
@@ -101,5 +99,6 @@ window_id <- 90
 
 # Run analysis
 source(here("Code/Run_Analysis.R"))
+
 
 # Results script

### 2022-11-15 characterisation/Code/Create_data_Table1.R

@@ -1,412 +1,0 @@
-##  CHaracteristing Long COVID ### 
-# Getting  TABLE 1-  Comparing characteristics of Covid cases vs Long Covid 
-
-# packages
-library(SqlRender)
-library(DBI)
-library(DatabaseConnector)
-library(here)
-library(dplyr)
-library(tidyr)
-library(CDMConnector)
-library(stringr)
-library(lubridate)
-library(tableone)
-
-
-# Connection details ----
-server    <- Sys.getenv("SERVER_JUN22")
-server_dbi<- Sys.getenv("SERVER_DBI_JUN22")
-user      <- Sys.getenv("DB_USER_JUN22")
-password  <- Sys.getenv("DB_PASSWORD_JUN22")
-port      <- Sys.getenv("DB_PORT_JUN22") 
-host      <- Sys.getenv("DB_HOST_JUN22") 
-
-
-db <- dbConnect(RPostgres::Postgres(), 
-                dbname = server_dbi,
-                port = port,
-                host = host, 
-                user = user, 
-                password = password)
-
-targetDialect              <- "postgresql"
-cdm_database_schema        <- "omop21t4_cmbd" 
-vocabulary_database_schema <-"omop21t4_cmbd" 
-write_schema               <-"results21t4_cmbd"
-
-# Generate cdm object to access the tables
-cdm <- cdm_from_con(db, 
-             cdm_schema = cdm_database_schema,
-             write_schema = write_schema,
-             cohort_tables = c("er_long_covid_final_cohorts"))
-
-cohorts_ids  <- read.csv2(here("ATLAS Cohort Definitions_LongCovid.csv")) %>%
-                          mutate(name= paste(sub(".*LongCov-ER_", "", name)))
-
-
-## cohrot of interest - first New Covid infections
-# main_cohort_interest <- cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == 22)
-# 90 days long Covid cohort
-# first two digits are for the "mother cohort"
-# digits 3,4 are for the symptoms cohort (99 is for any symptom") 
-# last two digits for window period
-# long_covid_cohort <- cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == 229990)
-
-
-# Function to get the data for the table 
-generate_data_table1 <- function(main_cohort_interest, long_covid_cohort){
-working_cohort <- main_cohort_interest %>% 
- rename(person_id=subject_id) %>%
-  left_join(cdm$person  %>%
[…]

### 2022-11-15 characterisation/Code/Data_prep.R

@@ -1,1123 +1,0 @@
-
-# packages
-library(SqlRender)
-library(DBI)
-library(DatabaseConnector)
-library(here)
-library(dplyr)
-library(dbplyr)
-library(tidyr)
-library(CDMConnector)
-library(stringr)
-
-
-# Connection details ----
-server    <- Sys.getenv("SERVER_JUN22")
-server_dbi<- Sys.getenv("SERVER_DBI_JUN22")
-user      <- Sys.getenv("DB_USER_JUN22")
-password  <- Sys.getenv("DB_PASSWORD_JUN22")
-port      <- Sys.getenv("DB_PORT_JUN22") 
-host      <- Sys.getenv("DB_HOST_JUN22") 
-
-
-db <- dbConnect(RPostgres::Postgres(), 
-                dbname = server_dbi,
-                port = port,
-                host = host, 
-                user = user, 
-                password = password)
-
-## we also cuse connection details to insert later tables using OHDSI  tools
-connectionDetails <-DatabaseConnector::downloadJdbcDrivers("postgresql", here::here())
-connectionDetails <- DatabaseConnector::createConnectionDetails(dbms = "postgresql",
-                                                                server =server,
-                                                                user = user,
-                                                                password = password,
-                                                                port = port ,
-                                                                pathToDriver = here::here())
-    
- 
-targetDialect              <- "postgresql"
-cdm_database_schema        <- "omop21t4_cmbd" 
-vocabulary_database_schema <- "omop21t4_cmbd" 
-write_schema               <- "results21t4_cmbd"
-
-# cdm object to access the tables easily
-cdm <- cdm_from_con(db, 
-             cdm_schema = cdm_database_schema,
-             write_schema = write_schema,
-             cohort_tables = c("er_cohorts_for_longcov"))
-
-# create results folder if needed
-cohorts.folder <- here::here("results")
-if (!file.exists(cohorts.folder)){
-  dir.create(cohorts.folder)
-}
-
-# parameters ----
-# to get rid of covid diagnoses captured before the start of the pandemic --
-# first case in Catalonia - 25 February 2020
-covid_start_date    <- as.Date("2020-02-25", "%Y-%m-%d")
-# we are not interested in old influenza diagnosis - so we can filter these
-influenza_start_date<- as.Date("2019-12-01", "%Y-%m-%d")
[…]

### 2022-11-15 characterisation/Code/Run_Analysis.R

@@ -1062,14 +1062,14 @@ change_any_symptom_date <- function(data){
   data
 }
 
-covid_infection_any_symp          <- change_any_symptom_date( covid_infection_any_symp)
-first_infection_any_symp          <- change_any_symptom_date( first_infection_any_symp)
-confirmed_infection_any_symp      <- change_any_symptom_date( confirmed_infection_any_symp)
-reinfections_any_symp             <- change_any_symptom_date( reinfections_any_symp)
-tested_negative_earliest_any_symp <- change_any_symptom_date( tested_negative_earliest_any_symp)
-tested_negative_all_any_symp      <- change_any_symptom_date( tested_negative_all_any_symp)
-PCR_negative_earliest_any_symp    <- change_any_symptom_date( PCR_negative_earliest_any_symp)
-PCR_negative_all_any_symp         <- change_any_symptom_date( PCR_negative_all_any_symp)
+covid_infection_any_symp          <- change_any_symptom_date(covid_infection_any_symp)
+first_infection_any_symp          <- change_any_symptom_date(first_infection_any_symp)
+confirmed_infection_any_symp      <- change_any_symptom_date(confirmed_infection_any_symp)
+reinfections_any_symp             <- change_any_symptom_date(reinfections_any_symp)
+tested_negative_earliest_any_symp <- change_any_symptom_date(tested_negative_earliest_any_symp)
+tested_negative_all_any_symp      <- change_any_symptom_date(tested_negative_all_any_symp)
+PCR_negative_earliest_any_symp    <- change_any_symptom_date(PCR_negative_earliest_any_symp)
+PCR_negative_all_any_symp         <- change_any_symptom_date(PCR_negative_all_any_symp)
   
 append_table(covid_infection_any_symp)
 append_table(first_infection_any_symp)
@@ -1111,17 +1111,14 @@ moderna_id <- cohorts_ids %>%
                     filter(str_detect(name, "Moderna")) %>% 
                     select(cohort_definition_id) %>% pull()
 
-cdm$er_
-
-
-
 
 ## cohrot of interest - first New Covid infections
-# main_cohort_interest <- cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == 22)
 # 90 days long Covid cohort
 # first two digits are for the "mother cohort"
 # digits 3,4 are for the symptoms cohort (99 is for any symptom") 
 # last two digits for window period
[…]

### 2022-11-15 characterisation/Cohort_Dx_initial/00_Get_json_cohorts_Atlas.R

@@ -13,11 +13,10 @@ baseUrl <- "https://atlas-demo.ohdsi.org/WebAPI"
 cohortIds <- c(
 1780619,1780589,1780628,1780624,1780622,1780617,1780615,1780618,1780621,1780620,
   1780626,1780612,1780625,1780614,1780613,1780631,1780623,1780627,1780629,1780630,
-1780632,1780603,1780604,  1780846
+1780632,1780603,1780604,  1780846,1780611,1780580,1780634,1780587,1780635,1780582,1780581, 1780608
 )
 
 # cohorts with measurements
-cohorts_measurements <- c(1780611,1780580,1780634,1780587,1780635,1780582,1780581, 1780608)
 
 
 # create folder to save cohorts if needed
@@ -27,7 +26,6 @@ if (!file.exists(cohorts.folder)){
 }
 
 
-cohortId <- 1780608
 for (i in 1:length(cohortIds)){
 cohortId <- cohortIds[i]
  message(paste0("working on ",cohortId))
@@ -36,7 +34,7 @@ cohort  <- getCohortDefinition(baseUrl = baseUrl, cohortId = cohortId)
 # get cohort name
 name <- cohort$name
 # get json expression
-validJsonExpression <- RJSONIO::toJSON(cohort$expression)
+validJsonExpression <- RJSONIO::toJSON(cohort$expression,  digits = 23)
 # save in jsons files with the cohort name
 fileConn<-file(paste0(cohorts.folder,"/", name,".json"))
 writeLines(validJsonExpression, fileConn)

### 2022-11-15 characterisation/Cohort_Dx_initial/01_CodeToRun.R

@@ -1,75 +1,0 @@
-
-# install.packages("renv") # if not already installed, install renv from CRAN
-# renv::activate()
-# renv::restore() # this should prompt you to install the various packages required for the study
-
-
-# packages -----
-# load the below packages 
-# you should have them all available, with the required version, after
-# having run renv::restore above
-library(DatabaseConnector)
-library(CohortDiagnostics)
-library(CirceR)
-library(CohortGenerator)
-library(here)
-library(stringr)
-
-# database metadata and connection details -----
-
-# database connection details
- server<-Sys.getenv("SERVER_JUN22")
- user<-Sys.getenv("DB_USER_JUN22")
- password<- Sys.getenv("DB_PASSWORD_JUN22")
- port<-Sys.getenv("DB_PORT_JUN22")
- host<-Sys.getenv("DB_HOST_JUN22")
-# The name/ acronym for the database
-server_dbi <-Sys.getenv("SERVER_DBI_JUN22")
-
-# sql dialect used with the OHDSI SqlRender package
-# schema that contains the OMOP CDM with patient-level data
-# schema that contains the vocabularie
-# schema where a results table will be created 
-
- targetDialect             <- "postgresql" 
- cdm_database_schema       <- "omop21t4_cmbd" 
- vocabulary_database_schema<- "omop21t4_cmbd"
- results_database_schema<- "results21t4_cmbd"
-
-
-
-
-# driver for DatabaseConnector
-downloadJdbcDrivers("postgresql", here()) # if you already have this you can omit and change pathToDriver below
-connectionDetails <- createConnectionDetails(dbms = "postgresql",
-                                             server =server,
-                                             user = user,
-                                             password = password,
-                                             port = port ,
-                                             pathToDriver = here())
-
-
-
-db <- dbConnect(RPostgres::Postgres(),
-                dbname = server_dbi,
-                port = port,
-                host = host, 
-                user = user, 
-                password = password)
-
-
-
-
-# stem for tables to be created in your results schema for this analysis
-# You can keep the above names or change them
-# Note, any existing tables in your results schema with the same name will be overwritten
-cohortTableStem<-"er_cohorts_for_longcov"
-
-# Run analysis ----
-source(here("Cohort_Dx_initial", "RunAnalysis.R"))
-
-# Review results -----
-# CohortDiagnostics::preMergeDiagnosticsFiles(dataFolder = here("Results"))
-# CohortDiagnostics::launchDiagnosticsExplorer(dataFolder = here("Results"))
-
-

### 2022-11-15 characterisation/Cohort_Dx_initial/RunAnalysis.R

@@ -1,76 +1,0 @@
-# Get cohort details -----
- cohortJsonFiles <- list.files(here("Cohort_Dx_initial","1_InstantiateCohorts", "Cohorts"))
-#cohortJsonFiles <- list.files(here("1_InstantiateCohorts", "Covid_cohorts"))
-
-cohortJsonFiles <- cohortJsonFiles[str_detect(cohortJsonFiles,".json")]
-
-cohortDefinitionSet <- list()
-for(i in 1:length(cohortJsonFiles)){
-working.json<-here("Cohort_Dx_initial","1_InstantiateCohorts", "Cohorts",
-                      cohortJsonFiles[i])
-cohortJson <- readChar(working.json, file.info(working.json)$size)
-cohortExpression <- cohortExpressionFromJson(cohortJson) # generates the sql
-sql <- buildCohortQuery(cohortExpression, 
-                   options = CirceR::createGenerateOptions(generateStats = TRUE))
-
-cohortDefinitionSet[[i]]<-tibble(atlasId = i,
-      cohortId = i,
-      cohortName = str_replace(cohortJsonFiles[i],".json",""),
-      json=cohortJson,
-      sql=sql,
-      logicDescription = NA,
-      generateStats=TRUE)
-}
-cohortDefinitionSet<-bind_rows(cohortDefinitionSet)
-
-# Names of tables to be created during study run ----- 
-cohortTableNames <- CohortGenerator::getCohortTableNames(cohortTable = cohortTableStem)
-
-# Create the tables in the database -----
-CohortGenerator::createCohortTables(connectionDetails = connectionDetails,
-                                    cohortTableNames = cohortTableNames,
-                                    cohortDatabaseSchema = results_database_schema)
-
-# Generate the cohort set -----
-CohortGenerator::generateCohortSet(connectionDetails= connectionDetails,
-                                   cdmDatabaseSchema = cdm_database_schema,
-                                   cohortDatabaseSchema = results_database_schema,
-                                   cohortTableNames = cohortTableNames,
-                                   cohortDefinitionSet = cohortDefinitionSet)
-
-# get stats  -----
-CohortGenerator::exportCohortStatsTables(
-    connectionDetails = connectionDetails,
-    connection = NULL,
-    cohortDatabaseSchema = results_database_schema,
-    cohortTableNames = cohortTableNames,
-    cohortStatisticsFolder = here("Cohort_Dx_initial", "Results"),
[…]

### 2022-11-15 characterisation/explorando_Tests.R

@@ -1,87 +1,0 @@
-
-
-# packages -----
-# load the below packages 
-# you should have them all available, with the required version, after
-# having run renv::restore above
-library(DatabaseConnector)
-library(CohortDiagnostics)
-library(CirceR)
-library(CohortGenerator)
-library(here)
-library(stringr)
-library(CDMConnector)
-
-
-
-# database metadata and connection details -----
-
-# database connection details
-server<-Sys.getenv("SERVER_JUN22")
-user<-Sys.getenv("DB_USER_JUN22")
-password<- Sys.getenv("DB_PASSWORD_JUN22")
-port<-Sys.getenv("DB_PORT_JUN22")
-host<-Sys.getenv("DB_HOST_JUN22")
-# # The name/ acronym for the database
- db.name<-Sys.getenv("SERVER_DBI_JUN22")
-
-# sql dialect used with the OHDSI SqlRender package
-# schema that contains the OMOP CDM with patient-level data
-# schema that contains the vocabularie
-# schema where a results table will be created 
-
-targetDialect              <- "postgresql"
-cdm_database_schema        <- "omop21t4_cmbd" 
-vocabulary_database_schema <-"omop21t4_cmbd" 
-write_schema               <-"results21t4_cmbd"
-
-db <- dbConnect(RPostgres::Postgres(),
-                dbname = server_dbi,
-                port = port,
-                host = host, 
-                user = user, 
-                password = password)
-
-# Generate cdm object to access the tables
-cdm <- cdm_from_con(db, 
-             cdm_schema = cdm_database_schema,
-             write_schema = write_schema)
-# PCR (SARS-CoV-2) 586310 Genetic material using Molecular method
-# antigen 37310257
-#antibody 37310258
-tests_ids <- c(586310 ,37310257)
-tests <- cdm$measurement %>% 
-  filter(measurement_concept_id %in% tests_ids) %>%
-  compute()
-
-
-tests %>% tally()
-covid_start_date    <- as.Date("2021-12-25", "%Y-%m-%d")
-tests <- tests %>%
-  filter(measurement_date > covid_start_date) %>%
-  collect()
-
-# value_as_concept_id
-# LOING negative: 45878583 - LA6577-6
-# LOINC positive: 45884084
-# LOINC undetermined: 45880649
-# LOINC likely
-
-
-
-# quiza el problema esta en los criterios de inclusion
-# tenemos edad
-cdm$person %>%
-  select(year_of_birth) %>%
[…]

### 2022-11-17 characterisation/Code/Comparing_symptoms_matched.Rmd
update

@@
 load(here("data", "table1_data.Rdata"))
-load(here("data", "table1_data_matched.Rdata"))
+#load(here("data", "table1_data_matched.Rdata"))
+load(here("data", "table1_data_matched_age_week.Rdata"))
+
+nice.num<-function(x){
+  prettyNum(x, big.mark=",", nsmall = 0, digits=0,scientific = FALSE)}
+nice.num2<-function(x){
+  prettyNum(x, big.mark=",", nsmall = 2, digits=2,scientific = FALSE)}
 
@@
         "renal_impairment",
-        "long_covid"
+        "long_covid",
+        "abdominal_pain",
+        "allergy", 
+        "altered_smell_taste",
+        "anxiety" , 
+        "blurred_vision" ,
+        "chest_pain" ,
+        "cognitive_dysfunction_brain_fog", 
+        "cough" ,
+        "depression" ,
+        "dizziness" ,
+        "dyspnea",
+        "fatigue_malaise" ,
+        "gastrointestinal_issues",
+        "headache" ,
+        "intermittent_fever",
+        "joint_pain"  , 
+        "memory_issues_v2" ,
+        "menstrual_problems" ,
+        "muscle_spams_pain",
+        "neuralgia" , 
+        "pins_sensation",  
+        "sleep_disorder" ,
+        "tachycardia" ,
+        "tinnitus_hearing_problems", 
+        "all_symp"
 )
@@
        table1_data_tested_negative_all %>%
-        mutate(group = "6 Tested negative, all "),
+        mutate(group = "6 Tested negative, all"),
        table1_data_pcr_negative_earliest  %>%
-        mutate(group = "7 PCR negative, earliest "),
+        mutate(group = "7 PCR negative, earliest"),
        table1_data_pcr_negative_all  %>%
-        mutate(group = "8 PCR negative, all ")) %>%
+        mutate(group = "8 PCR negative, all")) %>%
   filter(cohort_start_date >=full_testing_start_date)
@@
   factorVars = factor.vars,
-  includeNA=T,
+  includeNA=F,
   data = table1.data,
@@
   noSpaces = TRUE,
-  contDigits = 0,
-  catDigits = 0,
   printToggle=FALSE)
+
+for(i in 1:8) {
+# tidy up 
+  cur_column <- summary.characteristics[, i]
+  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
+                as.numeric() 
+  cur_column <-nice.num(cur_column)
+  # add back in
+ summary.characteristics[, i] <- str_replace(string=summary.characteristics[, i],
+                              pattern='[0-9.]+\\b', 
+                              replacement=cur_column)    
+}
 
@@
   factorVars = factor.vars,
-  includeNA=T,
+  includeNA=F,
   data = data,
@@
   noSpaces = TRUE,
-  catDigits = 0,
-  contDigits = 0,
   printToggle=FALSE)
+
+for(i in 1:2) {
+# tidy up 
+  cur_column <- summary.characteristics_covid_negative[, i]
+  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
+                as.numeric() 
+  cur_column <-nice.num(cur_column)
+  # add back in
+ summary.characteristics_covid_negative[, i] <- str_replace(string=summary.characteristics_covid_negative[, i],
+                              pattern='[0-9.]+\\b', 
+                              replacement=cur_column)    
+}
 
@@
   noSpaces = TRUE,
-  contDigits = 0,
-  catDigits = 0,
   printToggle=FALSE)
+
+for(i in 1:2) {
+# tidy up 
+  cur_column <- summary.characteristics.confirmed[, i]
+  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
+                as.numeric() 
+  cur_column <-nice.num(cur_column)
+  # add back in
+ summary.characteristics.confirmed[, i] <- str_replace(string=summary.characteristics.confirmed[, i],
+                              pattern='[0-9.]+\\b', 
+                              replacement=cur_column)    
+}
 
@@
 ```{r include=FALSE}
+
 data <- m.first_infection_reinfections[[3]]
@@
   noSpaces = TRUE,
-  contDigits = 0,
-  catDigits = 0,
   printToggle=FALSE)
+
+for(i in 1:2) {
+# tidy up 
+  cur_column <- summary.characteristics.reinfections[, i]
+  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
+                as.numeric() 
+  cur_column <-nice.num(cur_column)
+  # add back in
+ summary.characteristics.reinfections[, i] <- str_replace(string=summary.characteristics.reinfections[, i],
+                              pattern='[0-9.]+\\b', 
+                              replacement=cur_column)    
+}
 
@@
   factorVars = factor.vars,
-  includeNA=T,
+  includeNA=F,
   data = s.data,
@@
   noSpaces = TRUE,
-  contDigits = 0,
-   catDigits = 0,
   printToggle=FALSE)
+
+for(i in 1:2) {
+# tidy up 
+  cur_column <- summary.characteristics_symptoms[, i]
+  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
+                as.numeric() 
+  cur_column <-nice.num(cur_column)
+  # add back in
+summary.characteristics_symptoms[, i] <- str_replace(string=summary.characteristics_symptoms[, i],
+                              pattern='[0-9.]+\\b', 
+                              replacement=cur_column)    
+}
 
@@
   noSpaces = TRUE,
-  contDigits = 0,
-  catDigits = 0,
   printToggle=FALSE)
+
+for(i in 1:2) {
+# tidy up 
+  cur_column <- summary.characteristics_symptoms[, i]
+  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
+                as.numeric() 
+  cur_column <-nice.num(cur_column)
+  # add back in
+summary.characteristics_symptoms[, i] <- str_replace(string=summary.characteristics_symptoms[, i],
+                              pattern='[0-9.]+\\b', 
+                              replacement=cur_column)    
+}
+
 ```
@@
   noSpaces = TRUE,
-  contDigits = 0,
-  catDigits = 0,
   printToggle=FALSE)
+
+for(i in 1:2) {
+# tidy up 
+  cur_column <- summary.characteristics_symptoms[, i]
+  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
+                as.numeric() 
+  cur_column <-nice.num(cur_column)
+  # add back in
+summary.characteristics_symptoms[, i] <- str_replace(string=summary.characteristics_symptoms[, i],
+                              pattern='[0-9.]+\\b', 
+                              replacement=cur_column)    
+}
 

### 2022-11-17 characterisation/Code/Code_to_Run.R

@@ -3,10 +3,6 @@
 if (!require("pacman")) install.packages("pacman")
 library(pacman)
 
-
-
-
-
 p_load(SqlRender,
        DBI,
        DatabaseConnector,
@@ -23,24 +19,6 @@ p_load(SqlRender,
        tsibble,
        CirceR,
        survey)
-
-# library(here)
-# library(SqlRender)
-# library(DBI)
-# library(DatabaseConnector)
-# library(CohortGenerator)
-# library(CohortDiagnostics)
-# library(dplyr)
-# library(dbplyr)
-# library(tidyr)
-# library(CDMConnector)
-# library(stringr)
-# library(CirceR)
-# library(lubridate)
-# library(MatchIt)
-# library(tsibble)
-# library(survey)
-
 
 # Connection details ----
 server    <- Sys.getenv("SERVER_JUN22")

### 2022-11-17 characterisation/Code/Run_Analysis.R

@@ -299,99 +299,23 @@ exclusion_table<-rbind(exclusion_table,
                             distinct() %>%pull()
                          ))
 
-
-# covid_infection %>%tally()  #857732 infections
-# covid_infection %>% select(subject_id)%>% distinct() %>%tally() #805884 subjects
-
-### First COVID-19 infection 
-first_infection <- covid_infection %>%
-  filter(seq==1) %>% 
-  distinct() %>%
-  select(-seq) %>%
-  # we change cohort definition id so that is has its own id
-  mutate(cohort_definition_id=as.integer(70)) %>%
-  compute() 
-# check we have one row per person
-# first_infection %>%tally()    # 782948
-# first_infection %>% select(subject_id)%>% distinct() %>%tally() #782948
-
-# we add the cohort id to our cohorts ids table
-cohorts_ids <- rbind(cohorts_ids,
-                     tibble(atlas_id = NA,
-                            name = "First COVID-19 infection",
-                            cohort_definition_id =70, 
-                            name_var = "first_infection",
-                            type = "covid-19"))
-
-exclusion_table<-rbind(exclusion_table,
-                       tibble(N_current=first_infection %>%tally()%>%collect()%>%pull(), 
-                          exclusion_reason="initial pop",
-                          cohort_definition_id = first_infection%>%
-                                                  select(cohort_definition_id) %>% 
-                            distinct() %>%pull()
-                         ))
-
-
-reinfections <- covid_infection %>%
-  filter(seq!=1)%>% 
-  select(-seq) %>%
-  distinct() %>%
-  # we change cohort definition id so that is has its own id
-  mutate(cohort_definition_id=as.integer(71)) %>%
-  compute()
-
-# reinfections %>%tally()    #  74784
-reinfections %>% select(subject_id)%>% distinct() %>%tally() #70752
-
-exclusion_table<-rbind(exclusion_table,
-                       tibble(N_current=reinfections %>%tally()%>%collect()%>%pull(), 
-                          exclusion_reason="initial pop",
-                          cohort_definition_id = reinfections %>%
-                                                 select(cohort_definition_id) %>%
-                            distinct() %>%pull()
-                          ))
-# we add the cohort identificator to our cohorts ids table
-cohorts_ids <- rbind(cohorts_ids,
-                     tibble(atlas_id = NA,
-                            name = "Reinfections",
[…]

### 2022-11-17 characterisation/Code/Run_Analysis.R
update

@@ -299,147 +299,10 @@ exclusion_table<-rbind(exclusion_table,
                             distinct() %>%pull()
                          ))
 
-covid_infection <- covid_infection %>%
-   mutate(cohort_definition_id= as.integer(cohort_definition_id))%>%
-   select(-seq)%>%
-   compute()
-
-## inserting these cohorts into the database
-#### remove prior tables if needed
- sql_query <- glue::glue("DROP TABLE {write_schema}.er_long_covid_final_cohorts\n" )
- DBI::dbExecute(db, as.character(sql_query))
-
- # create new table 
-sql_query <- glue::glue("SELECT * INTO {write_schema}.er_long_covid_final_cohorts\n",
-                          "FROM (\n",
-                          dbplyr::sql_render(covid_infection),
-                          "\n) AS from_table")
-DBI::dbExecute(db, as.character(sql_query))
-
-###  Tested positive  ----
-confirmed_infection_id <- cohorts_ids %>% filter(str_detect(name, "Tested_Positive")) %>%select(cohort_definition_id) %>% pull()
-
-confirmed_infection <- covid_cohorts %>%
-  filter(cohort_definition_id==confirmed_infection_id) %>%# change this for confirmed infections
-  arrange(subject_id, desc(as.Date(cohort_start_date))) %>% 
-  group_by(subject_id) %>% 
-  arrange(cohort_start_date) %>%
-  mutate(seq=row_number()) %>% 
-  distinct() %>%
-  ungroup() %>%
-  compute()
-
-rm(confirmed_infection_id)
-# add next infection date to use for censoring 
-confirmed_infection <- confirmed_infection %>%
- arrange(subject_id,cohort_start_date) %>% 
- group_by(subject_id) %>%
- mutate(covid_next_inf_date = lead(cohort_start_date)) %>%
- ungroup() %>%
- compute()
-
-# add influenza to censor
-### first we get rid of influenzxa dx prior to cohort_start_date
-influenza_covid <- influenza_cohort %>%
-  inner_join(confirmed_infection) %>%
-  filter(influenza_start_date>cohort_start_date) %>%
-  distinct() %>%
-  compute()
-
-# we check if we have people with more than one influenza infection after cohort start  
-# it's cohorts in which all columns are identical aside from influenza_date
-# we don't have for confirmed infectiosn but we keep the code 
-repeated_influenza <-  influenza_covid %>%
[…]

### 2022-11-18 characterisation/Code/Comparing_symptoms_matched_nonbiased.Rmd
update

--- 2022-11-17 characterisation/Code/Comparing_symptoms_matched.Rmd
@@
 load(here("data", "table1_data.Rdata"))
-#load(here("data", "table1_data_matched.Rdata"))
-load(here("data", "table1_data_matched_age_week.Rdata"))
+load(here("data", "table1_data_matched.Rdata"))
+#load(here("data", "table1_data_matched_age_week.Rdata"))
 
@@
         mutate(group = "8 PCR negative, all")) %>%
-  filter(cohort_start_date >=full_testing_start_date)
+  filter(cohort_start_date >=full_testing_start_date) %>%
+     mutate(abdominal_pain=ifelse(is.na(abdominal_pain),0,abdominal_pain)) %>% 
+       mutate(allergy =ifelse(is.na(allergy ),0,allergy)) %>% 
+       mutate(altered_smell_taste =ifelse(is.na(altered_smell_taste ),0,altered_smell_taste)) %>% 
+       mutate(blurred_vision  =ifelse(is.na(blurred_vision  ),0,blurred_vision )) %>% 
+       mutate( anxiety =ifelse(is.na(  anxiety),0, anxiety)) %>% 
+       mutate(chest_pain =ifelse(is.na(chest_pain ),0,chest_pain)) %>% 
+       mutate(cognitive_dysfunction_brain_fog=ifelse(is.na(cognitive_dysfunction_brain_fog),0,cognitive_dysfunction_brain_fog)) %>% 
+       mutate( cough  =ifelse(is.na( cough  ),0, cough )) %>% 
+       mutate(depression =ifelse(is.na(depression ),0,depression)) %>% 
+       mutate(dizziness =ifelse(is.na(dizziness ),0,dizziness)) %>% 
+       mutate(dyspnea =ifelse(is.na( dyspnea),0,dyspnea)) %>% 
+       mutate(fatigue_malaise =ifelse(is.na(fatigue_malaise ),0,fatigue_malaise)) %>% 
+       mutate(gastrointestinal_issues =ifelse(is.na(gastrointestinal_issues ),0,gastrointestinal_issues)) %>% 
+       mutate(headache  =ifelse(is.na( headache ),0,headache )) %>% 
+       mutate(intermittent_fever =ifelse(is.na(intermittent_fever ),0,intermittent_fever)) %>% 
+       mutate( joint_pain =ifelse(is.na( joint_pain ),0, joint_pain)) %>% 
+       mutate( memory_issues_v2  =ifelse(is.na( memory_issues_v2 ),0, memory_issues_v2 )) %>% 
+       mutate(menstrual_problems =ifelse(is.na( menstrual_problems),0,menstrual_problems)) %>% 
+       mutate( muscle_spams_pain =ifelse(is.na(  muscle_spams_pain),0, muscle_spams_pain)) %>% 
+       mutate(neuralgia =ifelse(is.na(neuralgia),0,neuralgia)) %>% 
+       mutate(pins_sensation =ifelse(is.na(pins_sensation ),0,pins_sensation)) %>% 
+       mutate( sleep_disorder =ifelse(is.na(  sleep_disorder),0, sleep_disorder)) %>% 
+       mutate(tachycardia =ifelse(is.na(tachycardia ),0,tachycardia)) %>% 
+       mutate(tinnitus_hearing_problems =ifelse(is.na(tinnitus_hearing_problems ),0,tinnitus_hearing_problems)) %>% 
+       mutate(all_symp =ifelse(is.na(all_symp ),0,all_symp))
 
@@
   strata=c("name"),
-  test = F), 
+  test = T), 
   showAllLevels=F,
@@
 ```
-
-```{r Old_function_matching, eval=FALSE, include=FALSE}
-# matched_table_symptom_cohorts <- function(cohort_id1, cohort_id2, window, name1, name2){
-#  results_list <- list()
-#  
-#   cohort1 <- cdm$er_long_covid_all_symptoms_cohorts %>%
-#   filter(main_cohort_id == cohort_id1 & window_days == window) %>%
-#   mutate(name = name1) %>%
-#   mutate(cohort = "0") %>% 
-#   distinct() %>%
-#   collect()
-# 
-#   cohort2 <- cdm$er_long_covid_all_symptoms_cohorts %>%
-#   filter(main_cohort_id == cohort_id2 & window_days == window) %>%
-#    mutate(name = name2) %>%
-#       mutate(cohort = "1") %>%
-#   distinct() %>%
-#   collect()
-# 
-#   data <- rbind(cohort1 , cohort2) %>% mutate(week_year = yearweek(as.Date(cohort_start_date)))
-# # we match by week and year using exact method 
-# m.week_year <- matchit(cohort ~ week_year, data = data, method = "exact")
-# sum_matching <- summary(m.week_year)
-# # we extract matched data
-# m.data <- match.data(m.week_year) %>%
-#   rename(ps_weights= weights) %>%
-#     mutate(all_symp = as.factor(all_symp)) %>%
-#   select(-subject_id, -window_days, - cohort_start_date , -week_year, -main_cohort_id, -cohort) 
-# 
-# s.data <- svydesign(ids = ~subclass, # clusters 
-#           data = m.data, 
-#           weights= ~ps_weights) # weights
-# 
-# summary <-  s.data%>% 
-#    tbl_svysummary(
-#        by = "cohort",
-#   digits = all_categorical()~ c(0,1),
-#   missing = "ifany",
-#   missing_text= "Missing",
-#   percent = "col"
-#            ) %>% 
-#   bold_labels()
-# 
-# results_list <- list(sum_matching, m.data, s.data,   summary)
-# results_list
-# }
-# t.first.infections.reinfections <- matched_table_symptom_cohorts(cohort_id1= "70", name1= "First COVID-19 infection",
-#                                                            cohort_id2 = "71", name2 = "Reinfections", 
-#                                                            window="90")
-# 
-# 
-# t.infections.tested.negative <- matched_table_symptom_cohorts(cohort_id1= "22", name1= "New COVID-19 infection",
-#                                                            cohort_id2 = "30", name2 = "Tested negative, earliest", 
-#                                                            window="90")
-
-```
-
-# 90 days Long Covid symptoms distribution
-```{r}
-vars <- c("abdominal_pain", "allergy", "altered_smell_taste",  "anxiety" , 
-         "blurred_vision","chest_pain" ,"cognitive_dysfunction_brain_fog", "cough" ,"depression" ,
-         "dizziness" ,"dyspnea" , "fatigue_malaise" , "gastrointestinal_issues","headache" ,"intermittent_fever" ,
-         "joint_pain" ,  "memory_issues_v2" ,"menstrual_problems" , "muscle_spams_pain", "neuralgia" , "pins_sensation",  
-         "sleep_disorder", "tachycardia" ,"tinnitus_hearing_problems")
-
-factor.vars <- c("abdominal_pain", "allergy", "altered_smell_taste",  "anxiety" , 
-         "blurred_vision","chest_pain" ,"cognitive_dysfunction_brain_fog", "cough" ,"depression" ,
-         "dizziness" ,"dyspnea" , "fatigue_malaise" , "gastrointestinal_issues","headache" ,"intermittent_fever" ,
-         "joint_pain" ,  "memory_issues_v2" ,"menstrual_problems" , "muscle_spams_pain", "neuralgia" , "pins_sensation",  
-         "sleep_disorder", "tachycardia" ,"tinnitus_hearing_problems")
-
-```
-
-```{r include=FALSE}
-# function to get data for the plot
-get_prop <- function(data){
-  filt <- c("1","2","3","4","5","6","7","8","9","10","11", "__all_symp__")
-  names <- names(as_tibble(data,  col_labels = T)) 
-  names <- str_extract(names, "\\*(.*)\\*")
-  names <- str_sub(names, 3)
-  names <- str_sub(names, end=-3)
-
-  output <- as_tibble(data,  col_labels = F) %>%
-   filter(!(label %in% filt)) %>%
-    mutate(prop1 = str_extract(stat_1, "(?<=\\()(.*?)%")) %>%
-    mutate(prop1= substring(prop1,1, nchar(prop1)-1)) %>%
-  mutate(prop1 = as.numeric(prop1)) %>%
-  select(-stat_1) %>%
-     mutate(prop2 = str_extract(stat_2, "(?<=\\()(.*?)%")) %>%
-  mutate(prop2= substring(prop2,1, nchar(prop2)-1)) %>%
-  mutate(prop2 = as.numeric(prop2)) %>%
-      select(-stat_2) %>%
-  mutate(label= substring(label,1, nchar(label)-2)) %>%
-  mutate(label= substring(label,3)) %>%
-  mutate(label = str_replace_all(label, "_", " ")) %>%
-  mutate(label = str_to_title(label)) %>%
-  as.data.frame()
-
-  names(output) <- names
-  output
-}
-
-# plot function
-function_matched_heatmap <- function(data){
- plot <-  data %>% 
-  pivot_longer(!Characteristic, names_to = "Cohort", values_to = "Proportion") %>%
-  mutate(Characteristic = fct_rev(factor(Characteristic))) %>%
-  ggplot() +
-  aes(x = 1, y = Characteristic, fill = Proportion) +
-  facet_grid(~Cohort)+
-  geom_tile(colour = "black") +
-  scale_fill_gradient(high = "#C81D25", low = "#E4F1EB")+
-  geom_text(aes(label= round(Proportion, 1))) +
-  theme_minimal() +
-  theme(axis.text.x=element_blank(),
-        legend.position = "bottom")+
-  xlab("")+
-  ylab("Symptom")+
-  labs(fill= "Proportion, in %")
- plot
-}
-
-```
-
-## Matched New COVID-19 infection vs Tested negative (earliest record) cohorts
-```{r echo=FALSE}
-
-data <- m.new_covid_tested_negative_earliest[[2]] %>% filter(long_covid == 1) 
-data <- data %>% 
-  select(name, abdominal_pain, allergy, altered_smell_taste,  anxiety , 
-         blurred_vision ,chest_pain ,cognitive_dysfunction_brain_fog, cough ,depression ,
-         dizziness ,dyspnea , fatigue_malaise , gastrointestinal_issues,headache ,intermittent_fever ,
-         joint_pain  ,  memory_issues_v2 ,menstrual_problems , muscle_spams_pain, neuralgia , pins_sensation,  
-         sleep_disorder , tachycardia ,tinnitus_hearing_problems,  all_symp, ps_weights, matched_pair  )
-
-s.data <- svydesign(ids = ~matched_pair,  
-          data = data, 
-          weights= ~ps_weights) # weights all 1
-
-summary.characteristics_symptoms <-print(svyCreateTableOne(
-  vars =  vars,
-  factorVars = factor.vars,
-  includeNA=F,
-  data = s.data,
-  strata=c("name"),
-  test = F), 
-  showAllLevels=F,
-  smd=T,
-  nonnormal = vars, #all 
-  noSpaces = TRUE,
-  printToggle=FALSE)
-
-for(i in 1:2) {
-# tidy up 
-  cur_column <- summary.characteristics_symptoms[, i]
-  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
-                as.numeric() 
-  cur_column <-nice.num(cur_column)
-  # add back in
-summary.characteristics_symptoms[, i] <- str_replace(string=summary.characteristics_symptoms[, i],
-                              pattern='[0-9.]+\\b', 
-                              replacement=cur_column)    
-}
-
-```
-
-```{r}
-kable(summary.characteristics_symptoms
-     )%>%
-  kable_styling(bootstrap_options = c("striped", "bordered")) #%>%
- # pack_rows("Baseline comorbidities", 40, 44)
-```
-
-## Heatmap
-
-```{r eval=FALSE, include=FALSE}
-results <-  get_prop(summary_new_covid_tested_negative) 
-function_matched_heatmap(results)
-
-```
-
-## Matched Confirmed infection vs tested negative (earliest)
-```{r}
-data <- m.confirmed_infection_negative_earliest[[2]] %>% filter(long_covid == 1)
-data <- data %>% 
-  select(name, abdominal_pain, allergy, altered_smell_taste,  anxiety , 
-         blurred_vision ,chest_pain ,cognitive_dysfunction_brain_fog, cough ,depression ,
-         dizziness ,dyspnea , fatigue_malaise , gastrointestinal_issues,headache ,intermittent_fever ,
-         joint_pain  ,  memory_issues_v2 ,menstrual_problems , muscle_spams_pain, neuralgia , pins_sensation,  
-         sleep_disorder , tachycardia ,tinnitus_hearing_problems,  all_symp, ps_weights, matched_pair  )
-
-s.data <- svydesign(ids = ~matched_pair,  
-          data = data, 
-          weights= ~ps_weights) # weights all 1
-
-summary.characteristics_symptoms <-print(svyCreateTableOne(
-  vars =  vars,
-  factorVars = factor.vars,
-  includeNA=F,
-  data = s.data,
-  strata=c("name"),
-  test = F), 
-  showAllLevels=F,
-  smd=T,
-  nonnormal = vars, #all 
-  noSpaces = TRUE,
-  printToggle=FALSE)
-
-for(i in 1:2) {
-# tidy up 
-  cur_column <- summary.characteristics_symptoms[, i]
-  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
-                as.numeric() 
-  cur_column <-nice.num(cur_column)
-  # add back in
-summary.characteristics_symptoms[, i] <- str_replace(string=summary.characteristics_symptoms[, i],
-                              pattern='[0-9.]+\\b', 
-                              replacement=cur_column)    
-}
-
-```
-
-```{r}
-kable(summary.characteristics_symptoms
-     )%>%
-  kable_styling(bootstrap_options = c("striped", "bordered"))
-```
-
-```{r eval=FALSE, include=FALSE}
-data <- m.confirmed_infection_negative_earliest[[2]] %>% filter(long_covid == 1)
-# keep only variables of interest
-data <- data %>% 
-  select(name, abdominal_pain, allergy, altered_smell_taste,  anxiety , 
-         blurred_vision ,chest_pain ,cognitive_dysfunction_brain_fog, cough ,depression ,
-         dizziness ,dyspnea , fatigue_malaise , gastrointestinal_issues,headache ,intermittent_fever ,
-         joint_pain  ,  memory_issues_v2 ,menstrual_problems , muscle_spams_pain, neuralgia , pins_sensation,  
-         sleep_disorder , tachycardia ,tinnitus_hearing_problems,  all_symp, ps_weights, matched_pair  )
-
-s.data <- svydesign(ids = ~matched_pair, # clusters 
-          data = data, 
-          weights= ~ps_weights) # weights
-
-summary_confirmed_infection_tested_negative_earliest <-  s.data%>%
-   tbl_svysummary(
-       by = "name",
-  digits = all_categorical()~ c(0,1),
-  missing = "ifany",
-  missing_text= "Missing",
-  percent = "col"
-           ) %>%
-  bold_labels()
-
-summary_confirmed_infection_tested_negative_earliest 
-```
-
-## Heatmap
-```{r eval=FALSE, include=FALSE}
-results <-  get_prop(summary_confirmed_infection_tested_negative_earliest ) 
-function_matched_heatmap(results)
-```
-
-## Matched First COVID-19 infection vs Reinfection cohorts
-```{r}
-data <- m.first_infection_reinfections[[2]] %>% filter(long_covid == 1)
-data <- data %>% 
-  select(name, abdominal_pain, allergy, altered_smell_taste,  anxiety , 
-         blurred_vision ,chest_pain ,cognitive_dysfunction_brain_fog, cough ,depression ,
-         dizziness ,dyspnea , fatigue_malaise , gastrointestinal_issues,headache ,intermittent_fever ,
-         joint_pain  ,  memory_issues_v2 ,menstrual_problems , muscle_spams_pain, neuralgia , pins_sensation,  
-         sleep_disorder , tachycardia ,tinnitus_hearing_problems,  all_symp, ps_weights, matched_pair  )
-
-s.data <- svydesign(ids = ~matched_pair,  
-          data = data, 
-          weights= ~ps_weights) # weights all 1
-
-summary.characteristics_symptoms <-print(svyCreateTableOne(
-  vars =  vars,
-  factorVars = factor.vars,
-  includeNA=F,
-  data = s.data,
-  strata=c("name"),
-  test = F), 
-  showAllLevels=F,
-  smd=T,
-  nonnormal = vars, #all 
-  noSpaces = TRUE,
-  printToggle=FALSE)
-
-for(i in 1:2) {
-# tidy up 
-  cur_column <- summary.characteristics_symptoms[, i]
-  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
-                as.numeric() 
-  cur_column <-nice.num(cur_column)
-  # add back in
-summary.characteristics_symptoms[, i] <- str_replace(string=summary.characteristics_symptoms[, i],
-                              pattern='[0-9.]+\\b', 
-                              replacement=cur_column)    
-}
-
-```
-
-```{r}
-kable(summary.characteristics_symptoms
-     )%>%
-  kable_styling(bootstrap_options = c("striped", "bordered"))
-```
-
-## Heatmap
-```{r eval=FALSE, include=FALSE}
-results <-  get_prop(summary_first_infection_reinfections ) 
-function_matched_heatmap(results)
-```

### 2022-11-18 characterisation/Code/Code_to_Run.R

@@ -52,15 +52,14 @@ connectionDetails <- DatabaseConnector::createConnectionDetails(dbms = "postgres
                                                                 pathToDriver = here::here())
 
 ## Parameters ----
-# to get rid of covid diagnoses captured before the start of the pandemic --
-covid_start_date    <- as.Date("2020-02-25", "%Y-%m-%d")
+# to keep only records after the first wave  --
+covid_start_date    <- as.Date("2020-09-01", "%Y-%m-%d")
 # we are not interested in old influenza diagnoses - so we can filter these
 influenza_start_date<- as.Date("2019-12-01", "%Y-%m-%d")
 # for symptoms, we only need symptoms occurring during covid + 180 days washout
 symptoms_start_date <- as.Date("2019-08-29","%Y-%m-%d")
 end_index_date      <- as.Date("2021-09-02", "%Y-%m-%d")
-# for filtering some results 
-full_testing_start_date <- as.Date("2020-09-01", "%Y-%m-%d")
+
 
 # Create initial Json cohorts ---- 
 create_initial_json_cohorts     <- TRUE

### 2022-11-18 characterisation/Code/Run_Analysis.R

@@ -121,15 +121,19 @@ covid_ids    <- cohorts_ids %>% filter(type=="covid-19") %>% select(cohort_defin
 influenza_id <- cohorts_ids %>% filter(type=="influenza") %>% select(cohort_definition_id) %>% pull()
 controls_ids <- cohorts_ids %>% filter(type=="control") %>% select(cohort_definition_id) %>% pull()
 symptoms_ids <- cohorts_ids %>% filter(type=="symptom") %>% select(cohort_definition_id) %>% pull()
+covid_censoring_id <- cohorts_ids %>%  filter(str_detect(name, "Tested_Positive_and_diagnoses"))%>% 
+                      select(cohort_definition_id) %>% pull()
 
 # combine observation period (to have observation period end date) and death with our study cohorts
 observation_death <- cdm$observation_period %>%
   select(person_id, observation_period_end_date) %>%
   left_join(cdm$death %>% select (person_id, death_date)) %>%
-  mutate(death = ifelse(!(is.na(death_date)), 1,0))
+  mutate(death = ifelse(!(is.na(death_date)), 1,0))%>%
+  compute()
 
 cohorts <- cdm$er_cohorts_for_longcov %>%
-  left_join(observation_death, by = c("subject_id" = "person_id") )
+  left_join(observation_death, by = c("subject_id" = "person_id") )%>%
+  compute()
 
 ## get initial cohorts ----
 # influenza cohort - to use for censoring 
@@ -161,20 +165,23 @@ symptom_cohorts <- cohorts %>%
  select(symptom_definition_id, subject_id, symptom_date) %>%
  compute()
 
-rm(covid_ids, influenza_id, controls_ids, cohorts, observation_death)
+covid_censoring_cohort <- covid_cohorts %>%
+    filter(cohort_definition_id==covid_censoring_id)%>%
+    rename(covid_censoring_date = cohort_start_date) %>%
+    select(subject_id, covid_censoring_date)
+    compute()
+
+rm(covid_ids, influenza_id, controls_ids, cohorts, observation_death,covid_censoring_id)
 
 
-####################################### Getting cohorts ########
 
 ## COVID-19 cohorts ----
-###  Covid infection - diagnoses and or laboratory tests  ----
 new_infection_id <- cohorts_ids %>%
                     filter(str_detect(name, "New_Infection")) %>% 
                     select(cohort_definition_id) %>% pull()
 
 covid_infection <- covid_cohorts %>%
[…]

### 2022-11-18 characterisation/Code/Descriptive_tables.Rmd
update

--- 2022-11-18 characterisation/Code/Comparing_symptoms_matched_nonbiased.Rmd
@@
 
-## Confirmed infections vs tested negative (earliest), after matching by week/year of testing and 5y age group
-```{r}
-data <- m.confirmed_infection_negative_earliest[[3]]
-
-summary.characteristics.confirmed<-print(svyCreateTableOne(
-  vars =  vars,
-  factorVars = factor.vars,
-  includeNA=F,
-  data = data,
-  strata=c("name"),
-  test = T), 
-  showAllLevels=F,
-  smd=T,
-  nonnormal = vars, #all 
-  noSpaces = TRUE,
-  printToggle=FALSE)
-
-for(i in 1:2) {
-# tidy up 
-  cur_column <- summary.characteristics.confirmed[, i]
-  cur_column <- str_extract(cur_column, '[0-9.]+\\b') %>% 
-                as.numeric() 
-  cur_column <-nice.num(cur_column)
-  # add back in
- summary.characteristics.confirmed[, i] <- str_replace(string=summary.characteristics.confirmed[, i],
-                              pattern='[0-9.]+\\b', 
-                              replacement=cur_column)    
-}
-
-```
-
-```{r}
-kable(summary.characteristics.confirmed
-     )%>%
-  kable_styling(bootstrap_options = c("striped", "bordered"))
-
-```
-
 ## First infections vs reinfections, after matching by week/year of testing and 5y age group

### 2022-11-18 characterisation/Code/Run_Analysis.R

@@ -852,36 +852,13 @@ working_cohort <- main_cohort_interest %>%
               mutate(gender= ifelse(gender_concept_id==8507, "Male",
                              ifelse(gender_concept_id==8532, "Female", NA ))) %>%
               select(-gender_concept_id)) %>%
-  # SIDIAP specific  - MEDEA and nationality
+  # SIDIAP specific  - MEDEA 
  # left_join(cdm$observation %>%
  #             filter(observation_source_value == "medea") %>% 
  #             select(person_id, observation_source_value, value_as_string) %>%
  #             filter(value_as_string %in% c("R", "U1", "U2", "U3", "U4", "U5")) %>%
  #             mutate(medea=value_as_string) %>%
  #             select(person_id, medea)) %>%
- #   left_join(cdm$observation %>%
- #             select(person_id, observation_source_value, value_as_string) %>%
- #             filter(observation_source_value == "agr_nationality") %>%
- #            rename(nationality = value_as_string) %>%
- #             select(person_id, nationality))%>%
- #     # clean nationality
- #   mutate(nationality = ifelse(str_detect(nationality, "Austr"), "Australia & New Zealand", nationality)) %>%
- #   mutate(nationality_cat = ifelse( nationality== "Espanya", "Spain", 
- #                            ifelse(str_detect( nationality, "frica"),  "Africa",  
- #                            ifelse(str_detect( nationality, "rica central"), "Central & South America",
- #                            ifelse(str_detect( nationality, "del Nord"), "Europe & North America",    
- #                            ifelse(str_detect( nationality, "Europa"), "Europe & North America",       
- #                            ifelse(str_detect( nationality, "Europa oriental"),  "Eastern Europe",       
- #                            ifelse(str_detect( nationality, "del Sud"), "Central & South America",      
- #                            ifelse(str_detect( nationality, "Carib"), "Central & South America", 
- #                            ifelse(str_detect( nationality, "sia"), "Asia & Oceania",
- #                            ifelse(str_detect( nationality, "Melan"), "Asia & Oceania", 
- #                            ifelse(str_detect( nationality, "Polin"), "Asia & Oceania",
[…]

### 2022-11-18 characterisation/Code/Run_Analysis.R
update

@@ -832,21 +832,13 @@ moderna_id <- cohorts_ids %>%
                     select(cohort_definition_id) %>% pull()
 
 
-## cohrot of interest - first New Covid infections
-# 90 days long Covid cohort
-# first two digits are for the "mother cohort"
-# digits 3,4 are for the symptoms cohort (99 is for any symptom") 
-# last two digits for window period
-## testing function
-# main_cohort_interest <- cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == 22)
-# long_covid_cohort <- cdm$er_long_covid_final_cohorts %>% filter(cohort_definition_id == 229990)
-
-
-# Function to get the data for the table 
-# !! pendent add PCR for postivie test----
-generate_data_table1 <- function(main_cohort_interest, long_covid_cohort){
-working_cohort <- main_cohort_interest %>% 
- rename(person_id=subject_id) %>%
+# function to get baseline characteristics in each cohort
+# pendent add PCR for postivie test----
+get_baseline_characteristics <- function(main_cohort_id){
+                                             
+working_cohort <-   cdm$er_long_covid_final_cohorts %>% 
+  filter(cohort_definition_id == main_cohort_id) %>%
+  rename(person_id=subject_id) %>%
   left_join(cdm$person  %>%
               select(person_id, gender_concept_id, year_of_birth) %>%
               mutate(gender= ifelse(gender_concept_id==8507, "Male",
@@ -1056,331 +1048,6 @@ vaccines <- rbind(cdm$er_cohorts_for_longcov %>% filter(cohort_definition_id == 
     filter(drug_exposure_start_date < cohort_start_date) %>%
     distinct() %>%
     compute()
-
- # SIDIAP specific vaccines   
-# vaccinations <- cdm$drug_exposure%>% 
-#       filter(drug_concept_id %in% 
-#            c("37003436","724905",  "37003518", "739906")) %>% 
-#   full_join(main_cohort_interest %>% rename(person_id=subject_id)) %>%
-#   filter(drug_exposure_start_date < cohort_start_date) %>%
-#   compute()  %>%
-#    #"BNT162b2" #"ChAdOx1" #"mRNA-1273" #Ad26.COV2.S
-#    select(person_id, drug_concept_id, drug_exposure_start_date) %>%
-#   distinct() %>%
-#    mutate(vaccine_type=
-#             ifelse(drug_concept_id=="37003436", "BNT162b2",
[…]

### 2022-11-21 characterisation/Cohort_Dx_initial/00_Get_json_cohorts_Atlas.R
update jsons

@@ -11,16 +11,44 @@ library(ROhdsiWebApi)
 baseUrl <- "https://atlas-demo.ohdsi.org/WebAPI"
 # list of cohort ids
 cohortIds <- c(
-1780619,1780589,1780628,1780624,1780622,1780617,1780615,1780618,1780621,1780620,
-  1780626,1780612,1780625,1780614,1780613,1780631,1780623,1780627,1780629,1780630,
-1780632,1780603,1780604,  1780846,1780611,1780580,1780634,1780587,1780635,1780582,1780581, 1780608
+1780604,
+1780604,
+1780608,
+1780612,
+1780613,
+1780614,
+1780603,
+1780615,
+1780617,
+1780618,
+1780620,
+1780621,
+1780622,
+1780619,
+1780623,
+1780611,
+1780624,
+1780625,
+1780626,
+1780627,
+1780628,
+1780629,
+1781117,
+1781135,
+1780630,
+1780846,
+1780631,
+1780632,
+1780635,
+1781126,
+1780589
 )
 
 # cohorts with measurements
 
 
 # create folder to save cohorts if needed
-cohorts.folder <- here::here("Cohort_Dx_initial/1_InstantiateCohorts/Cohorts_v2")
+cohorts.folder <- here::here("Cohort_Dx_initial/1_InstantiateCohorts/Cohorts")
 if (!file.exists(cohorts.folder)){
   dir.create(cohorts.folder)
 }

### 2022-11-29 characterisation/Code/Run_Analysis.R
Update run_analysis

@@ -99,6 +99,26 @@ rm(cohortDefinitionSet, cohortExpression,cohortTableNames)
 
 }
 
+#  IDs of the cohorts of interest ----
+# Cohort ids are in a csv with all cohorts ids
+cohorts_ids  <- read.csv2(here("ATLAS Cohort Definitions_LongCovid.csv")) %>%
+  mutate(name= paste(sub(".*LongCov-ER_", "", name)))
+
+get_id_interest <- function(name_id) {
+  cohorts_ids %>%
+    filter(name == name_id) %>% 
+    select(cohort_definition_id) %>%
+    pull()
+}
+
+new_infection_id   <- get_id_interest("New_Infection") 
+first_infection_id <- get_id_interest("First_infection")
+reinfection_id     <- get_id_interest("Reinfection") 
+tested_negative_all_id  <- get_id_interest("Tested_Negative_all_events") 
+tested_negative_earliest_id <- get_id_interest("Tested negative, earliest") 
+long_covid_id <- get_id_interest("Long COVID-19 symptoms (with test start date)")
+long_covid_symptom_id <- get_id_interest("Long COVID-19 symptoms (with symptom start date)") 
+
 # Creating Long Covid cohorts ----
 if(create_long_covid_cohorts=="FALSE"){
 print(paste0("- Skipping creating Long Covid cohorts"))
@@ -111,15 +131,9 @@ cdm <- cdm_from_con(db,
              write_schema = write_schema,
              cohort_tables = c("er_cohorts_for_longcov"))
 
-cohorts <- cdm$er_cohorts_for_longcov %>%
-compute()
+conn <- connect(connectionDetails)   
 
-
-## Cohort ids -----
-# Cohort ids are in a csv with all cohorts ids
-cohorts_ids  <- read.csv2(here("ATLAS Cohort Definitions_LongCovid.csv")) %>%
-                          mutate(name= paste(sub(".*LongCov-ER_", "", name)))
-# main cohorts
+# Ids for initial filtering
 covid_ids    <- cohorts_ids %>% filter(type=="covid-19") %>% select(cohort_definition_id) %>% pull()
 control_id <- cohorts_ids %>% filter(name=="Tested_Negative_all_events") %>% select(cohort_definition_id) %>% pull()
 # censoring cohorts
@@ -127,28 +141,30 @@ covid_censoring_id <- cohorts_ids %>% filter(type=="covid_censoring") %>% select
[…]

### 2022-12-01 characterisation/Code/Run_Analysis.R
update run analysis

@@ -1,5 +1,3 @@
-# Tables in the write_schema to save Inital Json cohorts
-cohortTableJsons <-"er_cohorts_for_longcov"
 
 # create results folder if needed
 cohorts.folder <- here::here("results")
@@ -13,6 +11,27 @@ if (!file.exists(cohorts.folder)){
   dir.create(cohorts.folder)
 }
 
+#  IDs of the cohorts of interest ----
+# Cohort ids are in a csv with all cohorts ids
+cohorts_ids  <- read.csv2(here("ATLAS Cohort Definitions_LongCovid.csv")) %>%
+  mutate(name= paste(sub(".*LongCov-ER_", "", name)))
+
+get_id_interest <- function(name_id) {
+  cohorts_ids %>%
+    filter(name == name_id) %>% 
+    select(cohort_definition_id) %>%
+    pull()
+}
+
+new_infection_id            <- get_id_interest("New_Infection") 
+first_infection_id          <- get_id_interest("First_infection")
+reinfection_id              <- get_id_interest("Reinfection") 
+tested_negative_all_id      <- get_id_interest("Tested_Negative_all_events") 
+tested_negative_earliest_id <- get_id_interest("Tested negative, earliest") 
+long_covid_id               <- get_id_interest("Long COVID-19 symptoms (with test start date)")
+long_covid_symptom_id       <- get_id_interest("Long COVID-19 symptoms (with symptom start date)") 
+
+
 
 # Initial Json cohorts ----
 if(create_initial_json_cohorts=="FALSE"){
@@ -20,7 +39,9 @@ print(paste0("- Skipping creating initial json cohorts"))
 } else { 
 print(paste0("- Creating initial json cohorts"))
 
-
+  # Tables in the write_schema to save Inital Json cohorts
+  cohortTableJsons <-"er_cohorts_for_longcov"
+  
 ### Get cohort details -----
  cohortJsonFiles <- list.files(here("Cohort_Dx_initial","1_InstantiateCohorts", "Cohorts"))
 cohortJsonFiles <- cohortJsonFiles[str_detect(cohortJsonFiles,".json")]
@@ -99,25 +120,6 @@ rm(cohortDefinitionSet, cohortExpression,cohortTableNames)
 
 }
 
-#  IDs of the cohorts of interest ----
-# Cohort ids are in a csv with all cohorts ids
[…]

### 2022-12-01 characterisation/Code/Run_Analysis.R
update analysis

@@ -303,9 +303,7 @@ covid_infection <- covid_infection %>%
 exclusion_table<-rbind(exclusion_table,
                        tibble(N_current=covid_infection %>%tally()%>%collect()%>%pull(), 
                           exclusion_reason="Less than 120 days of follow-up",
-                          cohort_definition_id = covid_infection %>%
-                                                 select(cohort_definition_id) %>% 
-                            distinct() %>%pull()
+                          cohort_definition_id = covid_id
                          ))
 
 ### First COVID-19 infection  
@@ -1355,7 +1353,7 @@ m.new_covid_tested_negative_earliest_90 <- matching_cohorts(
   name1 = "New infections",
   cohort2 = table1_data_tested_negative_earliest, 
   name2 = "Tested negative, earliest",
-  ratio = 1,
+  ratio = 3,
   window_id = 90
 )
 
@@ -1364,7 +1362,7 @@ m.new_covid_tested_negative_all_90 <- matching_cohorts(
   name1 = "New infections",
   cohort2 = table1_data_tested_negative_all, 
   name2 = "Tested negative, all",
-  ratio = 1,
+  ratio = 3,
   window_id = 90
 )
 
@@ -1374,7 +1372,7 @@ m.first_infection_reinfections_90 <- matching_cohorts(
   name1 = "Reinfections",
   cohort2 = table1_data_first_infection,
   name2 = "First infection",
-  ratio = 3,
+  ratio = 6,
   window_id = 90
 )
 
@@ -1391,7 +1389,7 @@ m.new_covid_tested_negative_earliest_28 <- matching_cohorts(
   name1 = "New infections",
   cohort2 = table1_data_tested_negative_earliest, 
   name2 = "Tested negative, earliest",
-  ratio = 1,
+  ratio = 3,
   window_id = 28
 )
 
@@ -1400,7 +1398,7 @@ m.new_covid_tested_negative_all_28 <- matching_cohorts(
   name1 = "New infections",
   cohort2 = table1_data_tested_negative_all, 
   name2 = "Tested negative, all",
-  ratio = 1,
+  ratio = 3,
   window_id = 28
 )
 
@@ -1411,7 +1409,7 @@ m.first_infection_reinfections_28 <- matching_cohorts(
   cohort2 = table1_data_first_infection,
   name2 = "First infection",
   # cohort2
-  ratio = 3,
+  ratio = 6,
   window_id = 28
 )
 
[…]

### 2022-12-02 characterisation/Reporting_results.Rmd
code update

---
  title: "Long COVID characterisation tables, CPRD"
date: '2022-12-01'
output: 
  html_document:
  toc: true
toc_depth: 3

---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
# packages
library(dplyr)
library(ggplot2)
library(kableExtra)
library(stringr)
```

```{r include=FALSE}
# load results
# Table 1 results
folder <- "CPRD_results/"
database_name <- "_CPRD"
files <-list.files(path= folder, pattern="*.csv")
files <- str_remove(files, "_CPRD.csv")
#files <- paste0(folder, "/", files)

for (i in 1:length(files)){
  assign(files[i], read.csv(paste0(folder, files[i], database_name, ".csv"), header = TRUE, sep = ";"))
} 
# RR
folder <- "CPRD_results/RR/"
files <-list.files(path= folder, pattern="*.csv")
files <- str_remove(files, "_CPRD.csv")
#files <- paste0(folder, "/", files)

for (i in 1:length(files)){
  assign(files[i], read.csv2(paste0(folder, files[i], database_name, ".csv"), header = TRUE, sep = ";", stringsAsFactors=FALSE))
}

```

```{r include=FALSE}
# theme and function for ggplot
mytheme <-  theme_bw() +
  theme(
    #   text = element_text(family = "A"),
    panel.spacing = unit(1, "lines"),
    panel.border = element_blank(),
    legend.position = "top",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    axis.ticks.x =element_line(),
    axis.ticks.y =element_blank(),
    strip.text.y.left = element_text(size = 14, face = "bold", angle = 0),
    strip.text.x = element_text(size = 14, face = "bold"),
    strip.background = element_blank(),
    #  panel.grid.major.y = element_blank() , # remove horizontal lines
    # top, rigth, bottom.left
    plot.margin = unit(c(0,0,1,0), "lines")
  )

get_plot <- function(data) {
  gg.plot <- data  %>%
    ggplot(aes(
      x = relative_risk,
      y = reorder(symptom, relative_risk),
      xmin = low_ci,
      xmax = up_ci,
      color = database)) +
    geom_point(size = 2, position = position_dodge(width = 1)) +
    geom_errorbar(width = 0, size = 1, position = position_dodge(width = 1)) +
    scale_y_discrete(expand=c(0,0), position = "left") +
    scale_x_log10() +
    geom_vline(
      xintercept = 1, colour = "#000000",
      linetype = 1
    ) +
    mytheme +
    xlab("\nRR (with 95% CI)") +
    ylab("")  +
    guides(color = guide_legend(title = ""))

  gg.plot
}

```

# Flowchart

![Study flowchart](flowchart_longcov.png)

## >90 days symptoms  {.tabset}
### Tables
#### Table 1: Baseline characteristics and symptoms recorded

```{r echo=FALSE}
kable(Table1_90days,
      col.names = c("", "COVID-19\ninfection",
                    "First\ninfection", "Reinfections",
                    "Tested negative,\nall", 
                    "Tested negative,\nearliest")) %>%  
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                fixed_thead = T
  ) %>%
  pack_rows("Comorbidities",12, 20) %>%
  row_spec(21, bold = T) %>%
  row_spec(47, bold = T) %>%
  pack_rows("Symptoms",22, 46)

```

#### Table 2: Baseline characteristics and symptoms distribution among COVID-19 infections vs Tested negative, earliest (after matching 1:3 by age group, week of testing and antigen/PCR test)

```{r echo=FALSE}
kable(Table_Matched_Infection_Tested_Negative_earliest_90days,
      col.names = c("", "COVID-19\ninfection", "Tested negative,\nearliest", "SMD")) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F,
                fixed_thead = T) %>%
  pack_rows("Comorbidities",12, 20) %>%
  row_spec(21, bold = T) %>%
  row_spec(47, bold = T) %>%
  pack_rows("Symptoms",22, 46)

```

#### Table 3: Baseline characteristics and symptoms distribution among COVID-19 infections vs Tested negative, all records (after matching 1:3 by age group, week of testing and antigen/PCR test)
```{r}
kable(Table_Matched_Infection_Tested_Negative_all_90days,
      col.names = c("", "COVID-19\ninfection", "Tested negative,\nall", "SMD")) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F,
                fixed_thead = T) %>%
  pack_rows("Comorbidities",12, 20) %>%
  row_spec(21, bold = T) %>%
  row_spec(47, bold = T) %>%
  pack_rows("Symptoms",22, 46)

```

##### Table 4: Baseline characteristics and symptoms among people with a first COVID-19 infection vs Reinfection (after matching 1:6 by age group, week of testing and antigen/PCR test)

```{r echo=FALSE}
kable(Table_Matched_First_infection_Reinfections_90days,
      col.names = c("", "First infection", "Reinfection", "SMD")) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F,
                fixed_thead = T) %>%
  pack_rows("Comorbidities",12, 20) %>%
  row_spec(21, bold = T) %>%
  row_spec(47, bold = T) %>%
  pack_rows("Symptoms",22, 46) 
```

### Relative risks
#### Figure 1: RR for each symptom, COVID-19 infections vs Tested negative
```{r, fig.dim= c(12,8), echo=FALSE}

rr_new_covid_tested_negative <- rbind(RR_new_covid_tested_negative_earliest_90days %>% mutate(records = "Earliest record"),
                                      RR_new_covid_tested_negative_all_90days %>% mutate(records = "All records"))

gg.rr.infec_negative <- get_plot(rr_new_covid_tested_negative)+ facet_grid(.~ records )
gg.rr.infec_negative

```

#### Figure 2: RR for each symptom, first infection vs reinfections
```{r, fig.dim = c(6, 6), echo = FALSE}
gg.rr.first_reinfection <- get_plot(RR_first_infection_reinfections_90days)
gg.rr.first_reinfection
```

## > 28 days symptoms  {.tabset}
### Tables
#### Table 1: Baseline characteristics and symptoms recorded

```{r echo=FALSE}
kable(Table1_28days,
      col.names = c("", "COVID-19\ninfection",
                    "First\ninfection",
                    "Reinfections",
                    "Tested negative,\nall",
                    "Tested negative,\nearliest")) %>%  
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                fixed_thead = T
  ) %>%
  pack_rows("Comorbidities",12, 20) %>%
  row_spec(21, bold = T) %>%
  row_spec(47, bold = T) %>%
  pack_rows("Symptoms",22, 46)

```

#### Table 2: Baseline characteristics and symptoms distribution among COVID-19 infections vs Tested negative, earliest (after matching 1:1 by age group, week of testing and antigen/PCR test)

```{r echo=FALSE}
kable(Table_Matched_Infection_Tested_Negative_earliest_28days,
      col.names = c("", "COVID-19 infection", "Tested negative, earliest", "SMD")) %>%  
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F,
                fixed_thead = T) %>%
  pack_rows("Comorbidities",12, 20) %>%
  row_spec(21, bold = T) %>%
  row_spec(47, bold = T) %>%
  pack_rows("Symptoms",22, 46)

```

#### Table 3: Baseline characteristics and symptoms among people with a first COVID-19 infection vs Reinfection (after matching 1:1 by age group, week of testing and antigen/PCR test)

```{r echo=FALSE}
kable(Table_Matched_First_infection_Reinfections_28days,
      col.names = c("", "First infection", "Reinfection", "SMD")) %>%  
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F,
                fixed_thead = T) %>%
  pack_rows("Comorbidities",12, 20) %>%
  row_spec(21, bold = T) %>%
  row_spec(47, bold = T) %>%
  pack_rows("Symptoms",22, 46) 
```

### Relative risks
#### Figure 1: RR for each symptom, COVID-19 infections vs Tested negative (earliest and all records)
```{r, fig.dim = c(12, 8), echo = FALSE}

rr_new_covid_tested_negative <- rbind(RR_new_covid_tested_negative_earliest_28days %>% mutate(records = "Earliest record"),
                                      RR_new_covid_tested_negative_all_28days %>% mutate(records = "All records"))

gg.rr.infec_negative <- get_plot(rr_new_covid_tested_negative)+ facet_grid(.~ records )
gg.rr.infec_negative

```

#### Figure 2: RR for each symptom, first infection vs reinfections
```{r, fig.dim = c(6, 6), echo = FALSE}
gg.rr.first_reinfection <- get_plot(RR_first_infection_reinfections_28days)
gg.rr.first_reinfection
```

### 2022-12-02 characterisation/Code/Run_Analysis.R

@@ -1291,7 +1291,7 @@ matching_cohorts <- function(cohort1, cohort2,
   data <- rbind(cohort_1 %>%  mutate(cohort = 1, name = name1) ,
                 # comparator cohort
                 cohort_2 %>% mutate(cohort =0,   name = name2)) %>%
-   mutate(age_gr2 = factor(age_gr2,
+  mutate(age_gr2 = factor(age_gr2,
                        levels = c("<=34",
                                   "35-49",
                                   "50-64",
@@ -1429,11 +1429,7 @@ print(paste0("Skipping  generating descriptive tables"))
 } else { 
 print(paste0("Generating descriptive tables"))
   
-  # cdm to get the cohorts for Table 1 - unmatched cohorts 
-  cdm <- cdm_from_con(db, 
-                      cdm_schema = cdm_database_schema,
-                      write_schema = write_schema,
-                      cohort_tables = c("er_long_covid_table1_cohorts")) # here are the cohorts with all symptoms
+
   # functions for numbers
   nice.num<-function(x){
     prettyNum(x, big.mark=",", nsmall = 0, digits=0,scientific = FALSE)
@@ -1450,6 +1446,7 @@ print(paste0("Generating descriptive tables"))
                          "sex",
                          "trimester",
                          "vaccination_status",
+                         "pcr",
                          #comorbidities
                          "asthma",
                          "autoimmune_disease",
@@ -1463,12 +1460,17 @@ print(paste0("Generating descriptive tables"))
                          # long covid + symptoms
                          "long_covid")
  
- factor.vars <- c(other_factor_vars, symptoms, "all_symp")
+factor.vars <- c(other_factor_vars, symptoms, "all_symp")
  rm(other_factor_vars)
    
 # all variables - (includes continous variables)
 vars <- c("age", factor.vars)
   
+# cdm to get the cohorts for Table 1 - unmatched cohorts 
+cdm <- cdm_from_con(db, 
+                    cdm_schema = cdm_database_schema,
+                    write_schema = write_schema,
+                    cohort_tables = c("er_long_covid_table1_cohorts")) # here are the cohorts with all symptoms
 # load matched data 
 load(here("data/table1_data_matched_28.Rdata"))
 load(here("data/table1_data_matched_90.Rdata"))
@@ -1506,7 +1508,7 @@ get_characteristics_matched <- function(df){
[…]

### 2022-12-05 characterisation/Code/Run_Analysis.R
Update Run_Analysis.R

@@ -359,32 +359,13 @@ confirmed_infections <- generate_tested_cohorts(cohorts_interest = covid_cohorts
                                                          )
 covid_infection <- confirmed_infections[[1]]
 first_infection <- confirmed_infections[[2]]
-reinfection     <- confirmed_infections[[3]]
-## inserting these cohorts into the database
-#### remove prior tables if needed
-  sql_query <- glue::glue("DROP TABLE {write_schema}.er_long_covid_final_cohorts\n" )
-  DBI::dbExecute(db, as.character(sql_query))
+reinfections    <- confirmed_infections[[3]]
+## save these cohorts into the database
+computePermanent(covid_infection, name = "er_long_covid_final_cohorts", 
+                 schema = write_schema,   overwrite = TRUE)
 
- # create new table 
-sql_query <- glue::glue("SELECT * INTO {write_schema}.er_long_covid_final_cohorts\n",
-                          "FROM (\n",
-                          dbplyr::sql_render(covid_infection),
-                          "\n) AS from_table")
-DBI::dbExecute(db, as.character(sql_query))
-
-# function to append rows to existing table - using sql
-add_sql_query <- function(tbl_df){
-sql_query <- glue::glue("INSERT INTO {write_schema}.er_long_covid_final_cohorts\n",
-                          "SELECT * FROM (\n",
-                          dbplyr::sql_render(tbl_df),
-                          "\n) AS from_table")
-DBI::dbExecute(db, as.character(sql_query)) 
-}
-
-
-
-add_sql_query(first_infection)
-add_sql_query(reinfection)
+appendPermanent(first_infection, name = "er_long_covid_final_cohorts", schema = write_schema)
+appendPermanent(reinfections,    name = "er_long_covid_final_cohorts",  schema = write_schema)
 
 ## getting Tested negative cohorts ----
 ### PCR and antigen negative _all events 
@@ -401,13 +382,13 @@ tested_negative_all      <- negative_infections[[1]]
 tested_negative_earliest <- negative_infections[[2]]
 
 # add tested negative cohorts to db
-add_sql_query(tested_negative_all)
-add_sql_query(tested_negative_earliest)
+appendPermanent(tested_negative_all, name = "er_long_covid_final_cohorts",  schema = write_schema)
[…]

### 2023-01-09 characterisation/Manuscript_Tables_Figures.Rmd
Create Manuscript_Tables_Figures.Rmd

---
title: "Manuscript_Tables_LongCovid"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 6
    toc_float:
      collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, cache = FALSE, cache.lazy = FALSE)
```

```{r include=FALSE}
# packages
library(dplyr)
library(ggplot2)
library(kableExtra)
library(stringr)
library(here)
library(cowplot)
library(lubridate)

Sys.setlocale("LC_ALL", "English")
options(knitr.kable.NA = " ")

# SIDIAP results
database_name <- "SIDIAP"
folder <- paste0("Results_", database_name)

files <-list.files(path= folder, pattern="*.csv") 
files <- str_remove(files, paste0(".csv"))

for (i in 1:length(files)){
  assign(files[i], read.csv(paste0(folder, "/", files[i], ".csv"), header = TRUE, sep = ","))
}

# CPRD results
database_name <- "CPRD"
folder <- paste0("Results_", database_name)

files <-list.files(path= folder, pattern="*.csv")
files <- str_remove(files, paste0(".csv"))

for (i in 1:length(files)){
  assign(files[i], read.csv(paste0(folder, "/", files[i], ".csv"), header = TRUE, sep = ","))
}

get_baseline_main_table <- function(sidiap_data, cprd_data) {
  Table <- sidiap_data %>%
    select(X, COVID.19.infection, Tested.negative..earliest) %>%
    left_join(cprd_data%>%
                select("X",
                       "COVID.infection.CPRD" = "COVID.19.infection"  ,
                       "Tested.negative.CPRD" = "Tested.negative..earliest"
                ) %>% 
          mutate(X = ifelse(X == "Trimester = jan-apr 2021 (%)",
                            "   Jan-apr 2021"  ,
                            ifelse(X == "Vaccination status = first dose vaccination (%)",                "   First dose vaccination", X)))) 
  Table1 <- kable(Table[c(1:30),],
                  col.names = c("", 
                                "COVID-19\ninfection", 
                                "First SARS-CoV-2 negative test ",
                                "COVID-19\ninfection", 
                                "First SARS-CoV-2 negative test "
                  )) %>%  
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  fixed_thead = T
    ) %>%
    add_header_above(c(" ", "SIDIAP" = 2, "CPRD" = 2)) %>%
    pack_rows("Comorbidities",22, 30) 
  Table1
}

# symptoms table
get_baseline_sup_table <- function(sidiap_data, cprd_data) {
  Table <- sidiap_data %>%
    select(-"COVID.19.infection",-"Tested.negative..earliest") %>%
    left_join(cprd_data%>%
                select("X",
                       "First.infection.CPRD" = "First.infection",
                       "Reinfections.CPRD" = "Reinfections",
                       "Tested.negative.all.CPRD" = "Tested.negative..all",
                ) %>% 
          mutate(X = ifelse(X == "Trimester = jan-apr 2021 (%)",
                            "   Jan-apr 2021"  ,
                     ifelse(X == "Vaccination status = first dose vaccination (%)",
                                   "   First dose vaccination", X)))) 
  Table1 <- kable(Table[c(1:30),],
                  col.names = c("",
                                "First infection",
                                "Re-infections",
                                "SARS-CoV-2 negative tests, all records",
                                "First infection",
                                "Re-infections",
                                "SARS-CoV-2 negative tests, all records"
                  ),
                  row.names = FALSE) %>%  
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  fixed_thead = T
    ) %>%
    add_header_above(c(" ", "SIDIAP" = 3, "CPRD" = 3)) %>%
    pack_rows("Comorbidities",22, 30) 
  Table1
}

get_matched_table_negative <- function(sidiap_data, cprd_data) {
  Table <- sidiap_data %>%
  left_join(cprd_data%>%
              select("X",
                     "COVID-19 infection, CPRD" = "New.infections"  ,
                     "Tested negative, CPRD" = "Tested.negative..earliest",
                     "SMD, CPRD" = "SMD"
              ) %>% 
          mutate(X = ifelse(X == "Trimester = jan-apr 2021 (%)",
                            "   Jan-apr 2021"  ,
                            ifelse(X == "Vaccination status = first dose vaccination (%)",
                                   "   First dose vaccination", X))))
Table1 <- kable(Table[c(1:30),],
                col.names = c("", "COVID-19\ninfection",
                              "First SARS-CoV-2 negative test ", "SMD", 
                              "COVID-19\ninfection",
                              "First SARS-CoV-2 negative test ", "SMD"
                )) %>%  
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                fixed_thead = T
  ) %>%
  add_header_above(c(" ", "SIDIAP" = 3, "CPRD" = 3)) %>%
  pack_rows("Comorbidities",22, 30) 
Table1
}

get_matched_table_first_reinfection <- function(sidiap_data, cprd_data) {
  Table <- sidiap_data %>%
    left_join(cprd_data%>%
                select("X",
                       "First infection, CPRD" = "First.infection"  ,
                       "Reinfections, CPRD" = "Reinfections",
                       "SMD, CPRD" = "SMD"
                )%>% 
          mutate(X = ifelse(X == "Trimester = jan-apr 2021 (%)",
                            "   Jan-apr 2021"  ,
                   ifelse(X == "Vaccination status = first dose vaccination (%)",
                                   "   First dose vaccination", X))))
  Table1 <- kable(Table[c(1:30),],
                  col.names = c("", "First\ninfection", 
                                "Re-infections", "SMD",
                                "First\ninfection",
                                "Re-infections", "SMD"
                  )) %>%  
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  fixed_thead = T
    ) %>%
    add_header_above(c(" ", "SIDIAP" = 3, "CPRD" = 3)) %>%
    pack_rows("Comorbidities",22, 30) 
  Table1
}

mytheme <-  theme_bw() +
  theme(
    #   text = element_text(family = "A"),
    panel.spacing = unit(1, "lines"),    
    axis.line.x.bottom = element_line(color = 'black'),
    axis.line.y.left   = element_line(color = 'black'),
    panel.border = element_blank(),
    panel.grid.major.y = element_blank() ,
    # explicitly set the horizontal lines (or they will disappear too)
    panel.grid.major.x = element_line( size=.1, color="#F5F4F6" ),
    legend.position = "top",
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    axis.title = element_text(size = 14),
    axis.text.y = element_text(size = 14,),
    axis.text.x = element_text(size = 14,),
    axis.ticks.x =element_line(),
    axis.ticks.y =element_blank(),
    # strip.text.x.left = element_text(size = 14, face = "bold", angle = 90),
    strip.text.y = element_text(size = 14, face = "bold"),
    strip.background = element_blank(),
    #  panel.grid.major.y = element_blank() , # remove horizontal lines
    # top, rigth, bottom.left
    plot.margin = unit(c(0,0,1,0), "lines")
  )

# symptoms table
get_symptoms_main_table <- function(sidiap_data, cprd_data) {
  Table <- sidiap_data %>%
    left_join(cprd_data%>%
                select("X",
                       "COVID.infection.CPRD" = "COVID.19.infection"  ,
                       "First.infection.CPRD" = "First.infection",
                       "Reinfections.CPRD" = "Reinfections",
                       "Tested.negative.all.CPRD" = "Tested.negative..all",
                       "Tested.negative.CPRD" = "Tested.negative..earliest"
                ) %>% 
          mutate(X = ifelse(X == "Trimester = jan-apr 2021 (%)",
                            "   Jan-apr 2021"  ,
                     ifelse(X == "Vaccination status = first dose vaccination (%)",
                                   "   First dose vaccination", X)))) 
  Table1 <- kable(Table[c(1,31:69),],
                  col.names = c("",
                                "COVID-19\ninfection", 
                                "First infection",
                                "Re-infections",
                                "SARS-CoV-2 negative tests",
                                "First SARS-CoV-2 negative test ",
                                 "COVID-19\ninfection", 
                                "First infection",
                                "Re-infections",
                                "SARS-CoV-2 negative tests",
                                "First SARS-CoV-2 negative test "
                  ),
                  row.names = FALSE) %>%  
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  fixed_thead = T
    ) %>%
       pack_rows("Symptoms",3,27 ) %>%
    add_header_above(c("", "SIDIAP" = 5, "CPRD" = 5)) 
  Table1
}

get_rr_infection_negative_plot <- function(data){
plot <- RR_data  %>%
    ggplot(aes(
      x = relative_risk,
      y = reorder(symptom, relative_risk),
      xmin = low_ci,
      xmax = up_ci,
      shape = database,
      color = database)) +
    geom_point(size = 2, position = position_dodge(width = 1)) +
    geom_errorbar(width = 0, size = 1, position = position_dodge(width = 1)) +
    scale_y_discrete(expand=c(0,0), position = "left") +
    scale_x_log10(breaks = c(0.5, 0.8, 1,2, 4, 6),
                  labels = c("0.5","0.8", "1","2", "4", "6"),
                  limits = c(0.5, 8)) +  
    scale_colour_manual(values = c( "#3F8D47","#AE221E",  "#1E27AE")) +
    geom_vline(
      xintercept = 1, colour = "#000000",
      linetype = 1
    ) +
    mytheme +
    xlab("\nRR (with 95% CI)") +
    ylab("")  +
    guides(color = guide_legend(title = "Database"),
           shape = guide_legend(title = "Database")) +
    geom_hline(yintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,10.5,11.5,
                     12.5,13.5,14.5,15.5,16.5,17.5,18.5,19.5,20.5,21.5,22.5,23.5),
                linetype = "dashed",
               color = "#D2D6DB"
    )
plot
}

get_rr_first_reinfection_plot <- function(data){
plot <- RR_data  %>%
    ggplot(aes(
      x = relative_risk,
      y = reorder(symptom, -relative_risk),
      xmin = low_ci,
      xmax = up_ci,
      shape = database,
      color = database)) +
    geom_point(size = 2, position = position_dodge(width = 1)) +
    geom_errorbar(width = 0, size = 1, position = position_dodge(width = 1)) +
    scale_y_discrete(expand=c(0,0), position = "left") +
     scale_x_log10(breaks = c(0.1, 0.2, 0.4, 0.6, 0.8, 1),
                   labels = c("0.1", "0.2", "0.4","0.6", "0.8", "1"),
                  limits = c(0.04, 1.2)
                  ) +  
    scale_colour_manual(values = c( "#3F8D47","#AE221E",  "#1E27AE")) +
    geom_vline(
      xintercept = 1, colour = "#000000",
      linetype = 1
    ) +
    mytheme +
    xlab("\nRR (with 95% CI)") +
    ylab("")  +
    guides(color = guide_legend(title = "Database"),
           shape = guide_legend(title = "Database")) +
    geom_hline(yintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,10.5,11.5,
                     12.5,13.5,14.5,15.5,16.5,17.5,18.5,19.5,20.5,21.5,22.5,23.5),
                linetype = "dashed",
               color = "#D2D6DB"
    )
plot
}

```

## Main results
### Table 1: Baseline characteristics of individuals with COVID-19 and tested negative (earliest record)

```{r echo=FALSE}
table1 <- get_baseline_main_table(sidiap_data = Table1_90days_SIDIAP,
                                  cprd_data = Table1_90days_CPRD)
table1
```

### Figure 1: Incidence rates of COVID-19 and long-COVID-19

```{r, fig.dim = c(8, 8), echo = FALSE}
Incidence_rates_Covid_LongCov_SIDIAP$time <- NULL
Incidence_rates_Covid_LongCov_CPRD <- Incidence_rates_Covid_LongCov_CPRD %>%
  rename(ir_100000_pys = incidence_100000_pys,
         ir_100000_pys_95CI_lower = incidence_100000_pys_95CI_lower,
         ir_100000_pys_95CI_upper = incidence_100000_pys_95CI_upper)
IR_data <- rbind(Incidence_rates_Covid_LongCov_CPRD, Incidence_rates_Covid_LongCov_SIDIAP)
Proportion_data <- rbind(Proportion_LongCovid_90days_CPRD, Proportion_LongCovid_90days_SIDIAP)

data_IR_fig90 <- IR_data %>%
  filter(cohort != "Long COVID-19 (28 days)" ) %>%
  filter(!(is.na(n_events))) %>%
  mutate(sex= as.character(sex)) %>%
  mutate(incidence_start_date = as.Date(incidence_start_date)) %>%
  select(incidence_start_date, n_persons, n_events, person_years, ir_100000_pys,  ir_100000_pys_95CI_lower,  ir_100000_pys_95CI_upper, age_group, sex, cohort, database) %>%
  rbind(Proportion_data %>%
          mutate(person_years = person_days/365) %>%
          select(-person_days) %>%
          filter(cohort=="COVID-19 infection") %>%
          mutate(age_group = ifelse(age_group == "<=34", "18;34",
                              ifelse(age_group == "35-49", "35;49", 
                              ifelse(age_group == "50-64", "50;64",
                              ifelse(age_group == "65-79", "65;79",
                              ifelse(age_group == ">=80", "80;150",
                              ifelse(age_group == "Overall", "Overall", 
                                     NA))))))) %>%
          mutate(cohort = "Long COVID-19 among those with COVID-19, 90 days")
  ) %>%
  mutate(age_group = ifelse(age_group == "18;150", "Overall", 
                            ifelse(age_group == "80;150", "\u226580", age_group))) %>%
  mutate(age_group = factor(age_group,
                            levels = c("Overall", "18;34", "35;49", "50;64", "65;79", "\u226580"))) %>%
      mutate(cohort = ifelse(cohort == "Long COVID-19 among those with COVID-19, 90 days", 
                           "Long COVID symptoms among those with COVID-19",
                           ifelse(cohort == "Long COVID-19 (90 days)", "Long COVID symptoms after COVID-19 among the general population", cohort))) %>%
  mutate(cohort = factor(cohort, levels = c(
    "COVID-19 infections",
     "Long COVID symptoms after COVID-19 among the general population",
     "Long COVID symptoms among those with COVID-19"
  )))

plot_IR_overall <- function(age_to_filter, data){ 
  plot <- data %>%
  filter(age_group %in% age_to_filter) %>%
  ggplot() +
#  geom_smooth(aes(x =incidence_start_date, y =  ir_100000_pys), method="auto", se=TRUE, fullrange=FALSE, level=0.95)+
geom_line(aes(x =incidence_start_date, y =  ir_100000_pys, color = database), size = 1.2)+
geom_ribbon(aes(x =incidence_start_date, y =  ir_100000_pys,
                ymin = ir_100000_pys_95CI_lower, ymax = ir_100000_pys_95CI_upper,
                group= database
                ), alpha = 0.3) +
scale_y_continuous(limits = c(0,NA)) +
scale_x_date(date_breaks = "2 month",
               date_labels = ("%b %y"),
               expand = c(0,0)) +
        scale_colour_manual(values = c( "#3F8D47","#AE221E",  "#1E27AE")) +
  theme_bw()+
  theme(legend.position="top",
        plot.margin = unit(c(0.1, 0.5, 0.1, 0.1), "cm"),
        strip.text.y = element_text(angle = 0),
    strip.background =element_rect(fill="#F5F5F5")) +
  ylab("IR per 100,000 p-y") +
    facet_wrap(~cohort, scales = "free_y", ncol = 1) +
 # facet_grid(rows = vars(cohort),
 #            scales = "fixed") +
    xlab("Date of COVID-19 infection") +
        guides(color = guide_legend(title = "Database"), 
               fill = guide_legend(title = "Database"))
   plot         
  }

fig_IR_overall <- plot_IR_overall(age_to_filter = "Overall", data = data_IR_fig90) 
fig_IR_overall
```

### Figure 2: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days

```{r, fig.dim = c(8, 8), echo = FALSE}
## Relative risks figure
 RR_data <- rbind(RR_new_covid_tested_negative_earliest_90days_SIDIAP,
                  RR_new_covid_tested_negative_earliest_90days_CPRD) %>%
  mutate(symptom = ifelse(symptom == "Altered smell taste", "Altered smell or taste",
                          ifelse(symptom =="Cognitive dysfunction brain fog", "Cognitive dysfunction",
                                 ifelse(symptom == "Fatigue malaise", "Fatigue or malaise",
                                        ifelse(symptom == "Muscle spams pain", "Muscle spasms or pain", symptom
                                        )))))

gg.rr.covid_negative_both_90 <- get_rr_infection_negative_plot(data = RR_data)
gg.rr.covid_negative_both_90

```

```{r, fig.dim = c(8, 8), echo = FALSE}
gg.rr.covid_negative_both <-  gg.rr.covid_negative_both_90 + 
   theme(axis.text.x = element_text(size = 14, angle = 90,hjust=0.95,vjust=0.2)) +
  coord_flip()
gg.rr.covid_negative_both
```

### Figure 3: RR of long-COVID symptoms: first infection vs re-infection - 90 days

```{r, fig.dim = c(8, 8), echo = FALSE}
RR_data <- rbind(RR_first_infection_reinfections_90days_SIDIAP,
                  RR_first_infection_reinfections_90days_CPRD) %>%
  mutate(symptom = ifelse(symptom == "Altered smell taste",
                          "Altered smell or taste",
                    ifelse(symptom =="Cognitive dysfunction brain fog",
                           "Cognitive dysfunction",
                    ifelse(symptom == "Fatigue malaise",
                           "Fatigue or malaise",
                    ifelse(symptom == "Muscle spams pain",
                           "Muscle spasms or pain", symptom
                                        )))))

 gg.rr.first_reinfection_90 <-  get_rr_first_reinfection_plot(data = RR_data)
  gg.rr.first_reinfection_90
```

## Supplementary
### Baseline characteristics and symptoms distribution
#### 1. Table: Baseline characteristics of first infections, re-infections and all negative SARS-CoV-2 tests records

```{r}
table1_sup <- get_baseline_sup_table(sidiap_data = Table1_90days_SIDIAP,
                                  cprd_data = Table1_90days_CPRD)
table1_sup
```

#### 2. Table: Symptoms distribution across cohorts (unmatched) - 90 days

```{r}
get_symptoms_main_table(sidiap_data = Table1_90days_SIDIAP, 
                        cprd_data = Table1_90days_CPRD)
```

#### 3. Table: Symptoms distribution across cohorts (unmatched) - 28 days

```{r}
get_symptoms_main_table(sidiap_data = Table1_28days_SIDIAP, 
                        cprd_data = Table1_28days_CPRD)
```

#### 4. Table: Baseline characteristics - COVID-19 infection vs first negative test matched 3:1

```{r echo=FALSE}
Sup_table_matched_negative_90 <- get_matched_table_negative(
  sidiap_data = Table_Matched_Infection_Tested_Negative_earliest_90days_SIDIAP,
  cprd_data = Table_Matched_Infection_Tested_Negative_earliest_90days_CPRD)
Sup_table_matched_negative_90 
```

#### 5. Table: Baseline characteristics: first COVID-19 infection vs re-infections matched 1:3

```{r echo=FALSE}
Sup_table_matched_first_reinfection_90 <- get_matched_table_first_reinfection(
  sidiap_data = Table_Matched_First_infection_Reinfections_90days_SIDIAP,
  cprd_data = Table_Matched_First_infection_Reinfections_90days_CPRD)
Sup_table_matched_first_reinfection_90 
```
### Incidence Rates
#### 1. Table: Incidence Rates of COVID-19 & long COVID symptoms

```{r}

data_table_IR <- data_IR_fig90 %>% 
  filter(age_group == "Overall" & sex == "Both") %>%
  relocate(database, cohort, incidence_start_date, n_events,
           person_years) %>%
  select(-n_persons, -age_group, -sex) %>%
  mutate(person_years = sprintf(person_years, fmt = '%.0f'),
    ir_100000_pys = sprintf(ir_100000_pys, fmt = '%.1f'),
         ir_100000_pys_95CI_lower = sprintf(ir_100000_pys_95CI_lower, fmt = '%.1f'),
         ir_100000_pys_95CI_upper = sprintf(ir_100000_pys_95CI_upper, fmt = '%.1f'),
         ci = paste0(ir_100000_pys, " [",
                     ir_100000_pys_95CI_lower, "-", ir_100000_pys_95CI_upper, "]")
         ) %>%
  select(-ir_100000_pys, -ir_100000_pys_95CI_lower, -ir_100000_pys_95CI_upper)

Table_IR <-  kable(data_table_IR,
                  col.names = c(
                                "Database",
                                "Cohort",
                                "COVID-19 test date",
                                "Number of events",
                                "Person-years",
                                "Incidence Rate"
                  ),
                  row.names = FALSE) %>%  
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  fixed_thead = T
    ) %>%
    collapse_rows(columns = c(1,2))

Table_IR
```

#### 2. Figure: Incidence Rates by Sex and Age group
##### A. SIDIAP

```{r echo=FALSE}

brk_vec <- seq.Date(as.Date("2020-10-01"),
                    as.Date("2021-10-01"),by="2 month")

plot_IR <- function(age_to_filter, data, brk_vec){ 
  plot <- data %>%
  filter(age_group %in% age_to_filter) %>%
    mutate(cohort = ifelse(cohort == "COVID-19 infections", "COVID-19 infections",
                           ifelse(cohort == "Long COVID symptoms after COVID-19 among the general population", "Long COVID among\nthe general population", "Long COVID among\nthose infected"))) %>%
  ggplot() +
#  geom_smooth(aes(x =incidence_start_date, y =  ir_100000_pys), method="auto", se=TRUE, fullrange=FALSE, level=0.95)+
geom_line(aes(x =incidence_start_date,
              y =  ir_100000_pys,
              color = age_group), size = 1.2)+
#    geom_ribbon(aes(x =incidence_start_date, 
    # y =  ir_100000_pys, color = age_group,
    # ymin = ir_100000_pys_95CI_lower, ymax = ir_100000_pys_95CI_upper
    # ), alpha = 0.1) +
#scale_y_continuous(limits = c(0,NA)) +
scale_x_date(breaks = brk_vec,
 #date_breaks = "2 month",
               date_labels = ("%b %y"),
               expand = c(0,0)) +
scale_colour_manual(values = c("#90e0ef","#00b4d8","#0077b6","#023E8A", "#01022F"
  #"#000000","#0075c4","#5b8c5a","#d8973c","#dc392e","#d8973c","#dc392e"
  # "#bee9e8","#62b6cb",","#cae9ff","#5fa8d3"
                                     )) +
    theme_bw()+
    theme(
      #panel.spacing.x = unit(4, "mm"),
      strip.text.y.left =  element_text(angle = 0),
      legend.position="top",
      plot.margin = unit(c(0, 0, 0, 0), "cm"))+
  ylab("IR per 100,000 p-y") +
 facet_grid(cohort ~sex  , 
            scales = "free") +    
    xlab("Date of COVID-19 infection") +
        guides(color = guide_legend(title = "Age group"))
   plot         
  }

fig_IR_age_sex_SIDIAP  <- plot_IR(data = data_IR_fig90 %>% filter(database == "SIDIAP"),
                                     age_to_filter = c("18;34",
                                             "35;49",
                                             "50;64",
                                             "65;79",
                                             "\u226580"),
                                  brk_vec = brk_vec)
fig_IR_age_sex_SIDIAP 
```

```{r include=FALSE}

ggsave(paste0(here(),"/Results/Figures/IR_Sex_Age_SIDIAP.tiff"),
fig_IR_age_sex_SIDIAP ,
       dpi = 300,
       width = 9, height = 6)
```

##### B. CPRD

```{r echo=FALSE}

brk_vec <- seq.Date(as.Date("2020-10-01"),
                    as.Date("2020-12-01"),by="1 month")

fig_IR_age_sex_CPRD <-  plot_IR(data = data_IR_fig90 %>% filter(database == "CPRD"),
                                     age_to_filter = c(
                                       "18;34",
                                             "35;49",
                                             "50;64",
                                             "65;79",
                                             "\u226580"),
                                brk_vec = brk_vec)
fig_IR_age_sex_CPRD

ggsave(paste0(here(),"/Results/Figures/IR_Sex_Age_CPRD.tiff"),
fig_IR_age_sex_CPRD,
       dpi = 300,
       width = 9, height = 6)
```

### Relative Risks - infections vs first negative test 
#### 1. Table: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days
```{r}
get_RR <- function(sidiap_data, cprd_data) {
  RR_infections <- rbind(sidiap_data, cprd_data
                      ) %>%
  mutate(name_1 = "COVID-19 infection") %>%
  mutate(relative_risk = paste0(sprintf(relative_risk, fmt = '%.2f'),
                                " [",
                                sprintf(low_ci, fmt = '%.2f'),
                                ";",
                                sprintf(up_ci, fmt = '%.2f'),
                                "]"
         )) %>%
    select (-prop_1, -prop_2, -low_ci, -up_ci, 
                        -name_1, -name_2, -total_pop_1, -total_pop_2,) %>%
    relocate(database, .before = symptom)  %>%
    arrange(desc(database), desc(relative_risk))

table <- kable(RR_infections,  col.names = c(
     "Database",
                               "Symptom",
                              "Events COVID-19 infection",
                              "Events first negative test",
                             "Relative risk [with 95%CI]"

                  ),
                  row.names = FALSE) %>%  
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  fixed_thead = T
    ) %>%
    collapse_rows(columns = 1)
table
}

table_RR_90 <- get_RR(sidiap_data = RR_new_covid_tested_negative_earliest_90days_SIDIAP,
                  cprd_data = RR_new_covid_tested_negative_earliest_90days_CPRD)
table_RR_90
```

#### 2. Table: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 28 days

```{r}
table_RR_28 <- get_RR(sidiap_data = RR_new_covid_tested_negative_earliest_28days_SIDIAP,
                  cprd_data = RR_new_covid_tested_negative_earliest_28days_CPRD)
table_RR_28
```

#### 3. Figure: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 28 days

```{r, fig.dim = c(8, 8), echo = FALSE}
## Relative risks figure
 RR_data <- rbind(RR_new_covid_tested_negative_earliest_28days_SIDIAP,
                  RR_new_covid_tested_negative_earliest_28days_CPRD) %>%
  mutate(symptom = ifelse(symptom == "Altered smell taste", "Altered smell or taste",
                          ifelse(symptom =="Cognitive dysfunction brain fog", "Cognitive dysfunction",
                                 ifelse(symptom == "Fatigue malaise", "Fatigue or malaise",
                                        ifelse(symptom == "Muscle spams pain", "Muscle spasms or pain", symptom
                                        )))))

gg.rr.covid_negative_both_28 <- get_rr_infection_negative_plot(data = RR_data)
gg.rr.covid_negative_both_28 
```

### Relative Risks - re-infections vs first infection
#### 1. Table: RR of long-COVID symptoms, first infection vs re-infection - 90 days

```{r}
get_RR_numbers_re_infec <- function(sidiap_data, cprd_data) {
  RR_infections <- rbind(sidiap_data, cprd_data
                      ) %>%
  mutate(relative_risk = paste0(sprintf(relative_risk, fmt = '%.2f'),
                                " [",
                                sprintf(low_ci, fmt = '%.2f'),
                                ";",
                                sprintf(up_ci, fmt = '%.2f'),
                                "]"
         )) %>%
    select (-prop_1, -prop_2, -low_ci, -up_ci, 
                        -name_1, -name_2, -total_pop_1, -total_pop_2,) %>%
    relocate(database,.before = symptom)  %>%
    arrange(desc(database),relative_risk)

table_RR_re <- kable(RR_infections,  col.names = c(
     "Database",
                               "Symptom",
                              "Events re-infection",
                              "Events first infection",
                             "Relative risk [with 95%CI]"

                  ),
                  row.names = FALSE) %>%  
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  fixed_thead = T
    ) %>%
    collapse_rows(columns = 1)
table_RR_re

}

table_RR_re_90 <- get_RR_numbers_re_infec(sidiap_data = RR_first_infection_reinfections_90days_SIDIAP,
                                       cprd_data = RR_first_infection_reinfections_90days_CPRD)
 table_RR_re_90 
```

#### 2. Table: RR of long-COVID symptoms, first infection vs re-infection - 28 days
```{r}
table_RR_re_28 <- get_RR_numbers_re_infec(sidiap_data = RR_first_infection_reinfections_28days_SIDIAP,
                                       cprd_data = RR_first_infection_reinfections_28days_CPRD)
 table_RR_re_28
```

#### 3. Figure: RR of long-COVID symptoms, first infection vs re-infection - 28 days

```{r, fig.dim = c(8, 8), echo = FALSE}

RR_data <- rbind(RR_first_infection_reinfections_28days_SIDIAP,   RR_first_infection_reinfections_28days_CPRD) %>%
  mutate(symptom = ifelse(symptom == "Altered smell taste",
                          "Altered smell or taste",
                    ifelse(symptom =="Cognitive dysfunction brain fog",
                           "Cognitive dysfunction",
                    ifelse(symptom == "Fatigue malaise",
                           "Fatigue or malaise",
                    ifelse(symptom == "Muscle spams pain",
                           "Muscle spasms or pain", symptom
                                        )))))

gg.rr.first_reinfection_28 <-  get_rr_first_reinfection_plot(data = RR_data) +  
  scale_x_log10(breaks = c(0.1, 0.2, 0.4, 0.6, 0.8, 1,2, 3),
                   labels = c("0.1", "0.2", "0.4","0.6", "", "1", "2", "3"),
                  limits = c(0.04,3))

gg.rr.first_reinfection_28

```

### Relative Risks - infections vs all negative tests
#### 1. Table: RR of long COVID symptoms, COVID-19 infection vs all SARS-CoV-2 negative tests - 90 days
```{r}
table_RR_90 <- get_RR(sidiap_data = RR_new_covid_tested_negative_earliest_90days_SIDIAP,
                  cprd_data = RR_new_covid_tested_negative_earliest_90days_CPRD)
table_RR_90
```

#### 2. Figure: RR of long COVID symptoms, COVID-19 infection vs SARS-CoV-2 negative tests (all records) - 90 days

```{r, fig.dim = c(8, 8), echo = FALSE}

RR_data <- rbind(RR_new_covid_tested_negative_all_90days_SIDIAP,
                 RR_new_covid_tested_negative_all_90days_CPRD) %>%
  mutate(symptom = ifelse(symptom == "Altered smell taste",
                          "Altered smell or taste",
                    ifelse(symptom =="Cognitive dysfunction brain fog",
                           "Cognitive dysfunction",
                    ifelse(symptom == "Fatigue malaise",
                           "Fatigue or malaise",
                    ifelse(symptom == "Muscle spams pain",
                           "Muscle spasms or pain", symptom
                                        )))))

gg.rr.covid_negative_all_90 <- get_rr_infection_negative_plot(data = RR_data)
gg.rr.covid_negative_all_90
```

#### 3. Table: RR of long COVID symptoms, COVID-19 infection vs all SARS-CoV-2 negative tests - 28 days
```{r}
table_RR_28 <- get_RR(sidiap_data = RR_new_covid_tested_negative_earliest_28days_SIDIAP,
                  cprd_data = RR_new_covid_tested_negative_earliest_28days_CPRD)
table_RR_28
```

#### 4. Figure: RR of long COVID symptoms, COVID-19 infection vs SARS-CoV-2 negative tests (all records) - 28 days

```{r, fig.dim = c(8, 8), echo = FALSE}

RR_data <- rbind(RR_new_covid_tested_negative_all_28days_SIDIAP,
                 RR_new_covid_tested_negative_all_28days_CPRD) %>%
  mutate(symptom = ifelse(symptom == "Altered smell taste",
                          "Altered smell or taste",
                    ifelse(symptom =="Cognitive dysfunction brain fog",
                           "Cognitive dysfunction",
                    ifelse(symptom == "Fatigue malaise",
                           "Fatigue or malaise",
                    ifelse(symptom == "Muscle spams pain",
                           "Muscle spasms or pain", symptom
                                        )))))

gg.rr.covid_negative_all_28 <- get_rr_infection_negative_plot(data = RR_data)
gg.rr.covid_negative_all_28
```

### 2023-01-10 characterisation/Manuscript_Tables_Figures.Rmd
Update Manuscript_Tables_Figures.Rmd

@@
 }
+
+col1 <- "#3A6D82"
+col2 <- "#9F5339"
 
@@
                   limits = c(0.5, 8)) +  
-    scale_colour_manual(values = c( "#3F8D47","#AE221E",  "#1E27AE")) +
+    scale_colour_manual(values = c(col1, col2)) +
     geom_vline(
@@
                   ) +  
-    scale_colour_manual(values = c( "#3F8D47","#AE221E",  "#1E27AE")) +
+    scale_colour_manual(values = c(col1, col2)) +
     geom_vline(
@@
 ### Table 1: Baseline characteristics of individuals with COVID-19 and tested negative (earliest record)
-
 ```{r echo=FALSE}
@@
 ### Figure 1: Incidence rates of COVID-19 and long-COVID-19
-
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
                expand = c(0,0)) +
-        scale_colour_manual(values = c( "#3F8D47","#AE221E",  "#1E27AE")) +
+        scale_colour_manual(values = c(col1, col2)) +
   theme_bw()+
@@
 ### Figure 2: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days
-
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
 ### Figure 3: RR of long-COVID symptoms: first infection vs re-infection - 90 days
-
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
 #### 1. Table: Baseline characteristics of first infections, re-infections and all negative SARS-CoV-2 tests records
-
 ```{r}
@@
 #### 2. Table: Symptoms distribution across cohorts (unmatched) - 90 days
-
 ```{r}
@@
 #### 3. Table: Symptoms distribution across cohorts (unmatched) - 28 days
-
 ```{r}
@@
 #### 4. Table: Baseline characteristics - COVID-19 infection vs first negative test matched 3:1
-
 ```{r echo=FALSE}
@@
 #### 5. Table: Baseline characteristics: first COVID-19 infection vs re-infections matched 1:3
-
 ```{r echo=FALSE}
@@
 ```
+
 ### Incidence Rates
 #### 1. Table: Incidence Rates of COVID-19 & long COVID symptoms
-
 ```{r}
@@
 ##### A. SIDIAP
-
 ```{r echo=FALSE}
@@
 ##### B. CPRD
-
 ```{r echo=FALSE}
@@
 #### 2. Table: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 28 days
-
 ```{r}
@@
 #### 3. Figure: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 28 days
-
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
 #### 1. Table: RR of long-COVID symptoms, first infection vs re-infection - 90 days
-
 ```{r}
@@
 #### 3. Figure: RR of long-COVID symptoms, first infection vs re-infection - 28 days
-
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
 #### 2. Figure: RR of long COVID symptoms, COVID-19 infection vs SARS-CoV-2 negative tests (all records) - 90 days
-
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
 #### 4. Figure: RR of long COVID symptoms, COVID-19 infection vs SARS-CoV-2 negative tests (all records) - 28 days
-
 ```{r, fig.dim = c(8, 8), echo = FALSE}

### 2023-05-31 characterisation/Manuscript_Tables_Figures.Rmd
first version

@@
                    labels = c("0.1", "0.2", "0.4","0.6", "0.8", "1"),
-                  limits = c(0.04, 1.2)
+                  limits = c(0.035, 1.2)
                   ) +  
@@
 ```{r}
-table_RR_90 <- get_RR(sidiap_data = RR_new_covid_tested_negative_earliest_90days_SIDIAP,
-                  cprd_data = RR_new_covid_tested_negative_earliest_90days_CPRD)
+table_RR_90 <- get_RR(sidiap_data = RR_new_covid_tested_negative_all_90days_SIDIAP,
+                  cprd_data = RR_new_covid_tested_negative_all_90days_CPRD)
 table_RR_90
@@
 ```{r}
-table_RR_28 <- get_RR(sidiap_data = RR_new_covid_tested_negative_earliest_28days_SIDIAP,
-                  cprd_data = RR_new_covid_tested_negative_earliest_28days_CPRD)
+table_RR_28 <- get_RR(sidiap_data = RR_new_covid_tested_negative_all_28days_SIDIAP,
+                  cprd_data = RR_new_covid_tested_negative_all_28days_CPRD)
 table_RR_28

### 2023-05-31 characterisation/Code/Code_to_Run.R

@@ -3,10 +3,7 @@
 
 # # packages
 library(here)
-library(SqlRender)
 library(DBI)
-library(DatabaseConnector)
-library(CohortGenerator)
 library(tidyr)
 library(dplyr)
 library(dbplyr)
@@ -15,7 +12,6 @@ library(stringr)
 library(lubridate)
 library(MatchIt)
 library(tsibble)
-library(CirceR)
 library(survey)
 library(gtsummary)
 library(tableone)
@@ -24,51 +20,18 @@ library(epitools)
 library(fmsb)
 library(DescTools)
 library(IncidencePrevalence)
-library(DrugUtilisation)
-# if (!require("pacman")) install.packages("pacman")
-# library(pacman)
-# p_load(SqlRender,
-#        DBI,
-#        DatabaseConnector,
-#        CohortGenerator,
-#        here,
-#        tidyr,
-#        dplyr,
-#        dbplyr,
-#        CDMConnector,
-#        stringr,
-#        lubridate,
-#        MatchIt,
-#        tsibble,
-#        CirceR,
-#        survey,
-#        gtsummary,
-#        tableone,
-#        forcats,
-#        fmsb,
-#        DescTools,
-#        epitools,
-#        remotes)
-# when getting error instlling from Github - 
-# options(download.file.method = "libcurl")
-# remotes::install_github("darwin-eu-dev/IncidencePrevalence")
-# remotes::install_github("darwin-eu-dev/DrugUtilisation")
+library(PatientProfiles)
 
 # Connection details - to change locally  ----
+database_name <- "CPRD AURUM"
+server_dbi<- Sys.getenv("DB_SERVER_p20_059_cdm_aurum_dbi")
+user      <- Sys.getenv("DB_USER")
+password  <- Sys.getenv("DB_PASSWORD")
+port      <- Sys.getenv("DB_PORT") 
+host      <- Sys.getenv("DB_HOST") 
 
-server    <- Sys.getenv("SERVER_Long_covid22t2")
-server_dbi<- Sys.getenv("SERVER_DBI_Long_covid22t2")
-user      <- Sys.getenv("DB_USER_Long_test")
-password  <- Sys.getenv("DB_PASSWORD_Long_test")
-port      <- Sys.getenv("DB_PORT_Long_test") 
-host      <- Sys.getenv("DB_HOST_Long_test") 
-
-targetDialect              <- "postgresql"
-cdm_database_schema        <- "omop22t2_cmbd"
-vocabulary_database_schema <- "omop21t2_cmbd" 
[…]

### 2023-05-31 characterisation/Code/Run_Analysis.R

@@ -1,206 +1,102 @@
-# create results folder if needed
+# initial parameters ----
+## stratification periods
+if (cdmName(cdm) == "SIDIAP") {
+  wild_period_start <- as.Date("2020-09-01")
+  alpha_period_start <- as.Date("2020-12-15")
+  delta_period_start <- as.Date("2021-05-15")
+  omicron_period_start <- as.Date("2021-12-15")
+} else if (cdmName(cdm) == "CPRD AURUM") {
+  wild_period_start <- as.Date("2020-09-01")
+  alpha_period_start <- as.Date("2020-12-15")
+  delta_period_start <- as.Date("2021-05-15")
+  omicron_period_start <- as.Date("2021-12-15")
+} else {
+  stop("use `SIDIAP` or `CPRD AURUM` as database_name please")
+}
+
+## create results folder if needed
 cohorts.folder <- here::here("results")
 if (!file.exists(cohorts.folder)){
   dir.create(cohorts.folder)
 }
 
-# create data folder if needed
+## create data folder if needed
 cohorts.folder <- here::here("data")
 if (!file.exists(cohorts.folder)){
   dir.create(cohorts.folder)
 }
 rm(cohorts.folder)
 
-#  IDs of the cohorts of interest ----
-# Cohort ids are in a csv with all cohorts ids
-cohorts_ids  <- read.csv2(here("ATLAS Cohort Definitions_LongCovid.csv")) %>%
-  mutate(name= paste(sub(".*LongCov-ER_", "", name)))
+# cohortNames
+jsonCohortName <- paste0(cohortStem, "_json")
+attritionCohortName <- paste0(cohortStem, "_attrition_cohorts")
 
-get_id_interest <- function(name_id) {
-  cohorts_ids %>%
-    filter(name == name_id) %>% 
-    select(cohort_definition_id) %>%
-    pull()
+# get cohort Id
+getCohortId <- function(x, name) {
+  cohortSet(cdm) %>%
+    filter(cohort_name %in% name) %>%
+    pull(cohort_definition_id)
 }
 
-new_infection_id            <- get_id_interest("New_Infection") 
-first_infection_id          <- get_id_interest("First_infection")
-reinfection_id              <- get_id_interest("Reinfection") 
-tested_negative_all_id      <- get_id_interest("Tested_Negative_all_events") 
-tested_negative_earliest_id <- get_id_interest("Tested negative, earliest") 
-long_covid_id               <- get_id_interest("Long COVID-19 symptoms (with test start date)")
[…]

### 2023-05-31 characterisation/Revision/Code_to_Run.R
initial version of revision

@@ -1,0 +1,63 @@
+# Long Covid Characterisation study
+# First check that the project "characterisation" is open
+
+# # packages
+library(here)
+library(DBI)
+library(tidyr)
+library(dplyr)
+library(dbplyr)
+library(CDMConnector)
+library(stringr)
+library(lubridate)
+library(MatchIt)
+library(tsibble)
+library(survey)
+library(gtsummary)
+library(tableone)
+library(forcats)
+library(epitools)
+library(fmsb)
+library(DescTools)
+library(IncidencePrevalence)
+library(PatientProfiles)
+
+#remotes::install_github("darwin-eu-dev/DrugUtilisation")
+library(DrugUtilisation)
+
+# Connection details - to change locally  ----
+database_name <- "CPRD AURUM"
+server_dbi <- "cdm_aurum_p21_000557"
+user      <- Sys.getenv("DB_USER")
+password  <- Sys.getenv("DB_PASSWORD")
+port      <- Sys.getenv("DB_PORT") 
+host      <- Sys.getenv("DB_HOST") 
+
+cdm_database_schema        <- "public_100k"
+write_schema               <- "results"
+
+db <- dbConnect(RPostgres::Postgres(), 
+                dbname = server_dbi,
+                port = port,
+                host = host, 
+                user = user, 
+                password = password)
+
+# create cdm object
+cdm <- cdmFromCon(
+  con = db, 
+  cdmSchema = cdm_database_schema, 
+  writeSchema = write_schema,
+  cdmName = database_name
+)
+
+covid_start_date    <- as.Date("2020-09-01", "%Y-%m-%d")
+# censor when COVID-19 testing ends in SIDIAP - don't need to edit this
+covid_end_date      <- as.Date("2022-03-28", "%Y-%m-%d")
+
+# cohortStem
+cohortStem <- "lcwp1_"
+
+# Run analysis
+source(here("Code/Run_Analysis.R"))
+

### 2023-05-31 characterisation/Revision/Run_Analysis.R

@@ -1,0 +1,1977 @@
+# initial parameters ----
+## stratification periods
+if (cdmName(cdm) == "SIDIAP") {
+  wild_period_start <- as.Date("2020-09-01")
+  alpha_period_start <- as.Date("2020-12-15")
+  delta_period_start <- as.Date("2021-05-15")
+  omicron_period_start <- as.Date("2021-12-15")
+} else if (cdmName(cdm) == "CPRD AURUM") {
+  wild_period_start <- as.Date("2020-09-01")
+  alpha_period_start <- as.Date("2020-12-15")
+  delta_period_start <- as.Date("2021-05-15")
+  omicron_period_start <- as.Date("2021-12-15")
+} else {
+  stop("use `SIDIAP` or `CPRD AURUM` as database_name please")
+}
+
+## create results folder if needed
+cohorts.folder <- here::here("results")
+if (!file.exists(cohorts.folder)){
+  dir.create(cohorts.folder)
+}
+
+## create data folder if needed
+cohorts.folder <- here::here("data")
+if (!file.exists(cohorts.folder)){
+  dir.create(cohorts.folder)
+}
+rm(cohorts.folder)
+
+# cohortNames
+symptomCohortName <- paste0(cohortStem, "symptom")
+vaccinatedCohortName <- paste0(cohortStem, "vaccinated")
+indexCohortName <- paste0(cohortStem, "index")
+attritionCohortName <- paste0(cohortStem, "attrition_cohorts")
+
+# Initial Json cohorts ----
+cohorts <- readCohortSet(here("Cohorts", "Vaccinated"))
+cdm <- generateCohortSet(cdm, cohorts, vaccinatedCohortName)
+
+cohorts <- readCohortSet(here("Cohorts", "Index"))
+cdm <- generateCohortSet(cdm, cohorts, indexCohortName, overwrite = TRUE)
+
+cohorts <- readCohortSet(here("Cohorts", "Attrition"))
+cdm <- generateCohortSet(cdm, cohorts, attritionCohortName)
+
+cohorts <- readCohortSet(here("Cohorts", "Symptoms"))
+cdm <- generateCohortSet(cdm, cohorts, symptomCohortName)
+
+# Creating Long Covid cohorts ----
+
+getId <- function(x, name) {
+  cohortSet(x) %>% 
+    filter(grepl(name, cohort_name)) %>% 
+    pull("cohort_definition_id")
+}
+
[…]

### 2023-06-01 characterisation/Revision/Code_to_Run.R
new version

@@ -21,6 +21,7 @@ library(fmsb)
 library(DescTools)
 library(IncidencePrevalence)
 library(PatientProfiles)
+library(readr)
 
 #remotes::install_github("darwin-eu-dev/DrugUtilisation")
 library(DrugUtilisation)

### 2023-06-01 characterisation/Revision/Run_Analysis.R

@@ -31,407 +31,191 @@ rm(cohorts.folder)
 symptomCohortName <- paste0(cohortStem, "symptom")
 vaccinatedCohortName <- paste0(cohortStem, "vaccinated")
 indexCohortName <- paste0(cohortStem, "index")
-attritionCohortName <- paste0(cohortStem, "attrition_cohorts")
+longcovidCohortName <- paste0(cohortStem, "longcovid")
 
 # Initial Json cohorts ----
 cohorts <- readCohortSet(here("Cohorts", "Vaccinated"))
-cdm <- generateCohortSet(cdm, cohorts, vaccinatedCohortName)
+cdm <- generateCohortSet(cdm, cohorts, vaccinatedCohortName, overwrite = TRUE)
 
 cohorts <- readCohortSet(here("Cohorts", "Index"))
 cdm <- generateCohortSet(cdm, cohorts, indexCohortName, overwrite = TRUE)
 
-cohorts <- readCohortSet(here("Cohorts", "Attrition"))
-cdm <- generateCohortSet(cdm, cohorts, attritionCohortName)
-
 cohorts <- readCohortSet(here("Cohorts", "Symptoms"))
-cdm <- generateCohortSet(cdm, cohorts, symptomCohortName)
+cdm <- generateCohortSet(cdm, cohorts, symptomCohortName, overwrite = TRUE)
 
 # Creating Long Covid cohorts ----
 
 getId <- function(x, name) {
   cohortSet(x) %>% 
-    filter(grepl(name, cohort_name)) %>% 
+    filter(.data$cohort_name == .env$name) %>% 
     pull("cohort_definition_id")
 }
 
 influenza_id <- getId(cdm[[indexCohortName]], "influenza")
-covidAttrition_id <- getId(cdm[[attritionCohortName]], "covid")
+covidAttrition_id <- getId(cdm[[indexCohortName]], "any_covid")
+positiveTest_id <- getId(cdm[[indexCohortName]], "positive_test")
+negativeTest_id <- getId(cdm[[indexCohortName]], "negative_test")
 
-target <- cdm[[attritionCohortName]] %>%
-  filter(cohort_definition_id == 1) %>%
+target <- cdm[[indexCohortName]] %>%
+  filter(cohort_definition_id == positiveTest_id) %>%
   addDemographics(cdm, futureObservation = FALSE) %>%
[…]

### 2023-06-01 characterisation/Revision/Run_Analysis.R
Update Run_Analysis.R

@@ -142,8 +142,11 @@ longcovid <- cdm[[indexCohortName]] %>%
   mutate(follow_up = !!datediff("cohort_start_date", "cohort_end_date")) %>%
   filter(follow_up >= 120) %>%
   filter(cohort_start_date >= covid_start_date) %>%
+  group_by(subject_id) %>%
   window_order(cohort_start_date) %>%
   mutate(seq = row_number()) %>%
+  ungroup() %>%
+  window_order() %>%
   select(seq, subject_id, cohort_start_date, cohort_end_date) %>%
   computeQuery()
 

### 2023-06-01 characterisation/Revision/Run_Analysis.R
Update Run_Analysis.R

@@ -157,14 +157,16 @@ longnegative <- cdm[[indexCohortName]] %>%
   addIntersect(cdm, "observation_period", targetStartDate = "observation_period_end_date", targetEndDate = NULL, value = "date", window = c(1, Inf), nameStyle = "end_observation") %>%
   addIntersect(cdm, "death", targetStartDate = "death", targetEndDate = NULL, value = "date", window = c(1, Inf), nameStyle = "death") %>%
   mutate(
-    next_covid = next_covid - 1, next_influenza = next_influenza - 1,
-    one_year = cohort_start_date + 365, end_covid_testing = covid_end_date,
-    cohort_end_date = pmin(
+    next_covid = as.Date(next_covid - days(1)), 
+    next_influenza = as.Date(next_influenza - days(1)),
+    one_year = as.Date(cohort_start_date + days(365)), 
+    end_covid_testing = covid_end_date,
+    cohort_end_date = as.Date(pmin(
       end_observation, death, next_covid, next_influenza, one_year,
       end_covid_testing
-    ), follow_up = cohort_end_date - cohort_start_date
+    ))
   ) %>%
-  filter(cohort_start_date < cohort_end_date) %>%
+  mutate(follow_up = !!datediff("cohort_start_date", "cohort_end_date")) %>%
   filter(follow_up >= 120) %>%
   filter(cohort_start_date >= covid_start_date) %>%
   window_order(cohort_start_date) %>%

### 2023-09-07 characterisation/Manuscript_Tables_Figures.Rmd
solve attrition

--- 2023-01-10 characterisation/Manuscript_Tables_Figures.Rmd
@@
 for (i in 1:length(files)){
-  assign(files[i], read.csv(paste0(folder, "/", files[i], ".csv"), header = TRUE, sep = ","))
+  assign(
+    files[i], 
+    read.csv(paste0(folder, "/", files[i], ".csv"), header = TRUE, sep = ",")
+  )
 }
@@
     select(X, COVID.19.infection, Tested.negative..earliest) %>%
-    left_join(cprd_data%>%
+    full_join(cprd_data%>%
                 select("X",
@@
                             ifelse(X == "Vaccination status = first dose vaccination (%)",                "   First dose vaccination", X)))) 
-  Table1 <- kable(Table[c(1:30),],
+  Table1 <- kable(Table[c(1:34),],
                   col.names = c("", 
@@
     add_header_above(c(" ", "SIDIAP" = 2, "CPRD" = 2)) %>%
-    pack_rows("Comorbidities",22, 30) 
+    pack_rows("Comorbidities",26, 34) 
   Table1
@@
                                    "   First dose vaccination", X)))) 
-  Table1 <- kable(Table[c(1:30),],
+  Table1 <- kable(Table[c(1:34),],
                   col.names = c("",
@@
     add_header_above(c(" ", "SIDIAP" = 3, "CPRD" = 3)) %>%
-    pack_rows("Comorbidities",22, 30) 
+    pack_rows("Comorbidities",26, 34) 
   Table1
@@
                                    "   First dose vaccination", X))))
-Table1 <- kable(Table[c(1:30),],
+Table1 <- kable(Table[c(1:34),],
                 col.names = c("", "COVID-19\ninfection",
@@
   add_header_above(c(" ", "SIDIAP" = 3, "CPRD" = 3)) %>%
-  pack_rows("Comorbidities",22, 30) 
+  pack_rows("Comorbidities",26, 34) 
 Table1
@@
                                    "   First dose vaccination", X))))
-  Table1 <- kable(Table[c(1:30),],
+  Table1 <- kable(Table[c(1:34),],
                   col.names = c("", "First\ninfection", 
@@
                                    "   First dose vaccination", X)))) 
-  Table1 <- kable(Table[c(1,31:69),],
+  Table1 <- kable(Table[c(1,35:74),],
                   col.names = c("",
@@
 get_rr_infection_negative_plot <- function(data){
-plot <- RR_data  %>%
+plot <- data  %>%
     ggplot(aes(
@@
 
+get_rr_infection_negative_plot_facet <- function(data){
+plot <- data  %>%
+    ggplot(aes(
+      x = relative_risk,
+      y = reorder(symptom, relative_risk),
+      xmin = low_ci,
+      xmax = up_ci,
+      shape = database,
+      color = database)) +
+    geom_point(size = 2, position = position_dodge(width = 1)) +
+    geom_errorbar(width = 0, size = 1, position = position_dodge(width = 1)) +
+    facet_grid(cols = vars(wave)) +
+    scale_y_discrete(expand=c(0,0), position = "left") +
+    scale_x_log10(breaks = c(0.5, 0.8, 1,2, 4, 6),
+                  labels = c("0.5","0.8", "1","2", "4", "6"),
+                  limits = c(0.5, 8)) +  
+    scale_colour_manual(values = c(col1, col2)) +
+    geom_vline(
+      xintercept = 1, colour = "#000000",
+      linetype = 1
+    ) +
+    mytheme +
+    xlab("\nRR (with 95% CI)") +
+    ylab("")  +
+    guides(color = guide_legend(title = "Database"),
+           shape = guide_legend(title = "Database")) +
+    geom_hline(yintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,10.5,11.5,
+                     12.5,13.5,14.5,15.5,16.5,17.5,18.5,19.5,20.5,21.5,22.5,23.5),
+                linetype = "dashed",
+               color = "#D2D6DB"
+    )
+plot
+}
+
 get_rr_first_reinfection_plot <- function(data){
-plot <- RR_data  %>%
+plot <- data  %>%
     ggplot(aes(
@@
     scale_y_discrete(expand=c(0,0), position = "left") +
-     scale_x_log10(breaks = c(0.1, 0.2, 0.4, 0.6, 0.8, 1),
-                   labels = c("0.1", "0.2", "0.4","0.6", "0.8", "1"),
-                  limits = c(0.04, 1.2)
+     scale_x_log10(breaks = c(0.6, 0.8, 1, 2),
+                   labels = c("0.6", "0.8", "1", "2"),
+                  limits = c(0.5, 2)
                   ) +  
@@
 
+get_rr_first_reinfection_plot_facet <- function(data){
+plot <- data  %>%
+    ggplot(aes(
+      x = relative_risk,
+      y = reorder(symptom, -relative_risk),
+      xmin = low_ci,
+      xmax = up_ci,
+      shape = database,
+      color = database)) +
+    geom_point(size = 2, position = position_dodge(width = 1)) +
+    geom_errorbar(width = 0, size = 1, position = position_dodge(width = 1)) +
+    facet_grid(cols = vars(wave)) +
+    scale_y_discrete(expand=c(0,0), position = "left") +
+     scale_x_log10(breaks = c(0.1, 0.2, 0.4, 0.6, 0.8, 1, 2),
+                   labels = c("0.1", "0.2", "0.4","0.6", "0.8", "1", "2"),
+                  limits = c(0.04, 2)
+                  ) +  
+    scale_colour_manual(values = c(col1, col2)) +
+    geom_vline(
+      xintercept = 1, colour = "#000000",
+      linetype = 1
+    ) +
+    mytheme +
+    xlab("\nRR (with 95% CI)") +
+    ylab("")  +
+    guides(color = guide_legend(title = "Database"),
+           shape = guide_legend(title = "Database")) +
+    geom_hline(yintercept = c(1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5,10.5,11.5,
+                     12.5,13.5,14.5,15.5,16.5,17.5,18.5,19.5,20.5,21.5,22.5,23.5),
+                linetype = "dashed",
+               color = "#D2D6DB"
+    )
+plot
+}
+
+variables <- ls()
+for (variable in variables) {
+  x <- get(variable)
+  if ("vaccine" %in% colnames(x)) {
+    x <- x %>% 
+      dplyr::filter(.data$vaccine == "overall") %>% 
+      dplyr::select(-"vaccine")
+    assign(variable, x)
+  }
+}
+
 ```
@@
 ```{r, fig.dim = c(8, 8), echo = FALSE}
-Incidence_rates_Covid_LongCov_SIDIAP$time <- NULL
-Incidence_rates_Covid_LongCov_CPRD <- Incidence_rates_Covid_LongCov_CPRD %>%
-  rename(ir_100000_pys = incidence_100000_pys,
-         ir_100000_pys_95CI_lower = incidence_100000_pys_95CI_lower,
-         ir_100000_pys_95CI_upper = incidence_100000_pys_95CI_upper)
 IR_data <- rbind(Incidence_rates_Covid_LongCov_CPRD, Incidence_rates_Covid_LongCov_SIDIAP)
@@
   mutate(incidence_start_date = as.Date(incidence_start_date)) %>%
-  select(incidence_start_date, n_persons, n_events, person_years, ir_100000_pys,  ir_100000_pys_95CI_lower,  ir_100000_pys_95CI_upper, age_group, sex, cohort, database) %>%
+  select(
+    incidence_start_date, n_persons, n_events, person_years, 
+    ir_100000_pys = incidence_100000_pys,  
+    ir_100000_pys_95CI_lower = incidence_100000_pys_95CI_lower, 
+    ir_100000_pys_95CI_upper = incidence_100000_pys_95CI_upper, 
+    age_group, sex, cohort, database
+  ) %>%
   rbind(Proportion_data %>%
@@
           filter(cohort=="COVID-19 infection") %>%
-          mutate(age_group = ifelse(age_group == "<=34", "18;34",
-                              ifelse(age_group == "35-49", "35;49", 
-                              ifelse(age_group == "50-64", "50;64",
-                              ifelse(age_group == "65-79", "65;79",
-                              ifelse(age_group == ">=80", "80;150",
-                              ifelse(age_group == "Overall", "Overall", 
-                                     NA))))))) %>%
           mutate(cohort = "Long COVID-19 among those with COVID-19, 90 days")
   ) %>%
-  mutate(age_group = ifelse(age_group == "18;150", "Overall", 
-                            ifelse(age_group == "80;150", "\u226580", age_group))) %>%
+  mutate(age_group = ifelse(age_group == "18 to 150", "Overall", 
+                            ifelse(age_group == "80 to 150", "\u226580", age_group))) %>%
   mutate(age_group = factor(age_group,
-                            levels = c("Overall", "18;34", "35;49", "50;64", "65;79", "\u226580"))) %>%
+                            levels = c("Overall", "18 to 34", "35 to 49", "50 to 64", "65 to 79", "\u226580"))) %>%
       mutate(cohort = ifelse(cohort == "Long COVID-19 among those with COVID-19, 90 days", 
@@
 
-### Figure 2: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days
+### Figure 2A: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days, overall
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
                   RR_new_covid_tested_negative_earliest_90days_CPRD) %>%
+  filter(wave == "overall") %>%
+  select(-"wave") %>%
   mutate(symptom = ifelse(symptom == "Altered smell taste", "Altered smell or taste",
@@
 
+### Figure 2B: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days, by waves
+
+```{r, fig.dim = c(24, 8), echo = FALSE}
+## Relative risks figure
+ RR_data <- rbind(RR_new_covid_tested_negative_earliest_90days_SIDIAP,
+                  RR_new_covid_tested_negative_earliest_90days_CPRD) %>%
+  filter(wave != "overall") %>%
+  mutate(symptom = ifelse(symptom == "Altered smell taste", "Altered smell or taste",
+                          ifelse(symptom =="Cognitive dysfunction brain fog", "Cognitive dysfunction",
+                                 ifelse(symptom == "Fatigue malaise", "Fatigue or malaise",
+                                        ifelse(symptom == "Muscle spams pain", "Muscle spasms or pain", symptom
+                                        ))))) %>%
+  mutate(wave = factor(wave, levels = c("wild", "alpha", "delta", "omicron")))
+
+gg.rr.covid_negative_both_90 <- get_rr_infection_negative_plot_facet(data = RR_data)
+gg.rr.covid_negative_both_90
+
+```
+
+```{r, fig.dim = c(8, 8), echo = FALSE}
+gg.rr.covid_negative_both <-  gg.rr.covid_negative_both_90 + 
+   theme(axis.text.x = element_text(size = 14, angle = 90,hjust=0.95,vjust=0.2)) +
+  coord_flip()
+gg.rr.covid_negative_both
+```
+
 ### Figure 3: RR of long-COVID symptoms: first infection vs re-infection - 90 days
@@
                   RR_first_infection_reinfections_90days_CPRD) %>%
+  filter(wave == "overall") %>%
+  select(-"wave") %>%
   mutate(symptom = ifelse(symptom == "Altered smell taste",
@@
 fig_IR_age_sex_SIDIAP  <- plot_IR(data = data_IR_fig90 %>% filter(database == "SIDIAP"),
-                                     age_to_filter = c("18;34",
-                                             "35;49",
-                                             "50;64",
-                                             "65;79",
+                                     age_to_filter = c("18 to 34",
+                                             "35 to 49",
+                                             "50 to 64",
+                                             "65 to 79",
                                              "\u226580"),
@@
 
-fig_IR_age_sex_CPRD <-  plot_IR(data = data_IR_fig90 %>% filter(database == "CPRD"),
+fig_IR_age_sex_CPRD <-  plot_IR(data = data_IR_fig90 %>% filter(database == "CPRD AURUM"),
                                      age_to_filter = c(
-                                       "18;34",
-                                             "35;49",
-                                             "50;64",
-                                             "65;79",
+                                       "18 to 34",
+                                             "35 to 49",
+                                             "50 to 64",
+                                             "65 to 79",
                                              "\u226580"),
@@
                       ) %>%
+    filter(wave == "overall") %>%
+    select(-"wave") %>%
   mutate(name_1 = "COVID-19 infection") %>%
@@
                   RR_new_covid_tested_negative_earliest_28days_CPRD) %>%
+  filter(wave == "overall") %>%
+  select(-"wave") %>%
   mutate(symptom = ifelse(symptom == "Altered smell taste", "Altered smell or taste",
@@
                       ) %>%
+    filter(wave == "overall") %>%
+    select(-"wave") %>%
   mutate(relative_risk = paste0(sprintf(relative_risk, fmt = '%.2f'),
@@
 RR_data <- rbind(RR_first_infection_reinfections_28days_SIDIAP,   RR_first_infection_reinfections_28days_CPRD) %>%
+  filter(wave == "overall") %>% select(-"wave") %>%
   mutate(symptom = ifelse(symptom == "Altered smell taste",
@@
                  RR_new_covid_tested_negative_all_90days_CPRD) %>%
+  filter(wave == "overall") %>%
+  select(-"wave") %>%
   mutate(symptom = ifelse(symptom == "Altered smell taste",
@@
                  RR_new_covid_tested_negative_all_28days_CPRD) %>%
+  filter(wave == "overall") %>%
+  select(-"wave") %>%
   mutate(symptom = ifelse(symptom == "Altered smell taste",

### 2023-09-07 characterisation/Code/Run_Analysis_Revision.R

@@ -28,28 +28,28 @@ if (!file.exists(cohorts.folder)){
 rm(cohorts.folder)
 
 # Initial Json cohorts ----
-cohorts <- readCohortSet(here("Code", "Cohorts", "Index"))
-cdm <- generateCohortSet(
-  cdm = cdm, cohortSet = cohorts, name = "index", overwrite = TRUE
-)
-
-cohorts <- readCohortSet(here("Code", "Cohorts", "Vaccinated"))
-cdm <- generateCohortSet(
-  cdm = cdm, cohortSet = cohorts, name = "vaccinated", overwrite = TRUE
-)
-
-cohorts <- readCohortSet(here("Code", "Cohorts", "Symptoms"))
-cdm <- generateCohortSet(
-  cdm = cdm, cohortSet = cohorts, name = "symptoms", overwrite = TRUE
-)
-
-# cdm <- cdmFromCon(
-#   con = db, 
-#   cdmSchema = cdm_database_schema, 
-#   writeSchema = c("schema" = write_schema, "prefix" = write_stem),
-#   cohortTables = c("index", "vaccinated", "symptoms"),
-#   cdmName = database_name
+# cohorts <- readCohortSet(here("Code", "Cohorts", "Index"))
+# cdm <- generateCohortSet(
+#   cdm = cdm, cohortSet = cohorts, name = "index", overwrite = TRUE
 # )
+# 
+# cohorts <- readCohortSet(here("Code", "Cohorts", "Vaccinated"))
+# cdm <- generateCohortSet(
+#   cdm = cdm, cohortSet = cohorts, name = "vaccinated", overwrite = TRUE
+# )
+# 
+# cohorts <- readCohortSet(here("Code", "Cohorts", "Symptoms"))
+# cdm <- generateCohortSet(
+#   cdm = cdm, cohortSet = cohorts, name = "symptoms", overwrite = TRUE
+# )
+
+cdm <- cdmFromCon(
+  con = db,
+  cdmSchema = cdm_database_schema,
+  writeSchema = c("schema" = write_schema, "prefix" = write_stem),
+  cohortTables = c("index", "vaccinated", "symptoms"),
+  cdmName = database_name
+)
 
 # attrition ----
 
@@ -358,7 +358,7 @@ generate_tested_cohorts <- function(index_id, cohort_ids, days_censor_covid){
 } 
 
 confirmed_infections <- generate_tested_cohorts(
-  index_id = covid_id,
[…]

### 2023-10-09 characterisation/Manuscript_Tables_Figures.Rmd
revision

@@
 
+correctSymptomNames <- function(x, column = "symptom") {
+  pairs <- c(
+    "Altered smell taste" = "Altered smell or taste",
+    "Cognitive dysfunction brain fog" = "Cognitive dysfunction",
+    "Fatigue malaise" = "Fatigue or malaise",
+    "Muscle spams pain" = "Muscle spasms or pain",
+    "Depression wo recurrence" = "Depression",
+    "Dyspnea" = "Dyspnoea"
+  )
+  for (k in seq_along(pairs)) {
+    x <- x |>
+      mutate(!!column := gsub(
+        pattern = names(pairs)[k], 
+        replacement = unname(pairs[k]), 
+        x = .data[[column]]
+      ))
+  }
+  return(x)
+}
+
 for (i in 1:length(files)){
@@
                             "   Jan-apr 2021"  ,
-                            ifelse(X == "Vaccination status = first dose vaccination (%)",                "   First dose vaccination", X)))) 
+                            ifelse(X == "Vaccination status = first dose vaccination (%)",                "   First dose vaccination", X)))) %>%
+    correctSymptomNames(column = "X")
   Table1 <- kable(Table[c(1:34),],
@@
                      ifelse(X == "Vaccination status = first dose vaccination (%)",
-                                   "   First dose vaccination", X)))) 
+                                   "   First dose vaccination", X)))) %>%
+    correctSymptomNames(column = "X")
   Table1 <- kable(Table[c(1,35:74),],
@@
 plot <- data  %>%
+  correctSymptomNames() %>%
     ggplot(aes(
@@
 
-### Figure 1: Incidence rates of COVID-19 and long-COVID-19
+### Figure 1: Incidence rates of COVID-19 and Post-acute COVID-19 symptoms
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
       mutate(cohort = ifelse(cohort == "Long COVID-19 among those with COVID-19, 90 days", 
-                           "Long COVID symptoms among those with COVID-19",
-                           ifelse(cohort == "Long COVID-19 (90 days)", "Long COVID symptoms after COVID-19 among the general population", cohort))) %>%
+                           "Post-acute COVID-19 symptoms among those with COVID-19",
+                           ifelse(cohort == "Long COVID-19 (90 days)", "Post-acute COVID-19 symptoms after COVID-19 among the general population", cohort))) %>%
   mutate(cohort = factor(cohort, levels = c(
     "COVID-19 infections",
-     "Long COVID symptoms after COVID-19 among the general population",
-     "Long COVID symptoms among those with COVID-19"
+     "Post-acute COVID-19 symptoms after COVID-19 among the general population",
+     "Post-acute COVID-19 symptoms among those with COVID-19"
   )))
@@
 
-### Figure 2A: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days, overall
+### Figure 2A: RR of Post-acute COVID-19 symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days, overall
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
   select(-"wave") %>%
-  mutate(symptom = ifelse(symptom == "Altered smell taste", "Altered smell or taste",
-                          ifelse(symptom =="Cognitive dysfunction brain fog", "Cognitive dysfunction",
-                                 ifelse(symptom == "Fatigue malaise", "Fatigue or malaise",
-                                        ifelse(symptom == "Muscle spams pain", "Muscle spasms or pain", symptom
-                                        )))))
+  correctSymptomNames()
 
@@
 gg.rr.covid_negative_both_90
+
+ggsave(file="Figure2.svg", plot=gg.rr.covid_negative_both_90, width=10, height=8)
 
@@
 
-### Figure 2B: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days, by waves
+### Figure 2B: RR of Post-acute COVID-19 symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days, by waves
 
@@
   filter(wave != "overall") %>%
-  mutate(symptom = ifelse(symptom == "Altered smell taste", "Altered smell or taste",
-                          ifelse(symptom =="Cognitive dysfunction brain fog", "Cognitive dysfunction",
-                                 ifelse(symptom == "Fatigue malaise", "Fatigue or malaise",
-                                        ifelse(symptom == "Muscle spams pain", "Muscle spasms or pain", symptom
-                                        ))))) %>%
+  correctSymptomNames() %>%
   mutate(wave = factor(wave, levels = c("wild", "alpha", "delta", "omicron")))
@@
 gg.rr.covid_negative_both_90 
+ggsave(file="Figure3.svg", plot=gg.rr.covid_negative_both_90, width=10, height=8)
 
@@
 
-### Figure 3: RR of long-COVID symptoms: first infection vs re-infection - 90 days
+### Figure 3: RR of Post-acute COVID-19 symptoms: first infection vs re-infection - 90 days
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
   select(-"wave") %>%
-  mutate(symptom = ifelse(symptom == "Altered smell taste",
-                          "Altered smell or taste",
-                    ifelse(symptom =="Cognitive dysfunction brain fog",
-                           "Cognitive dysfunction",
-                    ifelse(symptom == "Fatigue malaise",
-                           "Fatigue or malaise",
-                    ifelse(symptom == "Muscle spams pain",
-                           "Muscle spasms or pain", symptom
-                                        )))))
+  correctSymptomNames()
 
@@
 gg.rr.first_reinfection_90
+
+ggsave(file="Figure4.svg", plot=gg.rr.first_reinfection_90, width=10, height=8)
 ```
@@
 ### Incidence Rates
-#### 1. Table: Incidence Rates of COVID-19 & long COVID symptoms
+#### 1. Table: Incidence Rates of COVID-19 & Post-acute COVID-19 symptoms
 ```{r}
@@
     mutate(cohort = ifelse(cohort == "COVID-19 infections", "COVID-19 infections",
-                           ifelse(cohort == "Long COVID symptoms after COVID-19 among the general population", "Long COVID among\nthe general population", "Long COVID among\nthose infected"))) %>%
+                           ifelse(cohort == "Long COVID symptoms after COVID-19 among the general population", "Post-acute COVID-19\nsymptoms among\nthe general population", "Post-acute COVID-19\nsymptoms among\nthose infected"))) %>%
   ggplot() +
@@
 brk_vec <- seq.Date(as.Date("2020-10-01"),
-                    as.Date("2020-12-01"),by="1 month")
+                    as.Date("2021-12-01"),by="2 month")
 
@@
 ### Relative Risks - infections vs first negative test 
-#### 1. Table: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days
+#### 1. Table: RR of Post-acute COVID-19 symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 90 days
 ```{r}
@@
     relocate(database, .before = symptom)  %>%
+    correctSymptomNames() %>%
     arrange(desc(database), desc(relative_risk))
@@
 
-#### 2. Table: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 28 days
+#### 2. Table: RR of Post-acute COVID-19 symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 28 days
 ```{r}
@@
 
-#### 3. Figure: RR of long COVID symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 28 days
+#### 3. Figure: RR of Post-acute COVID-19 symptoms: COVID-19 infection vs first SARS-CoV-2 negative test - 28 days
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
 ### Relative Risks - re-infections vs first infection
-#### 1. Table: RR of long-COVID symptoms, first infection vs re-infection - 90 days
+#### 1. Table: RR of Post-acute COVID-19 symptoms, first infection vs re-infection - 90 days
 ```{r}
@@
     relocate(database,.before = symptom)  %>%
-    arrange(desc(database),relative_risk)
+    arrange(desc(database),relative_risk) %>%
+    correctSymptomNames()
 
@@
 
-#### 2. Table: RR of long-COVID symptoms, first infection vs re-infection - 28 days
+#### 2. Table: RR of Post-acute COVID-19 symptoms, first infection vs re-infection - 28 days
 ```{r}
@@
 
-#### 3. Figure: RR of long-COVID symptoms, first infection vs re-infection - 28 days
+#### 3. Figure: RR of Post-acute COVID-19 symptoms, first infection vs re-infection - 28 days
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
   filter(wave == "overall") %>% select(-"wave") %>%
-  mutate(symptom = ifelse(symptom == "Altered smell taste",
-                          "Altered smell or taste",
-                    ifelse(symptom =="Cognitive dysfunction brain fog",
-                           "Cognitive dysfunction",
-                    ifelse(symptom == "Fatigue malaise",
-                           "Fatigue or malaise",
-                    ifelse(symptom == "Muscle spams pain",
-                           "Muscle spasms or pain", symptom
-                                        )))))
+  correctSymptomNames()
 
@@
 ### Relative Risks - infections vs all negative tests
-#### 1. Table: RR of long COVID symptoms, COVID-19 infection vs all SARS-CoV-2 negative tests - 90 days
+#### 1. Table: RR of Post-acute COVID-19 symptoms, COVID-19 infection vs all SARS-CoV-2 negative tests - 90 days
 ```{r}
@@
 
-#### 2. Figure: RR of long COVID symptoms, COVID-19 infection vs SARS-CoV-2 negative tests (all records) - 90 days
+#### 2. Figure: RR of Post-acute COVID-19 symptoms, COVID-19 infection vs SARS-CoV-2 negative tests (all records) - 90 days
 ```{r, fig.dim = c(8, 8), echo = FALSE}
@@
 
-#### 3. Table: RR of long COVID symptoms, COVID-19 infection vs all SARS-CoV-2 negative tests - 28 days
+#### 3. Table: RR of Post-acute COVID-19 symptoms, COVID-19 infection vs all SARS-CoV-2 negative tests - 28 days
 ```{r}
@@
 
-#### 4. Figure: RR of long COVID symptoms, COVID-19 infection vs SARS-CoV-2 negative tests (all records) - 28 days
+#### 4. Figure: RR of Post-acute COVID-19 symptoms, COVID-19 infection vs SARS-CoV-2 negative tests (all records) - 28 days
 ```{r, fig.dim = c(8, 8), echo = FALSE}
